%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Combat Feats}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Combat feats have an effect that scales up as you gain more BAB.

%%%
\featentry{Blind Fighting}{[Combat]}
%%%

You don't have to \textit{see} to kill.

\textbf{Benefits:} You may reroll your miss chances caused by concealment.

\textbf{+1:} While impaired visually, you may move your normal speed without difficulty.

\textbf{+6:} You have Blindsense out to 60', this allows you to know the location of all creatures within 60'.

\textbf{+11:} You have Tremorsense out to 120', this allows you to "see" anything within 120' that is touching the earth.

\textbf{+16:} You cannot be caught flat footed.

%%%
\featentry{Blitz}{[Combat]}
%%%

You go all out and try to achieve goals in a proactive manner.

\textbf{Benefits:} While charging, you may opt to lose your Dexterity Bonus to AC for one round, but inflicting an extra d6 of damage if you hit.

\textbf{+1:} You may go all out when attacking, adding your Base Attack Bonus to your damage, but provoking an Attack of Opportunity.

\textbf{+6:} Bonus attacks made in a Full Attack for having a high BAB are made with a -2 penalty instead of a -5 penalty.

\textbf{+11:} Every time you inflict damage upon an opponent with your melee attacks, you may immediately use an Intimidate attempt against that opponent as a bonus action.

\textbf{+16:} You may make a Full Attack action as a Standard Action.

%%%
\featentry{Combat Looting}{[Combat]}
%%%

You can put things into your pants in the middle of combat.

\textbf{Benefits:} You may sheathe or store an object as a free action.

\textbf{+1:} You get a +3 bonus to Disarm attempts. Picking up objects off the ground does not provoke an attack of opportunity.

\textbf{+6:} As a Swift action, you may take a ring, amulet/necklace, headband, bracer, or belt from an opponent you have successfully grappled. You may pick up an item off the ground in the middle of a move action.

\textbf{+11:} If you are grappling with an opponent, you may activate or deactivate their magic items with a successful Use Magic Device check. You may make Appraise checks as a free action.

\textbf{+16:} You can take 10 on Use Magic Device and Sleight of Hand checks.

%%%
\featentry{Combat School}{[Combat]}
%%%

You are a member of a completely arbitrary fighting school that has a number of recognizable signature fighting moves.

\textbf{Benefits:} First, name your fighting style (such as "Hammer and Anvil Technique" or "Crescent Moon Style", or "Way of the Lightning Mace"). This fighting style only works with a small list of melee weapons that you have to describe the connectedness to the DM in a half-way believable way. Now, whenever you are using that technique in melee combat, you gain a +2 bonus on attack rolls.

\textbf{+1:} Your immersion in your technique gives you great martial prowess, you gain a +2 to damage rolls in melee combat.

\textbf{+6:} When you strike your opponent with the signature moves of your fighting school in melee, they must make a Fortitude Save (DC 10 + half your level + your Strength bonus) or become \textit{dazed} for one round.

\textbf{+11:} You may take 10 on attack rolls while using your special techniques. The DC to disarm you of a school appropriate weapon is increased by 4.

\textbf{+16:} You may add +5 to-hit on any one attack you make after the first each turn. If you hit an opponent twice in one round, all further attacks this round against that opponent are made with The Edge.

%%%
\featentry{Danger Sense}{[Combat]}
%%%

Maybe Spiders tell you what's up. You certainly react to danger with uncanny effectiveness.

\textbf{Benefits:} You get a +3 bonus on Initiative checks.

\textbf{+1:} For the purpose of Search, Spot, and Listen, you are always considered to be "actively searching". You also get Uncanny Dodge.

\textbf{+6:} You may take 10 on Listen, Spot, and Search checks.

\textbf{+11:} You may make a Sense Motive check (opposed by your opponent's Bluff check) immediately whenever any creature approaches within 60' of you with harmful intent. If you succeed, you know the location of the creature even if you cannot see it.

\textbf{+16:} You are never surprised and always act on the first round of any combat.

%%%
\featentry{Elusive Target}{[Combat]}
%%%

You are very hard to hit when you want to be.

\textbf{Benefits:} You gain a +2 Dodge bonus to AC.

\textbf{+1:} Your opponents do not gain flanking or higher ground bonuses against you.

\textbf{+6:} Your opponents do not inflict extra damage from the Power Attack option.

\textbf{+11:} \textit{Diverting Defense} - As an immediate action, you may redirect an attack against you to any creature in your threatened range, friend or foe. You may not redirect an attack to the creature making the attack.

\textbf{+16:} As an immediate action, you may make an attack that would normally hit you miss instead.

%%%
\featentry{Expert Tactician}{[Combat]}
%%%

You benefit your allies so good they remember you long time.

\textbf{Benefits:} You gain a +4 bonus when flanking instead of the normal +2 bonus. Your allies who flank with you gain the same advantage.

\textbf{+1:} You may Feint as an Immediate action.

\textbf{+6:} As a move action, you may make any 5' square adjacent to yourself into difficult ground.

\textbf{+11:} For determining flanking with your allies, you may count your location as being 5' in any direction from your real location.

\textbf{+16:} You ignore Cover bonuses less than full cover.

%%%
\featentry{Ghost Hunter}{[Combat]}
%%%

You smack around those folks in the spirit world.

\textbf{Benefits:} Your attacks have a 50\% chance of striking incorporeal opponents even if they are not magical.

\textbf{+1:} You can hear incorporeal and ethereal creatures as if they lacked those traits (note that shadows and the like rarely bother to actively move silently).

\textbf{+6:} You can see \textit{invisible} and \textit{ethereal} creatures as if they lacked those traits.

\textbf{+11:} Your attacks count as if you had the Ghost Touch property on your weapons.

\textbf{+16:} Any Armor or shield you use benefits from the Ghost Touch quality.

%%%
\featentry{Giant Slayer}{[Combat]}
%%%

Everyone has a specialty. Yours is miraculously finding ways to stab creatures in the face when it seems improbable that you would be able to reach that high.

\textbf{Benefits:} When you perform a "grab on" Grapple maneuver, you do not provoke an attack of opportunity.

\textbf{+1:} You gain a +4 Dodge bonus to your AC and Reflex Saves against attacks from any creature with a longer natural reach than your own.

\textbf{+6:} You have The Edge against any creature you attack that is larger than you. Also, an opponent using the Improved Grab ability on you provokes an attack of opportunity from you. You may take this attack even if you do not threaten a square occupied by your opponent.

\textbf{+11:} When you attempt to trip an opponent, you may choose whether your opponent resists with Strength or Dexterity.

\textbf{+16:} When involved in an opposed bull rush, grapple, or trip check as the attacker or defender, you may negate the size modifier of both participants. You may not choose to negate the size modifier of only one character.

%%%
\featentry{Great Fortitude}{[Combat]}
%%%

You are so tough. Your belly is like a prism.

\textbf{Benefits:} You gain a +3 bonus to your Fortitude Saves.

\textbf{+1:} You die at -20 instead of -10, and you automatically become stable when reduced to negative hit points.

\textbf{+6:} You gain 1 hit point per level.

\textbf{+11:} You gain DR of 5/-, or your existing DR improves by 5.

\textbf{+16:} You are immune to the \textit{fatigued} and \textit{exhausted} conditions. If you are already immune to these conditions, you gain 1 hit point per level for each condition you were already immune to.

%%%
\featentry{Horde Breaker}{[Combat]}
%%%

You kill really large numbers of people.

\textbf{Benefits:} You gain a number of extra attacks of opportunity each round equal to your Dexterity Bonus (if positive).

\textbf{+1:} Whenever you drop an opponent with a melee attack, you are entitled to a bonus "cleave" attack against another opponent you threaten. You may not take a 5' step or otherwise move before taking this bonus attack. This Cleave attack is considered an attack of opportunity.

\textbf{+6:} You may take a bonus 5' step every time you are entitled to a Cleave attack, which you may take either before or after the attack.

\textbf{+11:} You may generate an aura of \textit{fear} on any opponents within 10' of yourself whenever you drop an opponent in melee. The save DC is 10 + the Hit Dice of the dropped creature.

\textbf{+16:} Opponents you have the Edge against provoke an attack of opportunity from you by moving \textit{into} your threatened area or attacking you.

%%%
\featentry{Hunter}{[Combat]}
%%%

You can move around and shoot things with surprising effectiveness.

\textbf{Benefits:} The penalties for using a ranged weapon from an unstable platform (such as a ship or a moving horse) are halved.

\textbf{+1:} \textit{shot on the run} -- you may take a standard action to attack with a ranged weapon in the middle of a move action, taking some of your movement before and some of your movement after your attack. That still counts as your standard and move action for the round.

\textbf{+6:} You suffer no penalties for firing from unstable ground, a running steed, or any of that.

\textbf{+11:} You may take a full round action to take a double move \textit{and} make a single ranged attack from any point during your movement.

\textbf{+16:} You may take a full round action to \textit{run} a full four times your speed \textit{and} make a single ranged attack from any point during your movement. You retain your Dexterity modifier to AC while running.

%%%
\featentry{Insightful Strike}{[Combat]}
%%%

You hack people down with inherent awesomeness.

\textbf{Benefits:} You may use your Wisdom Modifier in place of your Strength Modifier for your melee attack rolls.

\textbf{+1:} Your attacks have The Edge against an opponent who has a lower Wisdom and Dexterity than your own Wisdom, regardless of relative BAB.

\textbf{+6:} Your melee attacks have a doubled critical threat range.

\textbf{+11:} You make horribly telling blows. The extra critical multiplier of your melee attacks is doubled (x2 becomes x3, x3 becomes x5, and x4 becomes x7).

\textbf{+16:} Any Melee attack you make is considered to be made with a magic weapon that has an enhancement bonus equal to your Wisdom Modifier (if positive).

%%%
\featentry{Iron Will}{[Combat]}
%%%

You are able to grit your teeth and shake off mental influences.

\textbf{Benefits:} You gain a +3 bonus to your Willpower saves.

\textbf{+1:} You gain the \textit{slippery mind} ability of a Rogue.

\textbf{+6:} If you are \textit{stunned}, you are \textit{dazed} instead.

\textbf{+11:} You do not suffer penalties from \textit{pain} and \textit{fear}.

\textbf{+16:} You are immune to compulsion effects.

%%%
\featentry{Juggernaut}{[Combat]}
%%%

You are an unstoppable Juggernaut.

\textbf{Benefits:} You may be considered one size category larger for the purposes of any size dependent d20 roll you make (such as a Bull Rush, Overrun, or Lift action), but not for any other purposes (such as carrying capacity, or what weapons you can wield).

\textbf{+1:} You do not provoke an attack of opportunity for entering an opponent's square.

\textbf{+6:} You gain a +4 bonus to attack and damage rolls to destroy objects. You may shatter a Force Effect by inflicting 30 damage on it.

\textbf{+11:} When you successfully bullrush or overrun an opponent, you automatically Trample them, inflicting damage equal to a natural slam attack for a creature of your size.

\textbf{+16:} You gain the Rock Throwing ability of any standard Giant with a strength equal to or less than yourself.

%%%
\featentry{Lightning Reflexes}{[Combat]}
%%%

You are fasty McFastFast. It helps keep you alive.

\textbf{Benefits:} You gain a +3 bonus to your Reflex saves.

\textbf{+1:} You gain Evasion, if you already have Evasion, that stacks to Improved Evasion.

\textbf{+6:} You may make a Balance Check in place of your Reflex save.

\textbf{+11:} You gain a +3 bonus to your Initiative.

\textbf{+16:} When you take the Full Defense Action, add your level to your AC.

%%%
\featentry{Mage Slayer}{[Combat]}
%%%

You have trained long and hard to kill magic users. Maybe you hate them, maybe you just noticed that most of the really dangerous creatures in the world use magic.

\textbf{Benefits:} You gain Spell Resistance of 5 + Character Level.

\textbf{+1:} Damage you inflict is considered "ongoing damage" for the purposes of concentration checks made before the beginning of your next round. All your attacks in a round are considered the same source of continuing damage.

\textbf{+6:} Creatures cannot cast defensively within your threat range.

\textbf{+11:} Your attacks ignore Deflection bonuses to AC.

\textbf{+16:} When a creature uses a [Teleportation] effect within medium range of yourself, you may choose to be transported as well. This is not an action.

%%%
\featentry{Murderous Intent}{[Combat]}
%%%

You stab people in the face.

\textbf{Benefits:} You may make a coup de grace as a standard action.

\textbf{+1:} When you kill an opponent, you gain a +2 Morale Bonus to your attack and damage rolls for 1 minute.

\textbf{+6:} Once per round, you may take an attack of opportunity against an opponent who is denied their Dexterity bonus to AC.

\textbf{+11:} You may take a Coup de Grace action against opponents who are \textit{stunned}.

\textbf{+16:} You may take a Coup de Grace action against opponents who are \textit{dazed}.

%%%
\featentry{Phalanx Fighter}{[Combat]}
%%%

You fight well in a group.

\textbf{Benefits:} You may take attacks of opportunity even while flat footed.

\textbf{+1:} Any Dodge bonus to AC you gain is also granted to any adjacent allies for as long as you benefit from the bonus and your ally remains adjacent.

\textbf{+6:} Charging is an action that provokes an attack of opportunity from you. This attack is considered to be a "readied attack" if it matters for purposes like setting against a charge.

\textbf{+11:} You may attack with a reach weapon as if it was not a reach weapon. Thus, a medium creature would normally threaten at 5' and 10' with a reach weapon.

\textbf{+16:} You may take an Aid Another action once per round as a free action. You provide double normal bonuses from this effect.

%%%
\featentry{Point Blank Shot}{[Combat]}
%%%

You are crazy good using a ranged weapon in close quarters.

\textbf{Benefits:} When you are within 30' of your target, your attacks with a ranged weapon gain a +3 bonus to-hit.

\textbf{+1:} You add your base attack bonus to damage with any ranged attack within the first range increment.

\textbf{+6:} You do not provoke an attack of opportunity when you make a ranged attack.

\textbf{+11:} When armed with a Ranged Weapon, you may make attacks of opportunity against opponents who provoke them within 30' of you. Movement within this area does not provoke an attack of opportunity.

\textbf{+16:} With a Full Attack action, you may fire a ranged weapon once at every single opponent within the first range increment of your weapon. You gain no additional attacks for having a high BAB. Make a single attack roll for the entire round, and compare to the armor class of each opponent within range.

%%%
\featentry{Sniper}{[Combat]}
%%%

Your shooting is precise and dangerous.

\textbf{Benefits:} Your range increments are 50\% longer than they would ordinarily be. Any benefit of being within 30' of an opponent is retained out to 60'.

\textbf{+1:} \textit{Precise Shot} -- You do not suffer a -4 penalty when firing a ranged weapon into melee and never hit an unintended target in close combats or grapples.

\textbf{+6:} \textit{Sharp Shooting} -- Your ranged attacks ignore Cover Bonuses (total cover still bones you).

\textbf{+11:} Opponents struck by your ranged attacks do not automatically know what square your attack came from, and must attempt to find you normally.

\textbf{+16:} Any time you hit an opponent with a ranged weapon, it is counted as a critical threat. If your weapon already had a 19-20 threat range, increase its critical multiplier by 1.

%%%
\featentry{Subtle Cut}{[Combat]}
%%%

You cut people so bad they have to ask you about it later.

\textbf{Benefits:} Any time you damage an opponent, that damage is increased by 1.

\textbf{+1:} As a standard action, you can make a weapon attack that also reduces a creature's movement rate. For every 5 points of damage this attack does, reduce the creature's movement by 5'. This penalties lasts until the damage is healed.

\textbf{+6:} As a standard action, you may make a weapon attack that also does 2d4 points of Dexterity damage.

\textbf{+11:} Any weapon attack that you make at this level acts as if the weapon had the \textit{wounding} property.

\textbf{+16:} As a standard action, you may make an attack that \textit{daze}s your opponent. This effect lasts one round, and has a DC of 10 + half your level + your Intelligence bonus.

%%%
\featentry{Two Weapon Fighting}{[Combat]}
%%%

When armed with two weapons, you fight with two weapons rather than picking and choosing and fighting with only one. Kind of obvious in retrospect.

\textbf{Benefits:} You suffer no penalty for doing things with your off-hand. When you make an attack or full-attack action, you may make a number of attacks with your off-hand weapon equal to the number of attacks you are afforded with your primary weapon.

\textbf{+1:} While armed with two weapons, you gain an extra Attack of Opportunity each round for each attack you would be allowed for your BAB, these extra attacks of opportunity must be made with your off-hand.

\textbf{+6:} You gain a +2 Shield Bonus to your armor class when fighting with two weapons and not flat footed.

\textbf{+11:} You may Feint as a Swift action while fighting with two weapons.

\textbf{+16:} While fighting with two weapons and not flat footed you may add the enhancement bonus of either your primary or your off-hand weapon to your Shield Bonus to AC.

%%%
\featentry{Weapon Finesse}{[Combat]}
%%%

You are incredibly deft with a sword.

\textbf{Benefits:} You may use your Dexterity Modifier instead of your Strength modifier for calculating your melee attack bonus.

\textbf{+1:} Your special attacks are considered to have the Edge when you attack an opponent with a Dexterity modifier smaller than yours, even if your Base Attack Bonus is not larger.

\textbf{+6:} You may use your Dexterity modifier in place of your Strength modifier when attempting to trip an opponent.

\textbf{+11:} You may use your Dexterity modifier in place of your Strength modifier for calculating your melee damage.

\textbf{+16:} \textit{Opportunist} - Once per turn, when an opponent is struck, you may take an attack of opportunity on that opponent.

%%%
\featentry{Weapon of Righteous Destruction}{[Combat]}
%%%

Your soul powers whatever's in hand to be the perfect implement with which to destroy your foes.

\textbf{Benefit:} Any weapon you use (including unarmed strikes and improvised weapons) counts as Magic, giving it an enhancement bonus to attack and damage (one third you level, rounded up) and allowing it to penetrate DR/Magic.

\textbf{+1:} Your weapon is coated with elemental energy and now deals +1d6 damage of either Acid, Cold, Electric, or Fire (your choice when you get this ability). You can suppress or resume this ability as a Swift action, but while active it also causes your weapon to shed light like a Torch.

\textbf{+6:} The elemental damage improves to +2d6.

\textbf{+11:} Your weapon now deals +1d6 Force damage in addition to the elemental damage (Force damage ignores Hardness).

\textbf{+16:} Your weapon is now also Vorpal.

%%%
\featentry{Whirlwind}{[Combat]}
%%%

You are just as dangerous to everyone around you as to anyone around you.

\textbf{Benefits:} As a full round action, you may make a single attack against each opponent you can reach. Roll one attack roll and compare to each available opponent's AC individually.

\textbf{+1:} You gain a +3 bonus to Balance checks.

\textbf{+6:} As a full round action, you may take a regular move action and make a single attack against each opponent you can reach at any point during your movement. Roll one attack roll and compare to each available opponent's AC individually.

\textbf{+11:} Until your next round after making a whirlwind attack, you may take an attack of opportunity against any opponent that enters your threatened area.

\textbf{+16:} As a full round action, you take a charge action, overrunning any creature in your path, and may make a single attack against each opponent you can reach at any point during your movement. Roll one attack roll and compare to each available opponent's AC individually.

%%%
\featentry{Zen Archery}{[Combat]}
%%%

You are very calm about shooting people in the face. That's a good place to be.

\textbf{Benefits:} You may use your Wisdom Modifier in place of your Dexterity Modifier on ranged attack rolls.

\textbf{+1:} Any opponent you can hear is considered an opponent you can see for purposes of targeting them with ranged attacks.

\textbf{+6:} If you cast a Touch Spell, you can deliver it with a ranged weapon (though you must hit with a normal attack to deliver the spell).

\textbf{+11:} As a Full Round Action, you may make one ranged attack with a +20 Insight bonus to hit.

\textbf{+16:} As a Full Round Action, you may make one ranged attack with a +20 Insight bonus to hit. If this attack hits, your attack is automatically upgraded to a critical threat. If the threat range of your weapon is 19-20, your critical multiplier is increased by one.
