%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Fiendish Feats}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

A feat with the [Fiend] tag can only be taken by a creature who is a Fiend. For this purpose, any creature from any lower plane is a Fiend regardless of its alignment. Further, any elemental or outsider with an Evil alignment is a Fiend regardless of its plane of origin. As with other feats, the abilities granted by feats with the [Fiend] tag are Extraordinary Abilities unless otherwise stated.

%%%
\featentry{Breath Weapon}{[Fiend]}
%%%

\textbf{Prerequisites:} Character level 6, appropriate spell-like ability.

\textbf{Benefits:} Choose a spell-like ability with a duration of Instantaneous, this ability can be used as a supernatural breath Weapon with a conical area equal to a 10' per spell level of the spell-like ability used. Each use of this ability expends one use of the spell-like ability. Each time this breath weapon is used, it cannot be used again for 1d4 rounds.

%%%
\featentry{Carrier}{[Fiend]}
%%%

You are a carrier of a dangerous disease, though you are immune to its effects

\textbf{Prerequisite:} Must have one level of a Fiend class.

\textbf{Benefit:} When you gain this ability choose a disease with a DC equal to the DC your disease would have(Half HD + Con mod). You disease does ability damage or special effects equal to the disease chosen. Once chosen, your disease type does not change, but your diease DC will increase when your HD or Con modifier increase. Unlike a normal disease, this is a supernatural disease, and its initial effects occur immediately.

%%%
\featentry{Constricting Fiend}{[Fiend]}
%%%

Your legs merge into a long tail, and you gain the ability to squeeze the life from your foes.

\textbf{Prerequisites:} Character level 6.

\textbf{Benefits:} On a successful Grapple check, you can choose to do a 4d6 Constricting attack as a normal attack. Due to you change in form and body type, you can only use armor designed for your new form.

%%%
\featentry{Devour the Soul}{[Fiend]}
%%%

As a fiend, you gain nourishment from devouring souls.

\textbf{Prerequisite:} Must have one level of a Fiend class.

\textbf{Benefit:} Each time a soul is consumed (either a receptacle or petitioner), you regain HPs equal to 10 times its CR, heal ability damage or drain equal to its CR, and (if normally you do need to eat) don't need to eat anything else for one month per CR. Souls eaten in this fashion cannot be restored from the dead until you are killed.

%%%
\featentry{Dominions of the Infernal}{[Fiend]}
%%%

When you call, armies of those you have defeated are forced to answer in service.

\textbf{Prerequisite:} Must have the signature \textit{summon} ability of the great Fiendish Houses; must have a Leadership score.

\textbf{Benefit:} If you successfully \textit{summon} a fiend with a CR less than your level, more than one creature may appear. The weaker the creatures are, the more are summoned.

\begin{basictable}{Dominions of the Infernal}{l l}
\textbf{CR} & \textbf{Number Appearing}\\
Level - 2 & d2\\
Level - 3 & d3\\
Level - 4 & d4\\
Level - 5 & d6\\
Level - 6 & d8\\
Level - 7 & 2d6\\
Level - 8 & 2d10\\
Level - 9 & 3d10\\
Level - 10 & 7d6\\
Level - 11 & 3d20\\
Level - 12 & 7d12\\
Level - 13 & 5d20\\
Level - 14 & 6d20\\
Level - 15 & 25d6\\
Level - 16 & 10d20\\
Level - 17 & 40d6\\
Level - 18 & 60d6\\
Level - 19 & 80d6\\
\end{basictable}

%%%
\featentry{Elemental Aura}{[Fiend]}
%%%

Your close relationship with primal elemental forces has manifested in a damaging aura.

\textbf{Prerequisites:} Character level 7, must have a subtype granting immunity to a form of elemental damage.

\textbf{Benefits:} Choose one of your elemental subtypes granting immunity to a form of elemental damage. You radiate a damaging aura that does 4d6 elemental damage of that type to any creature within 10' of you at the beginning of your turn.

%%%
\featentry{Extra Arms}{[Fiend]}
%%%

You have more arms than normal.

\textbf{Prerequisite:} Character level 6 (per extra pair).

\textbf{Benefit:} You have two extra humanoid arms. Each arm has your full strength and dexterity.

\textbf{Special:} You may take this feat more than once, its effects stack. You must have a minimum of 6 levels for \textit{each} iteration of this feat (so a 12th level character may have 2 sets of extra arms).

%%%
\featentry{Essence Gourmand}{[Fiend]}
%%%

Even among soul-eating fiends, you are an accomplished eater.

\textbf{Prerequisite:} Must have one level of a Fiend class, \linkfeat{Devour the Soul}.

\textbf{Benefit:}: Whenever you devour a soul, you gain knowledge of your victim's personal history and important memories (not skills, levels, feats, etc), in addition to the normal effects. You also may cure any one status effect.

%%%
\featentry{Extra Summons}{[Fiend]}
%%%

You may use your Fiend Summoning ability two extra times each day

\textbf{Prerequisite:} Must have the signature \textit{summon} ability of the great Fiendish Houses.

\textbf{Benefit:} Your \textit{summon} ability may be used two extra times each day (the ability is normally usable once each day, so it could be used for 3 separate chances to conjure a fiend).

%%%
\featentry{Fiendish Invisibility}{[Fiend]}
%%%

You cannot be seen.

\textbf{Prerequisite:} Character level 6

\textbf{Benefit:} You are naturally invisible, as with the spell \textit{improved invisibility}.

\textbf{Special:} Fiendish Invisibility always has a flaw, something that will allow your character to be seen. Examples include:

\textit{Invisible in Light}: If you are ever in shadowy illumination, you are visible.

\textit{Visible by Breath}: You are only invisible if you hold your breath for 3 rounds first. When you next exhale, you become visible again.

\textit{Invisible on Stone}: Your character is invisible when touching the ground. While standing on worked floors or flying, you can be seen.

%%%
\featentry{Harmless Form}{[Fiend]}
%%%

You can assume the likeness of a mortal.

\textbf{Prerequisites:} Character level 4

\textbf{Benefits:} You can Change Shape into a medium-sized Humanoid appearance. You can use this ability to Disguise yourself as other people, and it gives a +10 to Disguise checks as normal. When using this ability, your reflection in mirrors is of your true form.

%%%
\featentry{Huge Size}{[Fiend]}
%%%

Your size increases to Huge.

\textbf{Prerequisites:} Character level 10

\textbf{Benefits:} If your size would normally be Large without this feat, it increases to Huge (with all the usual changes).

%%%
\featentry{Large Size}{[Fiend]}
%%%

Your size increases to Large.

\textbf{Prerequisites:} Character level 5.

\textbf{Benefits:} If your size would normally be Medium without this feat, it increases to Large (with all the usual changes).

%%%
\featentry{Pincers}{[Fiend]}
%%%

Two of your hands are converted into pincers.

\textbf{Benefit:} Each Pincer is a natural weapon (1d6 damage for Medium creatures), and attacks made with the Pincer are considered to have the Improved Grab ability.

%%%
\featentry{Poison Sacs}{[Fiend]}
%%%

One of your natural weapons is envenomed.

\textbf{Prerequisite:} Must have one level of a Fiend class.

\textbf{Benefit:} When you gain this ability choose any poison with a DC equal or less to the DC your poison would have (10 + Half HD + Con mod). You poison does ability damage or special effects equal to the poison chosen. Once chosen, your poison type does not change, but your poison DC will increase when your HD or Con modifier increase.

%%%
\featentry{Slime Trail}{[Fiend]}
%%%

You bodies secretes a slick mucus that dries quickly in contact with air, but you've learned to use this to your advantage.

\textbf{Prerequisites:} Character level 2.

\textbf{Benefits:} Your square counts as is the spell \linkspell{Grease} has been cast in it, and this effect ends when you leave a square and renews itself at the end of your turn. You are immune to this effect. You also gain a +4 bonus any checks to escape a Grapple.

%%%
\featentry{Spines of Fury}{[Fiend]}
%%%

Spines cover your body, and you may fire these spine at your enemies.

\textbf{Prerequisites:} Character level 3.

\textbf{Benefits:} You may fire up to two of your body's protruding spines per round as a standard action. You are proficient in these spines, and they have the same game effects as daggers. You may also remove them and use them as daggers, and they count as your natural weapons for purposes of damage reduction and spell effects. You body has a number of spines equal to twice your character level, and regenerate these amounts after one day of rest.

%%%
\featentry{Sting of the Scorpion}{[Fiend]}
%%%

You have a viciously barbed tail that carries a lethal poison.

\textbf{Benefit:} You have a stinger as a natural weapon that carries a poison that inflicts initial and secondary damage of 1d6 Con. The save DC is Constitution based. You may only inject a number of doses of poison per day equal to your Con bonus.

%%%
\featentry{Stolen Breath}{[Fiend]}
%%%

\textbf{Prerequisites:} Character level 3.

\textbf{Benefits:} On a successful grapple check, your opponent may not speak or breathe for one round in addition to any normal effects of a successful Grapple check.

%%%
\featentry{Stoning Gaze}{[Fiend]}
%%%

Your gaze petrifies the living and leaves them as statue to decorate your domain as a warning to others.

\textbf{Prerequisite:} Character level 9

\textbf{Benefit:} Once per round as a Free Action, you \textit{must} designate one living creature within 60 feet of you. If that creature meets your gaze before your next turn, it must make a Fortitude save or be permanently transformed into Stone as by a \linkspell{Stone to Flesh} spell. The save DC is Charisma based. The effects of this feat are a Supernatural Ability.

%%%
\featentry{Supernatural Virulence}{[Fiend]}
%%%

Your poison is as much magical as it is biological.

\textbf{Prerequisite:} Must have a poisonous natural weapon, spell-like ability of 3rd level or lower.

\textbf{Benefit:} Choose one of your spell-like abilities of 3rd level or lower. Any time you successfully poison a victim, they are also targeted by this spell-like ability as if this effect was cast (this expends one use of the ability). While poisoned with your venom, the victim cannot be effected by your spell-like ability again.

%%%
\featentry{Wings of Evil}{[Fiend]}
%%%

You have sinister bat-like wings growing from your back.

\textbf{Prerequisite:} Character level 5.

\textbf{Benefit:} You have a fly speed double that of your normal ground speed. You have good maneuverability, and you must be able to flap your wings to stay aloft (meaning that it requires very specialized armor or cloaks to permit flight).

\textbf{Special:} If you would prefer to have insectile wings or feathered wings instead, you can do that. The maneuverability and speed are unchanged. Once the look and feel of the wings is selected it cannot be changed.

%%%%
%\featentry{Apprenticeship}
%%%%
%
%New Mentor Types for the Lower Planes:
%
%While the race of a mentor is usually irrelevant, some mentors draw their knowledge
%and experience solely from their racial heritage and the magical radiations of
%their home plane. To choose one of these extraplanar mentors, the character must
%have at least 2 ranks in Knowledge (planes).
%
%\textbf{Devil:} A devil mentor is a powerful fiend from the Nine Hells
%that has decided to share its knowledge with a worthy apprentice. An apprentice
%of this mentor gains an innate understanding of infernal contracts, and may use
%Knowledge(the planes) to influence the attitude of any native of a plane that is
%aligned to law and evil, or any subject of a calling spell.
%
%Knowledge(Planes), Knowledge(any one)
%
%\textbf{Demon:} A demon mentor is a powerful fiend from the Abyss, and it has
%forced his apprentices to hide a portion of his power. Once per month, you may
%use one of its spell-like abilities of a 2nd level effect or less.
%
%Bluff, Knowledge(Planes),
%
%\textbf{Nokoloths}: While utterly evil, Nokoloths mentors are honorable in their
%own way and have been known to train apprentices in the dark arts. Apprentices
%of these fiends learn the true nature of evil, and may choose to count as evil
%for the prerequisites of feats or prestige classes, and for magical effects like
%spells or magic items.
%
%Knowledge(Planes), Diplomacy
%
%\textbf{Dezabi}: A Dezabi mentor is a powerful fiend from Carceri. An apprentice
%of this mentor learns the arts of punishment at the hands of these extraplanar
%jailors, and may use Intimidate to influence a creature's attitude to Helpful by
%accepting a +10 to the DC of the check.
%
%Knowledge(Planes), Intimidate
