%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{General Feats}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%
\featentry{Ability Focus}
%%%

\textbf{Prerequisite:} Special attack that allows a save (Breath Weapon, Stunning Attack, etc).

\textbf{Benefit:} Add +2 to the save DC of your selected special attack.

\textbf{Special:} You can take this feat more than once. The effects don't stack. Instead, select a new special attack each time.

%%%
\featentry{Armor Proficiency (Heavy)}
%%%

\textbf{Prerequisites:} \linkfeat{Armor Proficiency (Light)}, \linkfeat{Armor Proficiency (Medium)}.

\textbf{Benefit:} See Armor Proficiency (Light).

\textbf{Normal:} See Armor Proficiency (Light).

%%%
\featentry{Armor Proficiency (Light)}
%%%

\textbf{Benefit:} When you wear a type of armor with which you are proficient, use the armor's normal Armor Check Penalty and Armor Stealth Penalty with your skills, and to determine your movement rate.

\textbf{Normal:} A character who is wearing armor with which she is not proficient counts the Armor Check Penalty and Armor Stealth Penalty as if it were 4 worse than normal when making skill checks or calculating their maximum movement speed.

%%%
\featentry{Armor Proficiency (Medium)}
%%%

\textbf{Prerequisite:} \linkfeat{Armor Proficiency (Light)}.

\textbf{Benefit:} See Armor Proficiency (Light).

\textbf{Normal:} See Armor Proficiency (Light).

%%%
\featentry{Attune Domain}
%%%

You incorporate the workings of a divine domain into your magic.

\textbf{Prerequisite:} Caster level 1st, Must follow a god or philosophy consistent with the chosen domain.

\textbf{Benefit:} Choose a domain when this feat is selected. Every spell from that domain is considered to be on your spell-list for any spellcasting classes you happen to have. These spells are considered to be spells known at the level they appear in the chosen domain. These spells are cast (and prepared, if appropriate) as normal for your class.

\textbf{Special:} You may select this feat multiple times, its effects do not stack. Each time you may select a new domain, so long as your chosen god or philosophy can incorporate all of them. As usual, your DM must approve any god or philosophy. You may not have more than three attuned domains or spheres together.

%%%
\featentry{Attune Sphere}
%%%

You incorporate the workings of a fiendish sphere into your magic.

\textbf{Prerequisite:} Caster level 1st, Must have bled from a wound inflicted by a fiend with access to the chosen sphere.

\textbf{Benefit:} Choose a sphere when this feat is selected. Every spell from that sphere is considered to be on your spell-list for any spellcasting classes you happen to have. You are considered to know each of those spells at the level they appear in the chosen sphere. These spells are cast (and prepared, if appropriate) as normal for your class.

\textbf{Special:} You may select this feat multiple times, its effects do not stack. Each time you may select a new sphere. You may not have more than three attuned domains or spheres together.

%%%
\featentry{Augment Summoning}
%%%

\textbf{Prerequisite:} \linkfeat{Spell Focus} (conjuration).

\textbf{Benefit:} Each creature you conjure with any \textit{summon} spell gains a +4 enhancement bonus to Strength and Constitution for the duration of the spell that summoned it.

%%%
\featentry{Awesome Blow}{[General] [Fighter]}
%%%

\textbf{Prerequisites:} Str 25, size Large or larger.

\textbf{Benefit:} As a standard action, the creature may choose to subtract 4 from its melee attack roll and deliver an awesome blow. If the creature hits a corporeal opponent smaller than itself with an awesome blow, its opponent must succeed on a Reflex save (DC = damage dealt) or be knocked flying 10 feet in a direction of the attacking creature's choice and fall prone. The attacking creature can only push the opponent in a straight line, and the opponent can't move closer to the attacking creature than the square it started in. If an obstacle prevents the completion of the opponent's move, the opponent and the obstacle each take 1d6 points of damage, and the opponent stops in the space adjacent to the obstacle.

%%%
\featentry{Blood War Sorcerer}
%%%

As a battle magician in the blood War, you've learned killing arts that would amaze common spellcasters.

\textbf{Prerequisite:} \linkfeat{Blood War Squaddie}, Caster level 5, must have fought in the Blood war for one year.

\textbf{Benefit:}: Each time one of your spells successfully damages a creature with Spell Resistance, they take a cumulative -1 penalty to SR. This penalty is reduced by 5 for every day of rest, and can be otherwise healed as ability damage. In addition, you may cast any spell that requires you to be of a fiendish race.

%%%
\featentry{Blood War Squaddie}
%%%

Due to your time during the Blood War, you've been tainted, honed, and hardened by the horrors you've seen.

\textbf{Prerequisite:} Knowledge (planes) 2, must have fought in the Blood War for one year.

\textbf{Benefit:} You are immune to fear, and actually gain a +2 Morale bonus to hit, damage, and saves when exposed to an enemy's fear effect (this bonus lasts one minute). In addition, you may treat any fiendish Exotic weapons as martial weapons.

\textbf{Special:} This can only be taken at 1st level.

%%%
\featentry{Boneblade Master}
%%%

You have mastered the alchemic processes needed to create boneblades, as well as their use in combat.

\textbf{Prerequisite:} Craft (alchemy, weapons) 4 ranks

\textbf{Benefit:} You are considered to be proficient in the use of any weapon made from the special material Boneblade, and you may craft weapons out of Boneblade. In addition, you are considered to have the \linkfeat{Improved Critical} feat for any boneblade weapons you use in melee combat.

You also gain a +2 to Initiative checks when wielding a boneblade weapon.

%%%
\featentry{Broker of the Infernal}
%%%

Dues to the study of the Infernal laws, you have learned to harness the powers of True Names in your summoning magic.

\textbf{Prerequisites:} Knowledge(Planes) 10, must be able to cast a spell of the [calling] subtype

\textbf{Benefits:} When you possess the True Name of a creature, you may summon it with a \textit{Summon Monster} spell. The version of the \textit{Summon Monster} spell used must equal half their CR. For all effects, this spell is a summoning spell, and functions as if the creature were a summoned monster, but if killed the creature is dead as normal and cannot be summoned again until it is returned from the dead.

%%%
\featentry{Child Necromancer}
%%%

An obsession with death and experimentation with necromancy early in your childhood perverted your body and blossoming magical talent. As a result, your body never aged past childhood, and you are an adult in a child's body, magically powerful but physically weak.

\textbf{Prerequisite:} Caster level 1, must know at least one necromancy spell of each spell level you can cast.

\textbf{Benefit:} All Necromancy spells you cast are at +4 caster level, and you gain the effects of Weapon Finesse for all Necromancy touch attack spells you use (if you desire). You have -4 Strength, and appear to be a child despite your actual age category (this does not prevent penalties or bonuses from advancing in age categories, or stop the aging process). You are one size category smaller than normal for your race (do not further adjust ability modifiers). If you are a spontaneous caster, you may permanently exchange any spell known for any Necromancy spell you possess in written or scroll form. If you are a preparation caster, you may learn any Necromancy spell you possess in written or scroll form from any list, and you may not select Necromancy as a restricted school. These Necromancy spells may be from any list, can be exchanged at any time, and once gained are cast as spells of your spellcasting class. These spells remain as spells known even if you later lose this feat.

\textbf{Special:} This feat can only be taken at 1st level. If circumstances ever cause a character to no longer meet the prerequisites of this feat, they may choose any metamagic feat they qualify for to permanently replace this feat.

%%%
\featentry{Deflect Arrows}{[General] [Fighter]}
%%%

\textbf{Prerequisites:} Dex 13, \linkfeat{Improved Unarmed Strike}.

\textbf{Benefit:} You must have at least one hand free (holding nothing) to use this feat. Once per round when you would normally be hit with a ranged weapon, you may deflect it so that you take no damage from it. You must be aware of the attack and not flatfooted.

Attempting to deflect a ranged weapon doesn't count as an action. Unusually massive ranged weapons and ranged attacks generated by spell effects can't be deflected.

%%%
\featentry{Empower Spell-Like Ability}
%%%

\textbf{Prerequisite:} Spell-like ability at caster level 6th or higher.

\textbf{Benefit:} Choose one of the creature's spell-like abilities, subject to the restrictions below. The creature can use that ability as an empowered spell-like ability three times per day (or less, if the ability is normally usable only once or twice per day).

When a creature uses an empowered spell-like ability, all variable, numeric effects of the spell-like ability are increased by one half. Saving throws and opposed rolls are not affected. Spell-like abilities without random variables are not affected.

The creature can only select a spell-like ability duplicating a spell with a level less than or equal to half its caster level (round down) -2. For a summary, see the table in the description of the \linkfeat{Quicken Spell-Like Ability} feat. 

\textbf{Special:} This feat can be taken multiple times. Each time it is taken, the creature can apply it to a different one of its spell-like abilities.

%%%
\featentry{Eschew Materials}
%%%

\textbf{Benefit:} You can cast any spell that has a material component costing 1 gp or less without needing that component. (The casting of the spell still provokes attacks of opportunity as normal.) If the spell requires a material component that costs more than 1 gp, you must have the material component at hand to cast the spell, just as normal.

%%%
\featentry{Extra Turning}
%%%

\textbf{Prerequisite:} Ability to turn or rebuke creatures.

\textbf{Benefit:} Each time you take this feat, you can use your ability to turn or rebuke creatures four more times per day than normal.

If you have the ability to turn or rebuke more than one kind of creature each of your turning or rebuking abilities gains four additional uses per day.

\textbf{Normal:} Without this feat, a character can typically turn or rebuke undead (or other creatures) a number of times per day equal to 3 + his or her Charisma modifier.

\textbf{Special:} You can gain Extra Turning multiple times. Its effects stack. Each time you take the feat, you can use each of your turning or rebuking abilities four additional times per day.

%%%
\featentry{Fiend Cabalist}
%%%

You were trained in the mystic arts by a powerful fiend, and your magical power stems from a dark source.

\textbf{Prerequisite:} Caster level 1

\textbf{Benefit:} You gain Knowledge(planes) as a class skill, and all of your spells gain the [evil] subtype, and spells you cast and magic items you create radiate an evil aura equal to the strength of their normal magical aura. Any spells you cast that already have the Evil subtype gain a +4 caster level.

\textbf{Special:} This can only be taken at 1st level.

%%%
\featentry{Fleet of Foot}
%%%

\textbf{Prerequisites:} Dex 15, \linkfeat{Run}.

\textbf{Benefit:} When running or charging, you can make a single direction change of 90 degrees or less. You can't use this feat while wearing medium or heavy armor, or when carrying a medium or heavy load.  If you are charging, you must move in a straight line for 10 feet after the turn to maintain the charge.

%%%
\featentry{Flyby Attack}
%%%

\textbf{Prerequisite:} Fly speed.

\textbf{Benefit:} When flying, the creature can take a move action (including a dive) and another standard action at any point during the move. The creature cannot take a second move action during a round when it makes a flyby attack.

%%%
\featentry{Ghost Cut Technique}
%%%

Study of the ephemeral essence of incorporeal undead has taught you combat techniques that transcend the limitations of the flesh.

\textbf{Prerequisite:} Whispers of the Otherworld

\textbf{Benefit:} Each day, you can use the spell \textit{wraithstrike} as swift action spell-like ability a number of time equal to half your character level.

You also gain a +2 to initiative checks, a +4 to Move Silently checks, and Lifesight as a Special Quality.

%%%
\featentry{Great Shield Proficiency}
%%%

\textbf{Prerequisite:} Shield Proficiency.

\textbf{Benefit:} You can use a great shield and suffer only the standard penalties.

%%%
\featentry{Greater Manyshot}{[General] [Fighter]}
%%%

You are skilled at firing many arrows at once, even at different opponents.

\textbf{Prerequisites:} Dex 17, \linkfeat{Manyshot}, \linkfeat{Point Blank Shot}, \linkfeat{Rapid Shot}, base attack bonus +6.

\textbf{Benefit:} When you use the Manyshot feat, you can fire each arrow at a different target instead of firing all of them at the same target. You make a separate attack roll for each arrow, regardless of whether you fire them at separate targets or the same target. Your precision-based damage applies to each arrow fired, and, if you score a critical hit with more than one of the arrows, each critical hit deals critical damage.

%%%
\featentry{Greater Spell Focus}
%%%

Choose a school of magic to which you already have applied the Spell Focus feat.

\textbf{Benefit:} Add +1 to the Difficulty Class for all saving throws against spells from the school of magic you select. This bonus stacks with the bonus from Spell Focus.

\textbf{Special:} You can gain this feat multiple times. Its effects do not stack. Each time you take the feat, it applies to a new school of magic to which you already have applied the Spell Focus feat.

%%%
\featentry{Greater Spell Penetration}
%%%

\textbf{Prerequisite:} \linkfeat{Spell Penetration}.

\textbf{Benefit:} You get a +2 bonus on caster level checks (1d20 + caster level) made to overcome a creature's spell resistance. This bonus stacks with the one from Spell Penetration.

%%%
\featentry{Greater Teleport}
%%%

The extraplanar blood running through your veins allows you to use the signature travel methods of the outer planes.

\textbf{Prerequisite:} Outsider, character level 5th

\textbf{Benefit:} You may use \linkspell{Greater Teleport} at will as a spell-like ability. You may only transport yourself and 50 pounds of carried items.

%%%
\featentry{Heighten Spell-like Ability}
%%%

You can treat your spell-like abilities as more powerful spell effects.

\textbf{Benefit:} When you use a spell-like ability, you may use it as if it were of a higher than normal spell level. You may not raise a spell-like ability to in this fashion to an effective spell-level higher than half your character level.

%%%
\featentry{Hellscarred}
%%%

Having had your mind or body twisted by the essence of a fiend, you have gained some sensitivity and immunity to their power.

\textbf{Prerequisites:} Must have failed a saving throw to a spell or effect associated with a fiend, and cannot be a fiend or have any feats with the [Fiend] subtype.

\textbf{Benefits}: If you ever fail a save to a Special attack, Special Quality, or spell of a fiend, you may a reroll that save (once per save). This ability may be used a number of times per day equal to your Charisma modifier (minimum 1).

In addition, you may cast \textit{Detect Fiends} as a spell like ability at will: This spell functions as enlarged \linkspell{Detect Magic} (120 foot range), but it only detects the presence of fiends and their magical effects. This effect also cannot determine school of magic, but instead will indicate the race of the fiend (including subtype if appropriate).

%%%
\featentry{Hold The Line}
%%%

\textbf{Prerequisites:} \linkfeat{Horde Breaker}, base attack bonus +2.

\textbf{Benefit:} You may make an attack of opportunity against a charging opponent who enters an area you threaten.  Your attack of opportunity happens immediately before the charge attack is resolved.

%%%
\featentry{Hover}
%%%

\textbf{Prerequisite:} Fly speed.

\textbf{Benefit:} When flying, the creature can halt its forward motion and hover in place as a move action. It can then fly in any direction, including straight down or straight up, at half speed, regardless of its maneuverability.

If a creature begins its turn hovering, it can hover in place for the turn and take a full-round action. A hovering creature cannot make wing attacks, but it can attack with all other limbs and appendages it could use in a full attack. The creature can instead use a breath weapon or cast a spell instead of making physical attacks, if it could normally do so.

If a creature of Large size or larger hovers within 20 feet of the ground in an area with lots of loose debris, the draft from its wings creates a hemispherical cloud with a radius of 60 feet. The winds so generated can snuff torches, small campfires, exposed lanterns, and other small, open flames of non-magical origin. Clear vision within the cloud is limited to 10 feet. Creatures have concealment at 15 to 20 feet (20\% miss chance). At 25 feet or more, creatures have total concealment 
(50\% miss chance, and opponents cannot use sight to locate the creature).

Those caught in the cloud must succeed on a Concentration check (DC 10 + 1/2 creature's HD) to cast a spell.

%%%
\featentry{Improved Counterspell}
%%%

\textbf{Benefit:} When counterspelling, you may use a spell of the same school that is one or more spell levels higher than the target spell.

%%%
\featentry{Improved Critical}{[General] [Fighter]}
%%%

Choose one type of weapon.

\textbf{Prerequisite:} Proficient with weapon, base attack bonus +8.

\textbf{Benefit:} When using the weapon you selected, your threat range is doubled.

\textbf{Special:} You can gain Improved Critical multiple times. The effects do not stack. Each time you take the feat, it applies to a new type of weapon.

This effect doesn't stack with any other effect that expands the threat range of a weapon.

%%%
\featentry{Improved Flyby Attack}
%%%

\textbf{Prerequisite:} Fly speed, \linkfeat{Elusive Target}, \linkfeat{Flyby Attack}

\textbf{Benefit:} If the standard action taken by a creature during a round in which it uses Flyby Attack is a melee attack, the creature provokes no attacks of opportunity from moving out of squares threatened by its target.

%%%
\featentry{Improved Feint}{[General] [Fighter]}
%%%

\textbf{Prerequisites:} Int 13

\textbf{Benefit:} You can make a \linkskill{Bluff} check to feint in combat as a move action.

%%%
\featentry{Improved Initiative}{[General] [Fighter]}
%%%

\textbf{Benefit:} You get a +4 bonus on initiative checks.

%%%
\featentry{Improved Multiattack}
%%%

\textbf{Prerequisite:} Three or more natural weapons, \linkfeat{Multiattack}

\textbf{Benefit:} The creature's secondary attacks with natural weapons have no penalty. They still add only one-half the creature's Strength bonus, if any, to damage dealt.

%%%
\featentry{Improved Multiweapon Fighting}
%%%

\textbf{Prerequisites}: Dex 15, three or more arms, \linkfeat{Multiweapon Fighting}, base 
attack bonus +9.

\textbf{Benefit:} In addition to the single extra attack a creature gets with each extra weapon from Multiweapon Fighting, it gets a second attack with each extra weapon, albeit at a -5 penalty.

\textbf{Special:} This feat replaces the Improved Two-Weapon Fighting feat for creatures with more than two arms.

%%%
\featentry{Improved Natural Armor}
%%%

\textbf{Prerequisites:} Natural armor, Con 13.

\textbf{Benefit:} Your natural armor bonus increases by 1.

\textbf{Special:} You can gain this feat multiple times. Each time you take the feat your natural armor bonus increases by another point.

%%%
\featentry{Improved Natural Attack}
%%%

\textbf{Prerequisite:} Natural weapon, base attack bonus +4.

\textbf{Benefit:} Choose one of your natural attack forms. The damage for this natural weapon increases by one step, as if the creature's size had increased by one category: 1d2, 1d3, 1d4, 1d6, 1d8, 2d6, 3d6, 4d6, 6d6, 8d6, 12d6. 

A weapon or attack that deals 1d10 points of damage increases as follows: 1d10, 2d8, 3d8, 4d8, 6d8, 8d8, 12d8.

%%%
\featentry{Improved Shield Bash}{[General] [Fighter]}
%%%

\textbf{Prerequisite:} \linkfeat{Shield Proficiency}.

\textbf{Benefit:} When you perform a shield bash, you may still apply the shield's shield bonus to your AC.

%%%
\featentry{Improved Unarmed Strike}{[General] [Fighter]}
%%%

\textbf{Benefit:} You are considered to be armed even when unarmed  -- that is, you do not provoke attacks or opportunity from armed opponents when you attack them while unarmed. However, you still get an attack of opportunity against any opponent who makes an unarmed attack on you.

In addition, your unarmed strikes can deal lethal or nonlethal damage, at your option.

\textbf{Special:} A \linkclass{Monk} automatically gains Improved Unarmed Strike as a bonus feat at 1st level. She need not select it.

%%%
\featentry{Knockdown}
%%%

\textbf{Prerequisites:} Base attack bonus +2, \linkfeat{Improved Trip}, Str 15.

\textbf{Benefit:} Whenever you deal 10 or more points of damage to your opponent in melee, you make a trip attack as a free action against the same target.

%%%
\featentry{Manyshot}{[General] [Fighter]}
%%%

\textbf{Prerequisites:} Dex 17, \linkfeat{Point Blank Shot}, \linkfeat{Rapid Shot}, base attack bonus 
+6

\textbf{Benefit:} As a standard action, you may fire two arrows at a single opponent within 30 feet. Both arrows use the same attack roll (with a -4 penalty) to determine success and deal damage normally (but see Special).

For every five points of base attack bonus you have above +6, you may add one additional arrow to this attack, to a maximum of four arrows at a base attack bonus of +16. However, each arrow after the second adds a cumulative -2 penalty on the attack roll (for a total penalty of -6 for three arrows and -8 for four).

Damage reduction and other resistances apply separately against each arrow fired.

\textbf{Special:} Regardless of the number of arrows you fire, you apply precision-based damage only once. If you score a critical hit, only the first arrow fired deals critical damage; all others deal regular damage.

A 6th-level \linkclass{Ranger} who has chosen the archery combat style is treated as having Manyshot even if he does not have the prerequisites for it, but only when he is wearing light or no armor.

%%%
\featentry{Mobility}{[General] [Fighter]}
%%%

\textbf{Prerequisites:} Dex 13, \linkfeat{Dodge}.

\textbf{Benefit:} You get a +4 dodge bonus to Armor Class against attacks of opportunity caused when you move out of or within a threatened area. A condition that makes you lose your Dexterity bonus to Armor Class (if any) also makes you lose dodge bonuses.

Dodge bonuses stack with each other, unlike most types of bonuses.

%%%
\featentry{Mounted Archery}{[General] [Fighter]}
%%%

\textbf{Prerequisites:} \linkskill{Ride} 1 rank, \linkfeat{Mounted Combat}.

\textbf{Benefit:} The penalty you take when using a ranged weapon while mounted is halved: -2 instead of -4 if your mount is taking a double move, and -4 instead of -8 if your mount is running.

%%%
\featentry{Multiattack}
%%%

\textbf{Prerequisite:} Three or more natural attacks.

\textbf{Benefit:} The creature's secondary attacks with natural weapons take only a -2 penalty.

%%%
\featentry{Multiweapon Fighting}
%%%

\textbf{Prerequisites:} Dex 13, three or more hands.

\textbf{Benefit:} Penalties for fighting with multiple weapons are reduced by 2 with the primary hand and reduced by 6 with off hands.

\textbf{Special:} This feat replaces the \linkfeat{Two-Weapon Fighting} feat for creatures with more than two arms.

%%%
\featentry{Natural Spell}
%%%

\textbf{Prerequisites:} Wis 13, wild shape ability.

\textbf{Benefit:} You can complete the verbal and somatic components of spells while in a wild shape. You substitute various noises and gestures for the normal verbal and somatic components of a spell.

You can also use any material components or focuses you possess, even if such items are melded within your current form. This feat does not permit the use of magic items while you are in a form that could not ordinarily use them, and you do not gain the ability to speak while in a wild shape.

%%%
\featentry{Plant Control}
%%%

\textbf{Prerequisites:} \linkfeat{Plant Defiance}, ability to cast \linkspell{Speak with Plants}.

\textbf{Benefit:} You can rebuke or command plant creatures as an evil cleric rebukes undead. To command a plant, you must be able to speak with it via a \linkspell{Speak with Plants} effect, though it may reply mentally if desired. This ability is usable a total number of times per day equal to 3 + your Charisma modifier. You use your highest caster level to determine the level at which you rebuke plants.

%%%
\featentry{Plant Defiance}
%%%

\textbf{Prerequisite:} Ability to cast \linkspell{Detect Animals or Plants}.

\textbf{Benefit:} You can turn (but not destroy) plant creatures as a good cleric turns undead. When determining the result of a turning attempt, treat all destruction results as normal turning. Treat immobile plant creatures as creatures unable to flee. This ability is usable a total number of times per day equal to 3 + your Charisma modifier. You use your highest caster level to determine the level at which you turn plants.

%%%
\featentry{Power Critical}{[General] [Fighter]}
%%%

\textbf{Prerequisites:} \linkfeat{Weapon Focus} (chosen weapon), base attack bonus +4

\textbf{Benefit:} When using the weapon you selected, you gain a +4 bonus on the roll to confirm a threat.

\textbf{Special:} You can gain Power Critical multiple times. Each time you take the feat, it may be with a different weapon or the same weapon.  If you take it with the same weapon, the effects of the feats stack.

%%%
\featentry{Product of Infernal Dalliance}
%%%

One of your recent ancestors mated with an infernal creature, and now the tainted blood of a Lower Planar creature flows in your veins. Though you can resist the call of your evil heritage, it manifests itself in an inheritance of fiendish power.

\textbf{Benefits:} You may take any feat with the [Fiend] subtype. In addition, you radiate faint evil, have either two claws or one bite natural weapon, and have Cold Resistance 5 or Fire Resistance 5. When this feat is gained, you also gain the [Devil], [Demon], [Nokoloth], or [Dezabi] subtype.

\textbf{Special:} Can only be taken at 1st level.

%%%
\featentry{Quicken Spell-Like Ability}
%%%

\textbf{Prerequisite:} Spell-like ability at caster level 10th or higher.

\textbf{Benefit:} Choose one of the creature's spell-like abilities, subject to the restrictions described below. The creature can use that ability as a quickened spell-like ability three times per day (or less, if the ability is normally usable only once or twice per day).

Using a quickened spell-like ability is a swift action that does not provoke an attack of opportunity. The creature can perform another action -- including the use of another spell-like ability -- in the same round that it uses a quickened spell-like ability. The creature may use only one quickened spell-like ability per round.

The creature can only select a spell-like ability duplicating a spell with a level less than or equal to half its caster level (round down) -4. For a summary, see the table below.

In addition, a spell-like ability that duplicates a spell with a casting time greater than 1 full round cannot be quickened.

\textbf{Normal:} Normally the use of a spell-like ability requires a standard action and provokes an attack of opportunity unless noted otherwise.

\textbf{Special:} This feat can be taken multiple times. Each time it is taken, the creature can apply it to a different one of its spell-like abilities.

\begin{basictable}{Empower and Quicken Spell-Like Ability}{c c c}
\textbf{Spell Level} & \textbf{Caster Level to Empower} & \textbf{Caster Level to Quicken}\\
0th & 4th & 8th\\
1st & 6th & 10th\\
2nd & 8th & 12th\\
3rd & 10th & 14th\\
4th & 12th & 16th\\
5th & 14th & 18th\\
6th & 16th & 20th\\
7th & 18th & --\\
8th & 20th & --\\
9th & -- & --\\
\end{basictable}

%%%
\featentry{Rapid Shot}{[General] [Fighter]}
%%%

\textbf{Prerequisites:} Dex 13, \linkfeat{Point Blank Shot}.

\textbf{Benefit:} You can get one extra attack per round with a ranged weapon. The attack is at your highest base attack bonus, but each attack you make in that round (the extra one and the normal ones) takes a -2 penalty. You must use the full attack action to use this feat.

%%%
\featentry{Rapid Reload}{[General] [Fighter]}
%%%

Choose a type of crossbow (hand, light, or heavy).

\textbf{Prerequisite:} Weapon Proficiency (crossbow type chosen).

\textbf{Benefit:} The time required for you to reload your chosen type of crossbow is reduced to a free action (for a hand or light crossbow) or a move action (for a heavy crossbow). Reloading a crossbow still provokes an attack of opportunity.

If you have selected this feat for hand crossbow or light crossbow, you may fire that weapon as many times in a full attack action as you could attack if you were using a bow.

\textbf{Special:} You can gain Rapid Reload multiple times. Each time you take the feat, it applies to a new type of crossbow.

%%%
\featentry{Run}
%%%

\textbf{Benefit:} When running, you move five times your normal speed (if wearing medium, light, or no armor and carrying no more than a medium load) or four times your speed (if wearing heavy armor or carrying a heavy load). If you make a jump after a running start (see the \linkskill{Jump} skill description), you gain a +4 bonus on your Jump check. While running, you retain your Dexterity bonus to AC.

%%%
\featentry{Shield Proficiency}
%%%

\textbf{Benefit:} You can use a shield and take only the standard penalties.

%%%
\featentry{Shot On The Run}{[General] [Fighter]}
%%%

\textbf{Prerequisites:} Dex 13, \linkfeat{Elusive Target}, \linkfeat{Point Blank Shot}, base attack bonus +4.

\textbf{Benefit:} When using the attack action with a ranged weapon, you can move both before and after the attack, provided that your total distance moved is not greater than your speed.

%%%
\featentry{Skill Focus}
%%%

\textbf{Benefit:} Choose a skill, you get a +3 Feat bonus on all checks involving that skill.

\textbf{Special:} You can gain this feat multiple times. Its effects do not stack. Each time you take the feat, it applies to a new skill.

%%%
\featentry{Snatch}
%%%

\textbf{Prerequisite:} Size Huge or larger.

\textbf{Benefits:} The creature can choose to start a grapple when it hits with a claw or bite attack, as though it had the improved grab special attack. If the creature gets a hold on a creature three or more sizes smaller, it squeezes each round for automatic bite or claw damage. A snatched opponent held in the creature's mouth is not allowed a Reflex save against the creature's breath weapon, if it has one.

The creature can drop a creature it has snatched as a free action or use a standard action to fling it aside. A flung creature travels 1d6 x 10 feet, and takes 1d6 points of damage per 10 feet traveled. If the creature flings a snatched opponent while flying, the opponent takes this amount or falling damage, whichever is greater.

%%%
\featentry{Snatch Arrows}{[General] [Fighter]}
%%%

\textbf{Prerequisites:} Dex 15, \linkfeat{Deflect Arrows}, \linkfeat{Improved Unarmed Strike}.

\textbf{Benefit:} When using the Deflect Arrows feat you may catch the weapon instead of just deflecting it. Thrown weapons can immediately be thrown back at the original attacker (even though it isn't your turn) or kept for later use.

You must have at least one hand free (holding nothing) to use this feat.

%%%
\featentry{Spell Focus}
%%%

\textbf{Benefit:} Choose a school of magic. Add +1 to the Difficulty Class for all saving throws against spells from the school of magic you select.

\textbf{Special:} You can gain this feat multiple times. Its effects do not stack. Each time you take the feat, it applies to a new school of magic.

%%%
\featentry{Spell Mastery}
%%%

\textbf{Prerequisite:} \linkclass{Wizard} level 1st.

\textbf{Benefit:} Each time you take this feat, choose a number of spells equal to your Intelligence modifier that you already know. From that point on, you can prepare these spells without referring to a spellbook.

%%%
\featentry{Spell Penetration}
%%%

\textbf{Benefit:} You get a +2 bonus on caster level checks (1d20 + caster level) made to overcome a creature's spell resistance.

%%%
\featentry{Spirited Charge}{[General] [Fighter]}
%%%

\textbf{Prerequisites:} \linkskill{Ride} 1 rank, \linkfeat{Mounted Combat}, \linkfeat{Ride-by Attack}.

\textbf{Benefit:} When mounted and using the charge action, you deal double damage with a melee weapon (or triple damage with a lance).

%%%
\featentry{Stunning Fist}{[General] [Fighter]}
%%%

\textbf{Prerequisites:} Dex 13, Wis 13, \linkfeat{Improved Unarmed Strike}, base attack bonus 
+8.

\textbf{Benefit:} You must declare that you are using this feat before you make your attack roll (thus, a failed attack roll ruins the attempt). Stunning Fist forces a foe damaged by your unarmed attack to make a Fortitude saving throw (DC 10 + 1/2 your character level + your Wis modifier), in addition to dealing damage normally. A defender who fails this saving throw is stunned for 1 round (until just before your next action). A stunned character can't act, loses any Dexterity bonus to AC, and takes a -2 penalty to AC. You may attempt a stunning attack once per day for every four levels you have attained (but see Special), and no more than once per round. Constructs, oozes, plants, undead, incorporeal creatures, and creatures immune to critical hits cannot be stunned.

\textbf{Special:} A monk who selects this feat may attempt a stunning attack a number of times per day equal to her monk level, plus one more time per day for every four levels she has in classes other than monk.

%%%
\featentry{Stand Still}
%%%

You can prevent foes from fleeing or closing.

\textbf{Prerequisite:} Str 13.

\textbf{Benefit:} When a foe's movement out of a square you threaten grants you an attack of opportunity, you can give up that attack and instead attempt to stop your foe in his tracks. Make your attack of opportunity normally. If you hit your foe, he must succeed on a Reflex save against a DC of 10 + your damage roll (the opponent does not actually take damage), or immediately halt as if he had used up his move actions for the round.

Since you use the Stand Still feat in place of your attack of opportunity, you can do so only a number of times per round equal to the number of times per round you could make an attack of opportunity (normally just one).

\textbf{Normal:} Attacks of opportunity cannot halt your foes in their tracks.

%%%
\featentry{Trample}{[General] [Fighter]}
%%%

\textbf{Prerequisites:} \linkskill{Ride} 1 rank, \linkfeat{Mounted Combat}.

\textbf{Benefit:} When you attempt to overrun an opponent while mounted, your target may not choose to avoid you. Your mount may make one hoof attack against any target you knock down, gaining the standard +4 bonus on attack rolls against prone targets.

%%%
\featentry{Wingover}
%%%

\textbf{Prerequisite:} Fly speed.

\textbf{Benefits:} A flying creature with this feat can change direction quickly once each round as a free action. This feat allows it to turn up to 180 degrees regardless of its maneuverability, in addition to any other turns it is normally allowed. A creature cannot gain altitude during a round when it executes a wingover, but it can dive.

The change of direction consumes 10 feet of flying movement.
