%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Item Creation Feats}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

These feats augment your ability to create magical items using the \linkskill{Craft} skill.

%%%
\featentry{Scribe Scroll}{[Item Creation]}
%%%

\textbf{Benefit:} When crafting scrolls, a failed Craft check doesn't ruin any of your materials.

%%%
\featentry{Brew Potion}{[Item Creation]}
%%%

\textbf{Benefit:} When crafting potions, a failed Craft check doesn't ruin any of your materials. You can always craft a \textit{Cure} spell into a potion, even if you don't know the spell in question, as long as the spell level of the \textit{Cure} spell is no more than half your own level.

%%%
\featentry{Craft Magical Arms and Armor}{[Item Creation]}
%%%

\textbf{Benefit:} When crafting weapons, armor, shields, or the magical portions of any such items, a failed craft check does not ruin any of your materials. Further, you count as though you could cast any spell on the Cleric or Wizard spell list with a spell level of no more than half of your own level for fulfilling spell requirements when creating magical weapons, armor, and shields.

%%%
\featentry{Craft Wondrous Item}{[Item Creation]}
%%%

\textbf{Benefit:} A wondrous item is any permanent magical item that isn't a weapon, armor, or shield. When crafting the magical portion of a wondrous item, such as a magic belt or cloak, a failed craft check does not ruin any of your materials. Further, you count as though you could cast any spell on the Cleric or Wizard spell list with a spell level of no more than half of your own level for fulfilling spell requirements when creating wondrous items.