%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Leadership Feats}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Not all games allow Leadership feats, because all the additional Followers and the Cohort can be a lot to keep track of. If a Character has more than one Leadership feat they still only gain a single set of Followers, and they can still only have a single Cohort. However, they can mix their Follower and Cohort selection from among any allowed to them by their feats (and/or class features).

Cohorts and Followers can't ever take Leadership feats of their own.

%%%
\featentry{Army of Demons}{[Leadership] [Skill] [Fiend] [Celestial]}
%%%

You have an army of planar crazy crap. This feat scales to your Knowledge: Planes skill.

\textbf{Benefits:} You have a Command Rating equal to your Knowledge: Planes ranks divided by five (round up).

\textbf{4:} You can muster a group of followers. Your leadership score is your ranks in Knowledge: Planes plus your Charisma mod. These followers can and must be outsiders.

\textbf{9:} Your followers swell in number to that of an army.

\textbf{14:} You own a planar stronghold.

\textbf{19:} Your allies gain a +2 morale bonus to all saving throws if they can see you and you are within medium range.

%%%
\featentry{Bureaucrat}{[Leadership] [Skill]}
%%%

You have a functioning guild that makes stuff for you and gives you money. This feat scales to your Appraise skill.

\textbf{Benefits:} You draw an income for working as an administrator, getting 1 GP/week per rank in Appraise.

\textbf{4:} You can muster a group of followers. Your leadership score is your ranks in Appraise plus your Intelligence modifier. These followers all have profession and craft skills.

\textbf{9:} You get your own Stronghold.

\textbf{14:} You get a +2 bonus to profit checks.

\textbf{19:} Your guild goes planar, your number of followers swell to the size of an army and their ranks start filling up with producers and managers from other planes of existence.

%%%
\featentry{Command}{[Leadership] [Combat]}
%%%

You lead tiny men.

\textbf{Benefits:} You have a Command Rating equal to your Base Attack Bonus divided by five (round up).

\textbf{+1:} You can muster a group of followers. Your leadership score is your Base Attack Bonus plus your Charisma Modifier.

\textbf{+6:} You are able to delegate command to a loyal cohort. A cohort is an intelligent and loyal creature with a CR at least 2 less than your character level. Cohorts gain levels when you do.

\textbf{+11:} With a Swift Action you may rally troops, allowing all allies within medium range of yourself to reroll their saves vs. Fear and gain a +2 Morale Bonus to attack and damage rolls for 1 minute. This is a language-dependent ability that may be used an unlimited number of times.

\textbf{+16:} Your allies gain a +2 morale bonus to all saving throws if they can see you and you are within medium range.

%%%
\featentry{Craft Construct} [Skill] [Leadership] [Item Creation]
%%%
You can make an army of automatons that faithfully follow your orders without stopping to think or other troublesome things like that.

\textbf{Benefit:} When creating a Construct, a failed Craft check doesn't ruin any of your materials. You can build and animate constructs allowed to you by this feat using Gold Economy materials instead of Wish Economy materials, and the price is the CR squared times 75 gp (or 50gp for CR 1/2 followers). Making such a construct takes an hour of work. Instead of paying actual money, you can spend 1 extra day for each 100gp of materials that you would have had to pay for and just use whatever local materials are sitting around in the open. Unintelligent constructs from this feat crumble after a number of days equal to your level if you die or lose control of them for any other reason.

\textbf{4:} You can make a large number of Golems out of different sorts of materials. They count as your followers using the normal rules, so their CRs are also normal. Your leadership score is equal to your ranks in Craft plus your Intelligence Bonus. Very low CR golems are kinda like normal golems but they're made out exceptionally terrible materials, like paper, bread, or straw.

\textbf{9:} You gain an especially powerful construct that's your Cohort. Once per month you can give a construct that you animate the (Positronic) subtype for free. This gives it an Intelligence score with all the normal benefits (skill points, being able to think, able to have class levels, etc), but makes it vulnerable to Mind-Affecting things in the process.

\textbf{14:} All of your Constructs (both Followers and Cohort) are mystically linked to you, and as long as they remain under your command they gain Energy Resistance equal to your ranks in Craft to one energy type. Changing which energy type involves altering your own aura to change the mystic link, an alchemical process that takes one hour to complete.

\textbf{19:} Your limit on construct followers increases to that of an army. Also, your Construct Cohort gets +2 to all of its saves.

%%%
\featentry{Leadership}{[Leadership] [Skill]}
%%%

You convince people that obeying you is a good career move. (This is a Skill feat that scales with your ranks in Diplomacy.)

\textbf{Benefits:} You can awe even strangers and enemies into following your orders. With a DC 20 Diplomacy check, you can use command as a spell-like ability, with save DC equal to 10 + half your character level + your Cha modifier.

\textbf{4:} Your natural talent for leaderships attracts followers. Your leadership score is equal to your ranks in Diplomacy plus your Charisma modifier.

\textbf{9:} You persuade someone that you are so awesome that they should follow you around all the time, acquiring a cohort. A cohort is an intelligent and loyal creature with a CR at least 2 less than your character level. Cohorts gain levels when you do.

\textbf{14:} Your natural majesty stirs guilt in those who refuse your demands. With a DC 30 Diplomacy check, you can use geas as a spell-like ability, but it offers a Will save at DC 10 + half your character level + your Cha modifier.

\textbf{19:} You command the loyalty of armies -- even opposing ones. With a DC 40 Diplomacy check, you can use greater command as a spell-like ability, with save DC equal to 10 + half your character level + your Cha modifier and effective caster level equal to your bonus on Diplomacy checks.

%%%
\featentry{Lord of Death}{[Leadership] [Skill] [Necromantic]}
%%%

A whole bunch of skeletons and crap show up to fight under your tattered banner.

\textbf{Benefits:} You have a Command Rating equal to your ranks in Knowledge Religion divided by five (round up).

\textbf{4:} You can muster a group of followers. Your leadership score is your ranks in Knowledge Religion plus your Wisdom modifier. Your followers are all mindless Undead. You don't make them or anything, they just show up.

\textbf{9:} You are able to delegate command to a loyal cohort. Your cohort is an intelligent and loyal Undead creature with a CR 2 less than your character level. Cohorts gain levels when you do.

\textbf{14:} Your followers swell in number to that of an army.

\textbf{19:} Your allies gain energy resistance to Positive Energy equal to your level while they are within line of sight of you.

%%%
\featentry{Master Artisan}{[Leadership][Skill]}
%%%

You're so good at putting things together that it leaves people speechless. They follow you around in the hopes that they can see you work more wonders. (This is a Skill feat that scales with your ranks in Craft.)

\textbf{Benefit:} You get a +3 feat bonus to Craft checks

\textbf{4:} You attract followers, they probably work in your shop or help you with Aid Another checks or something. Your Leadership score is equal to your ranks in craft plus your Intelligence Bonus.

\textbf{9:} You attract an artisan's apprentice. They're exactly like a cohort, just with a special title.

\textbf{14:} You can cast \linkspell{Fabricate} three times per day.

\textbf{19:} When you repair a broken magical item, you also can also restore the magical portion of the broken item. This takes you no additional time and no additional materials. You cannot restore artifacts with this ability.

%%%
\featentry{Master of Terror}{[Leadership] [Skill]}
%%%

You scare people so bad they follow you around hoping you won't hurt them. (This is a Skill feat that scales with your ranks in Intimidate.)

\textbf{Benefits:} Whenever you use Intimidate in combat, it affects everyone within 30 feet of you.

\textbf{4:} You gain followers. Your leadership score is equal to your ranks in Intimidate plus your Charisma modifier.

\textbf{9:} You gain a cohort who enjoys frightening your underlings almost as much as you do. A cohort is an intelligent and loyal creature with a CR at least 2 less than your character level. Cohorts gain levels when you do.

\textbf{14:} You gain the frightful presence ability. When you speak or attack, enemies within 30 feet of you must succeed on a Will save (DC 10 + your character level + your Cha modifier) or become shaken for 5d6 rounds. An opponent that succeeds on its saving throw is immune to your frightful presence for 24 hours.

\textbf{19:} Your opponents take a -2 morale penalty to saving throws if they can see you and you are within medium range (based on your character level).

%%%
\featentry{Monster Rancher}{[Leadership] [Skill]}
%%%

You can breed and train a large number of crazy beasts. This feat scales to your ranks in Handle Animal.

\textbf{Benefits:} You can use Handle Animal as if it were Diplomacy when dealing with Magical Beasts and Dragons. You can do similarly with Aberrations and Plants with an Intelligence Score that is less than 9.

\textbf{4:} You can muster a group of followers. Your leadership score is your ranks in Handle Animal plus any synergy bonuses you gt to that skill. Your followers can, and must be monsters.

\textbf{9:} You have a loyal cohort that is a monster of some kind. A cohort is an intelligent and loyal creature with a CR at least 2 less than your character level. Cohorts gain levels when you do.

\textbf{14:} You know what any monster is unless it is disguised by illusion, and you can look up its stat line in the appropriate monster book when devising your strategies.

\textbf{19:} Once per day, you can reroll a saving throw allowed by a Supernatural Ability.

%%%
\featentry{Tyrant}{[Leadership] [Skill]}
%%%
You push people around and get larger and larger groups trapped in the iron gauntlet of your brutal rule. This feat scales with your ranks in Intimidate

\textbf{Benefits:} You inspire such terror that creatures you intimidate continue to act intimidated after you leave, too afraid to raise their voice in defiance even after you have apparently left them far behind.

\textbf{4:} You can muster a group of followers. Your leadership score is your ranks in Intimidate plus your Strength modifier.

\textbf{9:} Your followers swell in number to that of an army.

\textbf{14:} Your mere presence inspires fear and can break a battle. Enemies with more than 5 hit dice less than you do must make a Will save (DC 10 + half Level + Strength Modifier) of flee in panic. This is a [Fear] effect.

\textbf{19:} Your presence causes despair in even brave opponents. All enemies within 30' of your suffer a -2 Morale penalty to Willpower saves.
