%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Metamagic Feats}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Metamagic feats alter a spells that you cast. If you prepare spells then you must choose to apply a metamagic feat or not as you prepare the spell. If you spontaneously cast spells then you choose to apply the metamagic feat or not at the time of casting as a free action.

Metamagic feats all have an effective increase in spell level associated with them. This causes the spell to require a higher level slot than normal, but for all other purposes (Save DC, Concentration check DCs, ability to penetrate a \linkspell{Globe of Invulnerability}, etc) the spell counts as its original level.

%%%
\featentry{Disguise Spell}{[Metamagic]}
%%%

\textbf{Prerequisites:} Bardic music, \linkskill{Perform} 12 ranks.

\textbf{Benefit:} You have mastered the art of casting spells unobtrusively, mingling verbal and somatic components into its music and performances so that others rarely catch you in the act of casting a spell. Like a silent, stilled spell, a disguised spell can't be identified through \linkskill{Spellcraft}. Your performance is obvious to everyone in the vicinity, but the fact that you are casting a spell isn't. Unless the spell visibly emanates from you or observers have some other means of determining its source, they don't know where the effect came from. A disguised spell uses up a spell slot one level higher than the spell's actual level.

%%%
\featentry{Empower Spell}{[Metamagic]}
%%%

\textbf{Benefit:} All variable, numeric effects of an empowered spell are increased 
by one-half.

Saving throws and opposed rolls are not affected, nor are spells without random variables. An empowered spell uses up a spell slot two levels higher than the spell's actual level.

%%%
\featentry{Energy Substitution}{[Metamagic]}
%%%

\textbf{Prerequisites:} Any other metamagic feat, \linkskill{Knowledge} (arcana) 5 ranks.

\textbf{Benefit:} You choose one type of energy: acid, cold, electricity, fire, or sonic. When employing a spell with the acid, cold, electricity, fire, or sonic designator, you can modify the spell to use your chosen type of energy instead. The altered spell uses a spell slot of the spell's normal level.

The altered spell works normally in all respects except the type of damage dealt. 

\textbf{Special:} You can gain this feat multiple times. Each time the feat applies to a different type of energy.

%%%
\featentry{Enlarge Spell}{[Metamagic]}
%%%

\textbf{Benefit:} You can alter a spell with a range of close, medium, or long to increase its range by 100\%. An enlarged spell with a range of close now has a range of 50 ft. + 5 ft./level, while medium-range spells have a range of 200 ft. + 20 ft./level and long-range spells have a range of 800 ft. + 80 ft./level. An enlarged spell uses up a spell slot one level higher than the spell's actual level.

Spells whose ranges are not defined by distance, as well as spells whose ranges are not close, medium, or long, do not have increased ranges.

%%%
\featentry{Extend Spell}{[Metamagic]}
%%%

\textbf{Benefit:} An extended spell lasts twice as long as normal. A spell with a duration of concentration, instantaneous, or permanent is not affected by this feat. An extended spell uses up a spell slot one level higher than the spell's actual level.

%%%
\featentry{Heighten Spell}{[Metamagic]}
%%%

\textbf{Benefit:} A heightened spell has a higher spell level than normal (up to a maximum of 9th level). Unlike other metamagic feats, Heighten Spell actually increases the effective level of the spell that it modifies. All effects dependent on spell level (such as saving throw DCs and ability to penetrate a \linkspell{Lesser Globe of Invulnerability}) are calculated according to the heightened level. The heightened spell is as difficult to prepare and cast as a spell of its effective level.

%%%
\featentry{Maximize Spell}{[Metamagic]}
%%%

\textbf{Benefit:} All variable, numeric effects of a spell modified by this feat are maximized. Saving throws and opposed rolls are not affected, nor are spells without random variables. A maximized spell uses up a spell slot three levels higher than the spell's actual level.

An empowered, maximized spell gains the separate benefits of each feat: the maximum result plus one-half the normally rolled result.

%%%
\featentry{Persistant Spell}{[Metamagic]}
%%%

\textbf{Prerequisite:} \linkfeat{Extend Spell}.

\textbf{Benefit:} A persistent spell has a duration of 24 hours. The persistent spell must have a personal range or a fixed range. Spells of instantaneous duration cannot be affected by this feat, nor can spells whose effects are discharged.  You need not concentrate on spells such as \linkspell{Detect Magic} or \linkspell{Detect Thoughts} to be aware of the mere presence of absence of the things detected, but you must still concentrate to gain additional information as normal.  Concentration on such a spell is a standard action that does not provoke an attack of opportunity. 

A persistent spell uses up a spell slot six levels higher than the spell's actual level.

%%%
\featentry{Quicken Spell}{[Metamagic]}
%%%

\textbf{Benefit:} Casting a quickened spell is a swift action. You can perform another action, even casting another spell, in the same round as you cast a quickened spell. You may cast only one quickened spell per round. A spell whose casting time is more than 1 full round action cannot be quickened. A quickened spell uses up a spell slot four levels higher than the spell's actual level. Casting a quickened spell doesn't provoke an attack of opportunity.

%%%
\featentry{Reach Spell}{[Metamagic]}
%%%

\textbf{Benefit:} You may cast a spell that normally has a range of touch at any distance up to 30 feet. The spell effectively becomes a ray, so you must succeed at a ranged touch attack to bestow the spell upon the recipient. A reach spell uses up a spell slot two levels higher than the spell's actual level.

%%%
\featentry{Repeat Spell}{[Metamagic]}
%%%

\textbf{Prerequisites:} Any other metamagic feat.

\textbf{Benefit:} A repeated spell is automatically cast again at the beginning of your next round of actions. No matter where you are, the secondary spell originates from the same location and affects the same area as the primary spell. If the repeated spell designates a target, the secondary spell retargets the same target if the target is within 30 feet of its original position; otherwise the secondary spell fails to go off. A repeated spell uses up a spell slot three levels higher than the spell's actual level. Repeat Spell cannot be used on spells with a range of touch.

%%%
\featentry{Sacred Spell}{[Metamagic]}
%%%

\textbf{Benefit:} Half of the damage dealt by a sacred spell results directly from divine power and is therefore not subject to being reduced by protection from elements or similar magic. The other half of the damage dealt by the spell is as normal. A sacred spell uses up a spell slot two levels higher than the spell's actual level. Only divine spells can be cast as sacred spells.

%%%
\featentry{Silent Spell}{[Metamagic]}
%%%

\textbf{Benefit:} A silent spell can be cast with no verbal components. Spells without verbal components are not affected. A silent spell uses up a spell slot one level higher than the spell's actual level.

\textbf{Special:} \linkclass{Bard} spells cannot be enhanced by this metamagic feat.

%%%
\featentry{Still Spell}{[Metamagic]}
%%%

\textbf{Benefit:} A stilled spell can be cast with no somatic components.

Spells without somatic components are not affected. A stilled spell uses up a spell slot one level higher than the spell's actual level.

%%%
\featentry{Subdual Substitution}{Megamagic}
%%%

\textbf{Prerequisites:} Any other metamagic feat, \linkskill{Knowledge} (arcana) 5 ranks.

\textbf{Benefit:} When employing a spell with the acid, cold, electricity, fire, or sonic designator, you can modify the spell to deal subdual damage instead of the indicated type of energy damage. The altered spell uses a spell slot of the spell's normal level.

The altered spell works normally in all respects except the type of damage dealt.

%%%
\featentry{Widen Spell}{[Metamagic]}
%%%

\textbf{Benefit:} You can alter a burst, emanation, line, or spread shaped spell to increase its area. Any numeric measurements of the spell's area increase by 100\%.A widened spell uses up a spell slot three levels higher than the spell's actual level.

Spells that do not have an area of one of these four sorts are not affected by this feat.
