%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Necromantic Feats}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Any feat with the [Necromatic] tag is a necromantic creation feat. This means that it is merely one part of the dark tradition of necromancy; other means such as necromancy spells or other effects can create these undead, but this an easy path for the serious Necromancer. One trait shared by these feats is that each feat has a separate control pool for the undead it creates. For example, if a necromancer has the Path of Blood feat and the A Feast Unknown feat, he may control up to his unmodified charisma modifier in vampires or vampire spawn in addition to controlling up to his unmodified charisma modifier in ghouls. It is a move action to give commands any one undead creature. Any undead controlled by this feat cannot create undead or use the Spawn Undead ability.

The rituals are inexpensive, but require the flesh and blood of intelligent creatures as well as living creatures or fresh corpses as subjects. Any additional costs or conditions are listed in the individual feat. These rites take 1 hour per CR of the creature created, and can only be performed at night or in a location that has never been touched by the sun (such as a deep cave). The maximum CR of an undead creature created with these rites is two less than the creator's character level.

Materials to create any undead always cost at least 25 gp per hit die. Creating undead by these method generally requires at least an hour.

%%%
\featentry{A Feast Unknown}{[Necromantic]}
%%%

You have partaken of the feast most foul and count yourself a king among the ghouls.

\textbf{Prerequisite:} You must have consumed the rapidly cooling flesh of an intelligent mortal creature. Must be evil.

\textbf{Benefit:} You can create Ghouls or Ghasts from any dying person (at -1 to -9 hps). Any undead you create have the Scent special quality.

In addition, any time you completely consume the flesh of a sentient creature, you regain 5 hps per HD.

You automatically control up to your Charisma modifier in undead created by this feat, but no undead can have a CR greater than your character level.

%%%
\featentry{Devil Preparation}
%%%

By learning dark culinary techniques, you have learned to consume the flesh of devils, demons, and other infernals, absorbing their taint and some of their power.

\textbf{Prerequisite:} \linkfeat{A Feast Unknown}, character level 10, must have eaten the flesh of a Devil or Demon.

\textbf{Benefit:} You gain the ability to cast one spell from the Half-Fiend template per day as a spell-like ability (limited by your HD on the Half-fiend chart). In addition, all spells from the Evil Domain are considered spells known for you, you gain a +2 to Intimidate checks, and you can choose to count as a Demon or Devil for the effects of spells, magic items, or prerequisites for feats or prestige classes.

%%%
\featentry{Fairy Eater}
%%%

By consuming the flesh of fairies, you have absorbed a fraction of their magic.

\textbf{Prerequisite:} \linkfeat{A Feast Unknown}, must have eaten the flesh of a creature with the Fey type.

\textbf{Benefit:} All figments and glamers you cast have their duration extended by two rounds. In addition, all spells from the Trickery Domain are considered spells known for you, you gain a +4 to Disguise checks, and you can choose to count as a Fey for the effects of spells, magic items, or prerequisites for feats or prestige classes.

%%%
\featentry{Heavenly Desserts}
%%%

By gorging on the sweet flesh of angels, you have digested a portion of their divine essence.

\textbf{Prerequisite:} \linkfeat{A Feast Unknown}, character level 10, must have eaten the flesh of an Angel, Archon, Eladrin, or Deva.

\textbf{Benefit:} You gain the ability to cast one spell from the Half-Celestial template per day as a spell-like ability (limited by your HD on the Half-Celestial chart). In addition, all spells from the Gluttony Domain are considered spells known for you, you gain a +2 to Diplomacy checks, and you can choose to count as Good for the effects of spells or magic items.

%%%
\featentry{Path of Blood}{[Necromantic]}
%%%

You have learned the dark and selfish rites that create vampires, the legendary immortal blood drinkers of the night.

\textbf{Prerequisite:} Character level 5

\textbf{Benefit:} You can create Vampires and Vampire Spawn. Your unintelligent undead heal fully at the next sunset following them killing a living creature with a piercing or slashing attack. A spellcaster with this feat has access to any spell with a [blood] component.

You automatically control up to your unmodified Charisma modifier in undead created by this feat, but no undead can have a CR greater than two less than your character level.

%%%
\featentry{Blood Painter}
%%%

By painting magical diagrams out of your own blood, you can spontaneously cast spells using only your own life energy. This is of special use to casters who prepare spells, or to casters who have run out of spells.

\textbf{Prerequisite:} \linkfeat{Path of Blood}, Caster level 5, Spellcraft 4 ranks

\textbf{Benefit:} At any time, a caster with this feat can cast any spell he knows by painting a magical diagram on a flat 10' by 10' surface. This takes one minute per spell level, and deals two points of Constitution damage per spell level to the caster (or loses a like amount of Blood Pool if he has one). If the caster's current Con or Blood Pool is less than double the spell's level, the spell cannot be cast.

Any spells cast with this feat are Spell-like Abilities.

%%%
\featentry{Body Assemblage}{[Necromantic]}
%%%

The discarded husks of life are nothing more than a building material to you.

\textbf{Prerequisite:} Caster Level 1, ability to cast 1st level spells of the Necromancy school.

\textbf{Benefit:} You may create skeletons and zombies that serve you alone.

You automatically control up to your unmodified Charisma modifier in undead created by this feat, but no undead can have a CR greater than two less than your character level.

\textbf{Special:} A first or second level character can create undead less than their own CR, but each undead creature counts as two for control purposes.

%%%
\featentry{Feed the Dark Gods}{[Necromantic]}

You have attracted the attention of dark gods and demon lords, and they are willing to grant dark life to your creations in exchange for pain and power.

\textbf{Prerequisite:} Any two necromantic feats, character level 7, 10 ranks in Knowledge (Religion)

\textbf{Benefit:} You may create any undead creature through the art of sacrifice. For every CR of the creature you wish to create, you must sacrifice one sentient soul (Int of 5 or better) and 500 gp. For example, if you wish to create a CR 8 Slaughterwight, you must sacrifice eight sentients and 4,000 gp. You cannot create any undead with a CR greater than two less than your character level. 

You automatically control up to your unmodified Charisma modifier in undead created by this feat, but no undead can have a CR greater than two less than your character level.

%%%
\featentry{Wrappings of the Ages}{[Necromantic]}
%%%

The ancient secrets by which unlife can be sustained in mummification have been unearthed.

\textbf{Prerequisite:} character level 8

\textbf{Benefit:} You can create mummies. In addition, any undead you create has their natural armor increase by +3. Also, any time your undead rest (take no actions) in an enclosed space that has never been touched by the sun, the location counts as a Tomb for them as long as they inhabit it (see New Rules). In all other ways, the area is not a Tomb.

You automatically control up to your Charisma modifier in undead created by this feat, but no undead can have a CR greater than two less than your character level.

%%%
\featentry{Sleep of the Ages}
%%%

Your mastery of ancient mummification techniques has revealed a secret technique for sleeping away the ages.

\textbf{Prerequisite:} character level 8, \linkfeat{Wrappings of the Ages}, you must remove all of your internal organs and place them within canoptic jars during a magic ritual

\textbf{Benefit:} By arranging focuses worth 1,000 GP in a ritual manner and wrapping yourself in the funeral arrangements of a mummy, you can initiate the Sleep of the Ages. Until your focuses are disturbed, you will stay in suspended animation. In this state, you do not age, breath, need to eat, or are subject to any effect requiring a Fort Save.

As a side effect of learning this technique, you remove all of your internal organs and place them within canoptic jars during a magical ritual. This process does not harm you, and from this point onward you are no longer subject to critical hits or sneak attacks. Having your organs in canoptic jars has no other game effect, but if they are destroyed you no longer gain the effects of this feat (your organs magically return to your body and you must remove them again to regain the use of this feat.)

%%%
\featentry{Whispers of the Otherworld}{[Necromantic]}
%%%

You have learned the tricks of torturing a soul past the veil of life, and into the shadow of death.

\textbf{Prerequisite:} character level 4

\textbf{Benefit:} You may create incorporeal undead. In addition, any undead you create have a +2 to Initiative, +4 to Move Silently checks, and Lifesight as a Special Quality.

You automatically control up to your Charisma modifier in undead created by this feat, but no undead can have a CR greater than two less than your character level.
