%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\classentry{Commoner}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\tagline{"Help! Help! I'm being repressed!"}

\textbf{Hit Die:} d4

\textbf{Class Skills:} The Commoner's class skills (and the key ability for each skill) are \linkskill{Craft} (Int), \linkskill{Profession} (Wis), and \linkskill{Survival} (Wis).

\textbf{Skills/Level:} 2 + Intelligence Bonus

\poorbab
\poorfor
\poorref
\poorwil

\begin{classtable}
\levelone{Completely Common}
\leveltwo{Sharp Sticks}
\levelthree{Common Cause}
\end{classtable}

\classfeatures

\textbf{Weapon and Armor Proficiency:} The commoner is proficient with one simple weapon related to whatever it is they do in their day to day life. He is not proficient with any other weapons, nor is he proficient with any type of armor or shields.

\textbf{Completely Common (Ex):} A commoner's stats are all 10, modified by race. Commoners don't have feats. For each feat they would have had, give them +1 hit point instead.

\textbf{Sharp Sticks (Ex):} A 2nd level commoner becomes proficient in all polearms. They also gain weapon proficiency with all other implements that they use in their day to day life (in addition to their starting proficiency), such as farming tools or a craftsman hammer, that could potentially be used as a weapon. Any weapon "improvised" in this manner deals damage as a Club appropriate to the commoner's size. If the object has sharp segments it might do slashing or piercing damage instead of bludgeoning damage.

\textbf{Common Cause (Ex):} A 3rd level commoner can Take 10 on Aid Another checks, either in combat or out of combat. This applies to both skill use to provide an ally with a +2 to a skill check, and in combat to either give an ally +2 to AC or +2 to one attack roll.