%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\raceentry{Aasimar}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vspace*{-8pt}
\quot{``My ancestors were more beautiful than you can imagine."}

Aasimar get a short stick from just about everyone. They get screwed as PCs by the Level Adjustment rules, and they get no respect from players. Frankly, Celestials just don't have a lot of dramatic tension most of the time. Sure you can have the occasional ``Legacy" scenario where you couldn't possibly live up to your awesome ancestors, but generally when it's important that someone has powerful family members it's so that you can introduce evil family members, not additional heroes.

So here's the deal: Aasimar are the great grandchildren of beautiful outsiders. They aren't just for being dudes with Devas as ancestors, the same game stats represent characters who come from Erinyes or Marilith stock.

\begin{itemize}
\item \racesize{Medium}
\item \racetype{Outsider (Native, Human)}
\item \racemovement{30ft}
\item \racevision{Darkvision 60ft}
\item +2 Charisma, +2 Wisdom
\item Aasimar with a Charisma of at least 10 may cast \linkspell{Light} as a spell-like ability at will. They may only have one such Light active at a time.
\item +2 racial bonus to \linkskill{Spot}, and \linkskill{Listen} checks.
\item \racefavoredclass{Any class with Charisma-based spellcasting ability}
\item \racelang{Common}
\item \raceextralang{Abyssal, Aquan, Auran, Celestial, Formian, Giant Frog, Ignan, Infernal, Sylvan, Terran}
\end{itemize}
