%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\raceentry{Goblin}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace*{-8pt}
\quot{``You weren't hired to think. You were hired because you have opposable thumbs."}

Goblins are the weakest and smallest of the Goblinoid races, and that means that in society in general they get a really crap deal. But that's not really important for a Player Character, because player characters get access to classes like Rogue, Knight, and Wizard for whom being small is not a huge problem. Indeed, Goblins have a number of saving graces that in the wild barely keep them alive that when used by a player character can make them very effective. Naturally adept at stealth, Goblins are virtually made to be a Rogue or Wizard, and indeed most Goblins who have class levels are one or the other.

But the Goblins are also extremely gifted mounted combatants. And why is that? Because they are the smallest and weakest of the Goblinoids, the Worgs long ago enslaved the Goblin people. That's right, the Worgs came in and imposed their dominion upon Goblins, not the other way around. But time does funny things\ldots\ Worgs are pretty stupid, and they don't have thumbs. So while they are individually powerful, eventually they were forced to have the Goblins do all the important stuff -- like keep records and make decisions.

So now, the Worgs have gone many generations doing pretty much whatever it is that their ``servants" tell them to do. Which means that really the Goblins are totally in control. And because of this, Goblin children are practically born into the saddle. Those rich enough to afford a wolf to ride (like well, player characters) can be devastatingly effective lancers.

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Mechanics}
%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{itemize}
\item \racesize{Small}
\item \racetype{Humanoid (Goblin)}
\item \racemovement{30ft}
\item \racevision{Darkvision 60ft}
\item +2 Dexterity, -2 Strength, -2 Charisma
\item +4 bonus to \linkskill{Move Silently} and \linkskill{Ride} checks.
\item Bonus Feat: \linkfeat{Mounted Combat}.
\item Goblins benefit from an ancient pact with the Worgs, and every Goblin receives a +2 bonus to any \linkskill{Bluff}, \linkskill{Diplomacy}, \linkskill{Handle Animal}, \linkskill{Sense Motive}, or \linkskill{Survival} check made with respect to a Worg.
\item \racefavoredclass{Any class with Move Silently or Ride as a class skill}
\item \racelang{Common, Goblin}
\item \raceextralang{Draconic, Elvish, Dwarvish, Giant, Gnoll, Infernal, Orcish, and Undercommon}
\end{itemize}
