%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\raceentry{Half-Orc}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace*{-8pt}
\quot{``I don't fit in anywhere, but you may be surprised to know that this dagger fits all kinds of places."}

Ah, the Half-Orc. Has any race ever gotten quite as dusty a drumstick as they? The reason that we have half-orcs at all is because they were around in Tolkien. But they didn't really do much in those books, they were just easily deluded villains who were borderline racist stereotypes and made us want to forget them altogether. But time moves on, and where once the Half-Orcs were debased and pathetic pawns of The Dark One, now we have them as a legitimate playable race. And yet, their game mechanics have never really been compatible with that.

Here's what they're supposed to be: Half-Orcs have the smarts of a human and the strength of an Orc. If people didn't hate them so much, they'd rule everything. But people do hate them so much. And here's why: Human women are, compared to Orcs, weak; Orcish women are, compared to Humans, gullible. Making Half-Orcs is easy, and since the modern Orc looks like an Orc from World of Warcraft more than a pig-man, perfectly understandable.

With all the wars that Orcs and Humans have, even periods of relative peace are rarely considered periods of friendship. So any time a Half-Orc happens, both races tend to consider it an abomination. It doesn't matter that a Half-Orc is a better leader than any of the other Orcs. It doesn't matter that the Half-Orc is tougher than any of the other Humans -- he's hated for his talents. And that makes him perversely really good at finding out things he wants to know from people. He's dealt with prejudice all his life, and knows pretty much everything you'd want to know about working around it.

\begin{itemize}
\item \racesize{Medium}
\item \racetype{Humanoid (Human, Orc)}
\item \racemovement{30ft}
\item \racevision{Darkvision 60ft}
\item +2 Strength
\item +2 to \linkskill{Intimidate}, \linkskill{Gather Information}, and \linkskill{Survival}.
\item \racefavoredclass{Any class with full BAB}
\item \racelang{Common, Orc}
\item \raceextralang{Any}
\end{itemize}
