%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\raceentry{Elf}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\raceentry{Elf}{``You shall never harm my beautiful trees!"}


\begin{itemize}
\item \racesize{Medium}
\item \racetype{Humanoid (Elf)}
\item \racemovement{30ft}
\item \racevision{Low-light vision}
\item -2 Constitution and +2 to any other stat. The other stat that gets a bonus is different based on the elf's subtype, but there is a subtype for every stat and different worlds have different names for each subtype.
\item Immunity to Sleep effects, and a +2 racial saving throw bonus against other Enchantment spells or effects. Elves do not sleep, but they must enter a trance-like state for 4 hours each day to maintain their wellbeing. While in a trance an elf does not take a penalty to \linkskill{Listen} checks like a sleeping character does.
\item Weapon Proficiency: Elves receive the Martial Weapon Proficiency feats for the longsword, rapier, longbow (including composite longbow), and shortbow (including composite shortbow) as bonus feats.
\item +2 racial bonus on \linkskill{Listen}, \linkskill{Search}, and \linkskill{Spot} checks. An elf who merely passes within 5 feet of a secret or concealed door is entitled to a Search check to notice it as if she were actively looking for it.
\item \racefavoredclass{Any class with Arcane spellcasting, or that has longsword proficiency.}
\item \racelang{Common and Elven}
\item \raceextralang{Draconic, Gnoll, Gnome, Goblin, Orc, and Sylvan}
\end{itemize}
