%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\raceentry{Tiefling}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\quot{``My ancestors were more evil than you will ever know, but let's see how I compare.''}

Tieflings are the most popular of the bad touched races, and for good reason. They are awesome. Not mechanically, they're kind of unimpressive. But they have pizzazz as characters. They have fiendish ancestry, and that makes them great villains and great tortured heroes. What it doesn't make them is particularly powerful. Tieflings aren't actually that great. Darkness appears on some class lists as a cantrip, and that's not an accident. Fundamentally, darkness just isn't a good effect.

Tieflings are honestly somewhat less powerful than Aasimar are (having as they do, some reasonably annoying penalties), but they are descended from hideous monsters from all over the planes, and they are generally speaking more fun to play.

\begin{itemize}
\item \racesize{Medium}
\item \racetype{Outsider (Native, Human)}
\item \racemovement{30ft}
\item \racevision{Darkvision 60ft}
\item +2 Dexterity, +2 Intelligence, -2 Charisma
\item Tieflings with a Charisma of at least 10 may cast \linkspell{Darkness} as a spell-like ability once per day.
\item +2 bonus to \linkskill{Bluff}, \linkskill{Hide}, and \linkskill{Move Silently} checks.
\item \racefavoredclass{Any class with 3/4ths BAB, as well as True Fiend}
\item \racelang{Common}
\item \raceextralang{Abyssal, Aquan, Auran, Celestial, Formian, Ignan, Infernal, Slaad, Sylvan, Terran}
\end{itemize}
