%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Character Fluff}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\tagline{"It's time for you to look inward, and begin asking yourself the big questions: Who \textbf{are} you? And what do \textbf{you} want?"}

Even once you pick a character background, there's still a lot left to know. Not everyone wants to bother with this sort of stuff, so here's some incentives: For each of the following questions that you answer satisfactorily about your character you get a free skill point (maximum of 5 points). A satisfactory answer is any answer that the majority of the other players agree is good enough for the current game (each player other than you, including the GM, gets 1 vote).

\begin{itemize*}
\item Who are the people that raised your character?
\item Who are the people currently alive that your character knows?
\item What are some major losses (including deaths of course) that your character has faced so far?
\item What was your character's first life and death situation?
\item What favorite foods and drinks does your character have? Also, what foods and drinks will your character avoid?
\item What sort of music or artwork does your character care about?
\item What kinds of facts and lore does your character like to know? (This doesn't have to be a knowledge skill category, any kinds of lore will do.)
\item Name three things that your character will do even though it might inconvenience them and/or gives them no direct advantage or benefit (eg: helping old ladies across the street, always invoking the Wanderer's Prayer at every fork in the road, etc)
\item Name three things that your character will avoid doing even though it means everyone else probably thinks they're stupid or an asshole or both (eg: never travel by horse, never sell to elves, etc).
\item Describe your character's appearance. Also describe their preferred clothing styles, including both the kind of outfit that they'd fight in and the kind of outfit that they'd wear for non-combat scenes (fancy parties, town life, etc).
\end{itemize*}
