%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\raceentry{Dwarf}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

foo?

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Mechanics}
%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{itemize*}
\item \racesize{Medium}
\item \racetype{Humanoid (Dwarf)}
\item \racemovement{20ft}
\item \racevision{Darkvision 60ft}
\item +2 Constitution, -2 Charisma.
\item \textbf{Slow and Steady (Ex)} A dwarf's movement speed is only 20ft, but it is not further reduced by armor or encumbrance.
\item \textbf{Stonecunning (Ex):} This ability grants a dwarf a +2 racial bonus on \linkskill{Search} checks to notice unusual stonework, such as sliding walls, stonework traps, new construction (even when built to match the old), unsafe stone surfaces, shaky stone ceilings, and the like. Something that isn't stone but that is disguised as stone also counts as unusual stonework. A dwarf who merely comes within 10 feet of unusual stonework can make a Search check as if he were actively searching, and a dwarf counts as having Trapfinding when dealing with stonework. A dwarf can also intuit depth, sensing his approximate depth underground as naturally as a human can sense which way is up.
\item \textbf{Earth Stability (Ex):} A dwarf gains a +4 bonus on ability checks made to resist being bull rushed or tripped when standing on the ground (but not when climbing, flying, riding, or otherwise not already standing firmly on the ground).
\item Weapon Familiarity: Dwarves may treat dwarven waraxes and dwarven urgroshes as martial weapons, rather than exotic weapons.
\item +2 racial bonus on saving throws against poison, spells, and spell-like effects.
\item +1 racial bonus on attack rolls against orcs and goblinoids.
\item +4 dodge bonus to Armor Class against Giants.
\item +2 racial bonus on \linkskill{Appraise} checks that are related to stone or metal items.
\item +2 racial bonus on \linkskill{Craft} checks that are related to stone or metal.
\item \racefavoredclass{Any class with full BAB}
\item \racelang{Common and Dwarven}
\item \raceextralang{Giant, Gnome, Goblin, Orc, Terran, and Undercommon}
\end{itemize*}
