%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Races}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Each Racial Entry, when complete, should roughly consist of the following elements,

Tagline

Intro Paragraph

Appearance:

Culture:

Names:

Mechanics:

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Favored Class}
%%%%%%%%%%%%%%%%%%%%%%%%%

Every race has a set of Favored Classes. Favored Classes are intended to be a minor and mostly flavor element to each race, and you can change which race has which favored classes in your game without any fear of game balance upsets. The effect of a Favored Class is that when a character takes a level in a Favored Class they gain +1 hit point for that level. For example, Dwarves have any class with Full BAB as a favored class, so a Dwarven Fighter 2/Rogue 1 would have 2 hit points more than normal.

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Languages}
%%%%%%%%%%%%%%%%%%%%%%%%%

Every race has a list of automatic languages as well as a list of suggested additional languages. Characters start the game knowing their race's automatic languages, as well as one bonus language per point of Intelligence Modifier (if positive). You don't have to select from the suggested languages list, you could pick other languages if you want. See the \linkskill{Speak Language} description for a long list of languages and who speaks them. In addition to automatic and bonus languages, a character can also learn additional languages via skill points. If a character's Intelligence changes after character creation, either temporarily or permanently, they don't gain or lose bonus languages at that point.

\input{races/aasimar}
\input{races/drow}
\input{races/dwarf}
\input{races/elf}
\input{races/feytouched}
\input{races/gnome}
\input{races/goblin}
\input{races/half-elf}
\input{races/halfling}
\input{races/half-orc}
\input{races/hobgoblin}
\input{races/human}
\input{races/kobold}
\input{races/orc}
\input{races/tiefling}
