%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\classentry{Barbarian}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\tagline{"My name is Sharptooth of the Wolf Tribe. Your women, lands, and riches are mine."}

\textbf{Playing a Barbarian:} Playing a Barbarian is actually very easy. In general, you hit things, and they fall down. A Barbarian's action in almost any circumstance can plausibly be "I hit it with my great axe!" As such, a Barbarian character can be a good method to introduce a new player to the game or kill some orcs when you've had a few glasses of brew.

\textbf{Alignment:} Every alignment has its share of Barbarians, however more Barbarians are of Chaotic alignment than of Lawful Alignment.

\textbf{Races:} Anybody can become a barbarian, and in areas with little in the way of civilization, a lot of people do.

\textbf{Starting Gold:} 4d6x10 gp (140 gold)

\textbf{Starting Age:} As Barbarian.

\textbf{Hit Die:} d12

\textbf{Class Skills:} The Barbarian's class skills (and the key ability for each skill) are \linkskill{Balance} (Dex), \linkskill{Climb} (Str), \linkskill{Hide} (Dex), \linkskill{Intimidate} (Cha), \linkskill{Jump} (Str), \linkskill{Knowledge} (Nature) (Int), \linkskill{Listen} (Wis), \linkskill{Move Silently} (Dex), \linkskill{Sense Motive} (Wis), \linkskill{Spot} (Wis), \linkskill{Survival} (Wis), and \linkskill{Swim} (Str).

\textbf{Skills/Level:} 4 + Intelligence Bonus



\goodbab{}
\goodfor{}
\poorref{}
\poorwil{}

\begin{classtable}
\levelone{Rage, Fast Healing 1}
\leveltwo{Rage Dice +1d6, Combat Movement +5'}
\levelthree{Battle Hardened}
\levelfour{Rage Dice +2d6, Combat Movement +10'}
\levelfive{Sidestep Hazards , Fast Healing 5}
\levelsix{Rage Dice +3d6, Combat Movement +15'}
\levelseven{Great Blows}
\leveleight{Rage Dice +4d6, Combat Movement +20'}
\levelnine{Great Life}
\levelten{Rage Dice +5d6, Combat Movement +25', Fast Healing 10}
\leveleleven{Call the Horde}
\leveltwelve{Rage Dice +6d6, Combat Movement +30'}
\levelthirteen{Watched by Totems}
\levelfourteen{Rage Dice +7d6, Combat Movement +35'}
\levelfifteen{Primal Assault, Fast Healing 15}
\levelsixteen{Rage Dice +8d6, Combat Movement +40'}
\levelseventeen{Savagery}
\leveleighteen{Rage Dice +9d6, Combat Movement +45'}
\levelnineteen{One With The Beast}
\leveltwenty{Rage Dice +10d6, Combat Movement +50', Fast Healing 20}
\end{classtable}

\classfeatures

\textbf{Weapon and Armor Proficiency:} Barbarians are proficient with simple weapons, martial weapons, light armor, medium armor and with shields.

\textbf{Rage (Ex):} When doing melee damage to a foe or being struck by a foe, a Barbarian may choose to enter a Rage as an immediate action. While Raging, a Barbarian gains a +2 morale bonus to hit and damage in melee combat and may apply any Rage Dice he has to his melee damage rolls. He also gains a +2 to saves, a -2 to AC, and he gains DR X/- with "X'' being equal to half his Barbarian level +2 (rounded down). For example, a 1st level Barbarian has DR 2/- while Raging and a 10th level Barbarian has DR 7/- while Raging.

While Raging, a Barbarian may not cast spells, activate magic items, use spell-like abilities, or drop his weapons or shield. Rage lasts until he has neither struck an enemy for three consecutive rounds nor suffered damage from an enemy for three consecutive rounds. He may voluntarily end a Rage as a full-round action.

\textbf{Fast Healing (Ex):} Barbarians shrug off wounds that would cripple a lesser man, and have learned to draw upon deep reserves of energy and stamina. At 1st level, they gain Fast Healing 1. At 5th level this becomes Fast Healing 5, Fast Healing 10 at 10th level, Fast Healing 15 at 15th level, and Fast Healing 20 at 20th level. This healing only applies while he is \textit{not} raging.

If a Barbarian ever multi-classes, he permanently loses this ability. A multiclass character does not gain this ability. A character with 4 or more levels of Barbarian gains this ability even if multiclassed.

\textbf{Rage Dice (Ex):} While Raging, a Barbarian may add these dice of damage to each of his melee attacks. These dice are not multiplied by damage multipliers, and are not applied to any bonus attacks beyond those granted by Base Attack Bonus. These dice are not sneak attack dice, and do not count as sneak attack dice for the prerequisites of prestige classes or feats.

\textbf{Combat Movement (Ex):} While Raging, a Barbarian moves faster in combat, and may add his Combat Movement to his speed whenever he takes a move action to move. This only applies to move actions, and not to other actions that allow the barbarian to move, such as charges or withdraws.

\textbf{Battle Hardened (Ex):} At 3rd level, a Raging Barbarian's mind has been closed off from distractions by the depths of his bloodlust and battle fury. While Raging, he may use his Fortitude Save in place of his Will Save. If he is under the effects of a compulsion or fear effect, he may act normally while Raging as if he was inside a \textit{protection from evil} effect.

\textbf{Sidestep Hazards (Ex):} At 5th level, a Raging Barbarian learns to sidestep hazards with an intuitive and primal danger sense. While Raging, he may use his Fortitude Save in place of his Reflex Save.

\textbf{Great Blows (Ex):} At 7th level, a Raging Barbarian's melee attacks are Great Blows. Any enemy struck by the Barbarian's melee or thrown weapon attacks must make a Fort Save or be stunned for one round. No enemy can be targeted by this ability more than once a round, and the save DC for this ability is 10 + half the Barbarian's HD + his Constitution modifier.

\textbf{Great Life (Ex):} While Raging, a 9th level Barbarian is immune to nonlethal damage, death effects, stunning, critical hits, negative levels, and ability damage (but not ability drain).

\textbf{Call the Horde (Ex):} An 11th level Barbarian becomes a hero of his people. He gains the Command feat as a bonus feat, but his followers must be Barbarians. In campaigns that do not use Leadership feats, he instead gains a +2 unnamed bonus to all saves.

\textbf{Watched by Totems (Ex):} At 13th level, a Barbarian may immediately reroll any failed save. He may do this no more than once per failed save.

\textbf{Primal Assault (Ex):} At 15th level, a Raging Barbarian's may choose to radiate an effect similar to an \linkspell{Antimagic Field} when he enters a Rage, with a caster level equal to his HD. Unlike a normal Antimagic Field, this effect does not suppress magic effects on him or the effects of magic items he is wearing or holding.

\textbf{Savagery (Ex):} At 17th level, a Raging Barbarian may take a full round action to make a normal melee attack that has an additional effect similar to a \linkspell{Disjunction}. Unlike a normal Disjunction, this effect only targets a single item or creature struck.

\textbf{One With The Beast (Ex):} At 19th level, a Barbarian may no longer needs to be in a Rage to use any Barbarian ability.
