%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\classentry{Curator}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\tagline{"These people are under my stewardship. Please handle them with care."}

\textbf{Alignment:} Any

\textbf{Races:} Any

\textbf{Starting Gold:} 3d6x10 gp (100 gold)

\textbf{Starting Age:} As Cleric.

\textbf{Hit Die:} d8

\textbf{Class Skills:} The Curator's class skills (and the key ability for each skill) are \linkskill{Concentration} (Con), \linkskill{Craft} (Int), \linkskill{Decipher Script} (Int), \linkskill{Diplomacy} (Cha), \linkskill{Heal} (Wis), \linkskill{Listen} (Wis), \linkskill{Knowledge} (arcana) (Int), \linkskill{Knowledge} (local) (Int), \linkskill{Knowledge} (religion) (Int), \linkskill{Profession} (Wis), \linkskill{Sense Motive} (Wis), \linkskill{Spellcraft} (Int), \linkskill{Spot} (Wis), \linkskill{Survival} (Wis), and \linkskill{Use Magic Device} (Cha).

\textbf{Skills/Level:} 4 + Intelligence Bonus

\modebab{}
\goodfor{}
\poorref{}
\goodwil{}

\begin{classtable}
\levelone{Luminous Bolt, Benediction}
\leveltwo{Sphere}
\levelthree{Benediction}
\levelfour{Heal Injuries}
\levelfive{Benediction}
\levelsix{Sphere}
\levelseven{Benediction}
\leveleight{One and All, Greater Luminous Bolt}
\levelnine{Greater Benediction}
\levelten{Sphere}
\leveleleven{Greater Benediction}
\leveltwelve{Perfect Preservation}
\levelthirteen{Greater Benediction}
\levelfourteen{Sphere}
\levelfifteen{Supreme Benediction}
\levelsixteen{Supreme Luminous Bolt}
\levelseventeen{Supreme Benediction}
\leveleighteen{Sphere}
\levelnineteen{Supreme Benediction}
\leveltwenty{Eternity}
\end{classtable}

\classfeatures

\textbf{Weapon and Armor Proficiency:} A Curator is proficient with simple weapons, with light and medium armor, and with shields (but not great shields).

\textbf{Luminous Bolt (Sp):} As an attack action, a Curator may fire a bolt of light at her foes. This has a range of Close (25 feet +5 ft./2 levels), does 1d6 light damage per two levels of Curator (rounded up), and requires a ranged touch attack to hit. Any creature damaged by this attack must make a Fortitude save (DC 10 + Charisma Modifier + 1/2 your level) or be dazzled for one round. Undead and creatures specifically vulnerable to light take double damage, and incorporeal undead targeted by this effect have no miss chance due to incorporeality.

Once a Curator reaches 8th level, any creature that fails the Fortitude save when struck by her Luminous Bolt also becomes blinded for one round. When she reaches 16th level, a creature failing the save also becomes stunned for one round.

\textbf{Benedictions (Sp):} At levels 1, 3, 5, and 7, a Curator learns a Benediction. Each Benediction requires an immediate action to activate, may target any creature the Curator can see within Close range (including herself), and is usable at will. The effects of a Benediction end at the start of the Curator's next turn, and the affected creature is surrounded by a faint glow while its effects persist.

Each Benediction has two effects, chosen from the following list:
\begin{itemize*}
\item The target of your Benediction receives an amount of temporary HP equal to your ranks in the Heal skill.
\item The target of your Benediction is cured of one of the following status effects: dazzled, shaken, sickened, or magical fatigue (your choice at time of use).
\item The target of your Benediction receives a +2 morale bonus to AC.
\item The target of your Benediction receives a +2 morale bonus to all saves.
\item The target of your Benediction receives spell resistance equal to 5 + your character level.
\item The target of your Benediction gains a +3 insight bonus to resist enemy bullrush, disarm, grapple, and trip attempts.
\item The target of your Benediction gains a +5 insight bonus to Balance, Escape Artist, and Tumble checks.
\item The target of your Benediction gains a +5 insight bonus to Climb, Jump, and Swim checks.
\item The target of your Benediction gains a +5 insight bonus to Listen and Spot checks, and to resist enemy feints.
\item The target of your Benediction gains blindsense out to 15'.
\item The target of your Benediction gains a +10' insight bonus to move speed.
\item Anyone attacking the target of your Benediction in melee must make a Fortitude save (DC 10 + half level + Charisma Mod) or be sickened for one round. This occurs before the attack is resolved.
\item Anyone attacking the target of your Benediction in melee must make a Will save (DC 10 + half level + Charisma Mod) or be shaken for one round. This occurs before the attack is resolved.
\end{itemize*}

\textbf{Spheres (Sp):} At 2nd level, and every 4 levels thereafter, the Curator gains basic access to a Sphere, which must be one of: Exorcism, Mystery, Piety, Restraint, Revelation, Splendor, or Vigor (see below). If she selects a Sphere in which she already has basic access, she gains advanced access; if she already has advanced accesss, she gains expert access.

\textbf{Heal Injuries (Sp):} With a one minute ritual, a Curator of 4th level can heal a number of characters equal to her class level of a number of hit points of damage equal to her ranks in the Heal skill. This action may be taken a number of times per day equal to 3 + the Curator's Charisma Modifier (if any), and all affected characters must be within close range of the Curator for the entire period.

\textbf{One and All (Sp):} At 8th level, a Curator takes on wider responsibilities. Once per day, when she activates one of her Benedictions, she may apply its effects to herself and all allies within range, rather than just one target.

\textbf{Greater Benedictions (Sp):} At levels 9, 11, and 13, a Curator learns a Greater Benediction. Each Greater Benediction requires an immediate action to activate, may target any creature the Curator can see within Close range (including herself), and is usable at will. The effects of a Greater Benediction end at the start of the Curator's next turn, and the affected creature is surrounded by a warm glow while its effects persist.

When a Curator gains a Greater Benediction, she may replace one of her Benedictions with a different Benediction.

Each Greater Benediction has two effects, chosen from the following list:
\begin{itemize*}
\item The target of your Greater Benediction receives DR 8/-.
\item The target of your Greater Benediction gains energy resistance 15 against one energy type you select at the time of use.
\item The target of your Greater Benediction cannot be affected by poison, disease, fear, or charm effects (this does not suppress or remove effects already present).
\item The target of your Greater Benediction gains the benefits of a protection from alignment effect, using an alignment you choose at the time of use.
\item The target of your Greater Benediction benefits from Evasion and Improved Uncanny Dodge.
\item The target of your Greater Benediction benefits from blindsight out to 30'.
\item The target of your Greater Benediction does not provoke the normal attacks of opportunity for movement, ranged attacks, spells, spell-like abilities, or using items.
\item The target of your Greater Benediction benefits from a \linkspell{Freedom of Movement} effect.
\item Anyone attacking the target of your Greater Benediction in melee must make a Reflex save or be struck by a luminous pulse for 5d6 light damage (undead and light-vulnerable creatures take double damage). Each attacker is subjected to this effect only once per round.
\item Anyone attacking the target of your Greater Benediction must make a Will save (DC 10 + CHA + 1/2 your level) or fail, losing the action but not any resources (spell slots, components, XP, and the like) used to power it.
\item Your Greater Benediction affects one additional target within range.
\item Your Greater Benediction bestows any two effects from the Benediction Effects list.
\end{itemize*}

\textbf{Perfect Preservation (Ex):} Once she reaches 12th level, a Curator is immortal. She may also care for a number of willing creatures equal to her charisma modifier, and prevent them from aging for as long as they receive care. Additionally, neither the Curator nor any creature under her care will lose a level if they die and are resurrected.

\textbf{Supreme Benedictions (Sp):} At levels 15, 17, and 19, a Curator learns a Supreme Benediction. Each Supreme Benediction requires an immediate action to activate, may target any creature the Curator can see within Close range (including herself), and is usable at will. The effects of a Supreme Benediction end at the start of the Curator's next turn, and the affected creature is surrounded by a strong glow while its effects persist.

When a Curator gains a Supreme Benediction, she may replace one of her Benedictions or Greater Benedictions with a different Benediction of the same type.

Each Supreme Benediction has two effects, chosen from the following list:
\begin{itemize*}
\item The target of your Supreme Benediction is immune to fire, cold, electricity, acid, sonic, negative energy, and death effects.
\item The target of your Supreme Benediction is immune to fatigue, exhaustion, fear affects, mind-affecting effects, dazing, stunning, sickening, and nausea, and all such effects are immediately removed from him.
\item The target of your Supreme Benediction has total concealment.
\item The target of your Supreme Benediction benefits from true seeing and blindsight to 120', and his attacks never suffer a miss chance due to concealment.
\item The target of your Supreme Benediction may choose to teleport himself and everything he is physically carrying up to 100' in any direction as a free action once per round.
\item Any creature damaging the target of your Supreme Benediction also damages itself for half that amount (this includes ability damage).
\item Any creature forcing the target of your Supreme Benediction to make a saving throw must itself make a Fortitude save (DC 10 + CHA + 1/2 your level) or be knocked unconscious for two rounds.
\item Any hostile creature that meets the gaze of the target of your Supreme Benediction must make a Reflex save (DC 10 + CHA + 1/2 your level) or be cowered until it loses sight of him.
\item Any creature coming within 60' of the target of your Supreme Benediction with hostile intent must make a Will save (DC 10 + CHA + 1/2 your level) or become helpless for one round. Each creature is only subjected to this effect once per round.
\item The effects of your Supreme Benediction persist for one extra round.
\item Your Supreme Benediction bestows any two effects from the Greater Benediction Effects list.
\end{itemize*}

\textbf{Eternity (Su):} Upon reaching 20th level, a Curator selects one Benediction or Greater Benediction that she knows. Thereafter, she enjoys its effects unceasingly and at all times.

%%%
\subsubsection{Naming Your Benediction}
%%%

Naturally, all your benedictions should have a good name to shout as you're throwing them all over the place. Use the following chart for ideas

\begin{basictable}{Random Benediction Names}{c l l l}
\textbf{d12} & \textbf{Adjective} & \textbf{Noun} & \textbf{Subject}\\
1 & Holy & Benediction & of War\\
2 & Pure & Barrier & of the Gods\\
3 & Prismatic & Fog & of the Stars\\
4 & Divine & Grace & of the Nymph(s)\\
5 & Majestic & Favor & of the Flame\\
6 & Fearsome & Light & of Fervor\\
7 & Swirling & Kiss & of Vitality\\
8 & Bright & Hand & of Crystal\\
9 & Careful & Spirit & of the Blind\\
10 & Beautiful & Knowledge & of the Fallen\\
11 & Unearthly & Wings & of Ascension\\
12 & Guiding & Guidance & of the Guides\\
\end{basictable}

%%%
\subsubsection{Curator Spheres}
%%%

The Spheres available to the Curator do not follow the thematic restrictions given in the Tome of Fiends, and therefore are not available to Fiendish Sphere users, such as the True Fiend, Conduit of the Lower Planes, and Warlock. Additionally, these Spheres do not impart fiendish traits as the Fiendish Spheres do. However, they follow all other mechanics for Fiendish Spheres.

\begin{description}
\item[Mystery] You benefit from a constant Undetectable Alignment effect.
\begin{description*}
\item[1] Disguise Self
\item[3] Silence
\item[5] Blacklight
\item[7] Greater Invisibility
\item[9] Mirage Arcana
\item[11] Forbiddance
\item[13] Screen
\item[15] Mind Blank
\item[17] Etherealness
\item[19] Time Stop
\end{description*}

\item[Piety] If you succeed on a Sense Motive check (opposed by Bluff), you know the target's alignment. If you fail, you cannot make another attempt until you gain another rank of Sense Motive.
\begin{description*}
\item[1] Bless
\item[3] Aid
\item[5] Prayer
\item[7] Lesser Globe of Invulnerability
\item[9] Hallow
\item[11] Heroes' Feast
\item[13] Refuge
\item[15] Holy Aura
\item[17] Gate (Calling version only)
\item[19] Miracle
\end{description*}

\item[Restraint] You gain a +3 bonus on saves against Mind-affecting effects.
\begin{description*}
\item[1] Entangle
\item[3] Web
\item[5] Stinking Cloud
\item[7] Black Tentacles
\item[9] Wall of Stone
\item[11] Repulsion
\item[13] Forcecage
\item[15] Prismatic Wall
\item[17] Temporal Stasis
\item[19] Imprisonment
\end{description*}

\item[Revelation] You receive a +2 bonus on all Knowledge checks, and never count as untrained in any Knowledge skill.
\begin{description*}
\item[1] Detect Evil
\item[3] Detect Thoughts
\item[5] Clairaudience/Clairvoyance
\item[7] Divination
\item[9] True Seeing
\item[11] Find the Path
\item[13] Legend Lore
\item[15] Discern Location
\item[17] Foresight
\item[19] Astral Projection
\end{description*}

\item[Splendor] You gain a +2 bonus to Diplomacy, Intimidate, and Sense Motive
\begin{description*}
\item[1] Charm Person
\item[3] Eagle's Splendor
\item[5] Flame Strike
\item[7] Glorious Form (as Monstrous Form, except the new form appears glorious instead of monstrous)
\item[9] Sympathy
\item[11] Greater Heroism
\item[13] Planar Ally
\item[15] Sunburst
\item[17] Weird
\item[19] Implosion
\end{description*}

\item[Vigor] Whenever you heal someone with a spell-like ability, they recover additional HP equal to your ranks in the Heal skill.
\begin{description*}
\item[1] Cure Light Wounds
\item[3] Shield Other
\item[5] Cure Serious Wounds
\item[7] Death Ward
\item[9] Raise Dead
\item[11] Heal
\item[13] Greater Restoration
\item[15] Greater Spell Immunity
\item[17] Mass Heal
\item[19] True Resurrection
\end{description*}

\end{description}
