%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\classentry{Dragonfire Adept}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\tagline{"I studied the ways of the dragons. Mostly I learned how to set punks like you on fire."}

Dragonfire Adepts are heroes (and villains) who wander around the world doing draconic things. Mostly this entails breathing on things to set them on fire or whatever. They have studied the powers of dragons. Those fierce beasts that \sout{fly around terrorizing the countryside} laze about like cats and collect shines like magpies, the magical creatures that \sout{tower above cities} could actually sleep on your bed, generally.

Dragonfire Adepts are not born, they are taught. You don't just appear as a dragonfire adept because one of your ancestors needs to go to prison, they actually sit down and decide to learn how to be awesome, like a Wizard or Fighter or Monk. That said, many of them learn their ways on the job, and a large portion of the learning is always going to be via experience. They are almost compelled to "go out adventuring".

\textbf{Playing a Dragonfire Adept:} Constitution is awesome for your Hit Points, and more importantly for determining the Save DC of your Breath Weapon. However you can also find uses for Charisma - Spell-Like Abilities are keyed to it, and sometimes you want to talk at people. The other Ability Scores depend very much on what you want to do in particular. Dragonfire Adepts tend to take feats that either make their Breath Weapon more awesome, or that generally make them better at fighting such as Juggernaut and Elusive Target.

\textbf{Starting Age:} as Cleric

\textbf{Starting Wealth:} as Rogue

\textbf{Alignment:} Dragonfire Adepts can be of any alignment, and this often determines the kind of dragon they like best, because they're color-coded for your convenience.

\textbf{Hit Die:} d8

\textbf{Skill Points per level:} 4 + Int

\textbf{Class Skills:} \linkskill{Appraise}, \linkskill{Bluff}, \linkskill{Climb}, \linkskill{Concentration}, \linkskill{Craft}, \linkskill{Decipher Script}, \linkskill{Diplomacy}, \linkskill{Disable Device}, \linkskill{Gather Information}, \linkskill{Intimidate}, \linkskill{Jump}, \linkskill{Knowledge} (Any), \linkskill{Listen}, \linkskill{Ride}, \linkskill{Search}, \linkskill{Sense Motive}, \linkskill{Spellcraft}, \linkskill{Spot}, \linkskill{Survival}, and \linkskill{Use Magic Device}.

\modebab{}
\goodfor{}
\goodref{}
\goodwil{}

\begin{extraclasstable}{\multicolumn{1}{p{1.3cm}}{\textbf{Breath Weapon}}}
\levelone{Cone Breath, First Element, Draconic Mind & 2d6}
\leveltwo{Second Element, Wyrmling Spell-likes & 3d6}
\levelthree{Line Breath, Draconic Body, First Legacy Secret & 4d6}
\levelfour{Third Element, Spell Vision & 5d6}
\levelfive{Blast Breath, Energy Resistance & 6d6}
\levelsix{Fourth Element, Sphere, Dragoncraft & 7d6}
\levelseven{Hardened Scales, Juvenile Spell-likes & 8d6}
\leveleight{Sonic Breath, Greater Draconic Mind & 10d6}
\levelnine{Energy Resistance (x2), Second Legacy Secret & 11d6}
\levelten{Elemental Enhancements & 12d6}
\leveleleven{Reflective Scales & 13d6}
\leveltwelve{Force Breath, Sphere & 15d6}
\levelthirteen{Energy Resistance (x3), Adult Spell-likes & 16d6}
\levelfourteen{Shadow Breath, Master Draconic Mind & 18d6}
\levelfifteen{Draconic Soul, Third Legacy Secret & 20d6}
\levelsixteen{Gaseous Breath & 23d6}
\levelseventeen{Draconic Immunity & 26d6}
\leveleighteen{Space Rending Breath, Sphere & 30d6}
\levelnineteen{Draconic Health, Ancient Spell-likes & 35d6}
\leveltwenty{Ultimate Breath & 40d6}
\end{extraclasstable}

\classfeatures

\textbf{Weapons and Armor Proficiency:} The Dragonfire Adept is proficient with all Simple weapons, one Martial weapon, Light Armor, and Medium Armor. She is also proficient with any Intelligent weapon, as well as any weapon, armor, or shield made from dragon parts. Armor and Shields made from Dragon parts count as having an armor check penalty and armor stealth penalty of 4 less than normal when used by a Dragonfire Adept. The elemental resistance granted by such armor and shields stacks with the elemental resistance that the Dragonfire Adept gains at 5th level.

\textbf{Breath Weapon (Su):} The Dragonfire Adept has a breath weapon that can be used once per round as a standard action. The shape of the breath weapon, and the type of damage or other effect is variable (see below), but the save DC against the dragonfire adept's breath weapon is always 10 + 1/2 her level + her Constitution modifier. If the breath is dealing damage the amount of damage is given on the table, and the save is for half damage. If the breath is inflicting some other effect then the save negates that effect. Prestige Classes that improve spellcasting ability or "other class features" improve the breath weapon's damage. Metabreath feats can be applied to the breath weapon, simply add a delay where there wouldn't normally be one.

\textbf{Breath Shapes:} At first level the Dragonfire Adept's breath weapon always takes the form of a Close range Cone. At 3rd level it can also be used as a Medium ranged Line. At 5th level it can be used as a Blast within Medium range with a radius of 10ft + 5ft per 4 levels (rounded up).

\textbf{Breath Elements:} At first level the Dragonfire Adept can breathe a single type of elemental energy. At 2nd, 4th, and 6th level she gains an additional energy type she can use. The type of energy determines what kind of save the target must make against the attack:

\begin{itemize*}
\item Acid (fortitude)
\item Cold (fortitude)
\item Electric (reflex)
\item Fire (reflex)
\end{itemize*}

\textbf{Draconic Mind (Ex):} A 1st level Dragonfire Adept's mind is already adapted to viewing the world the way a Dragon does. She gains the (dragon) subtype, allowing her to count herself as a dragon in addition to her own type. Her senses improve greatly, giving her Darkvision 120ft and Low-light Vision. Lastly, her memory becomes incredibly keen like a dragon's, and she can recall almost any fact she's ever heard. This gives her a racial bonus to Appraise, Knowledge, and Spellcraft checks equal to one third her level.

\textbf{Wyrmling Spell-likes (Sp):} A 2nd level Dragonfire Adept can cast \linkspell{Endure Elements}, \linkspell{Speak With Animals}, \linkspell{Spider Climb}, and \linkspell{Water Breathing} as spell-like abilities. Each spell can be used once per day.

\textbf{Draconic Body (Ex):} A 3rd level Dragonfire Adept's body has been transformed through training to become more draconic in nature. She becomes completely immune to Sleep and Paralysis effects. She gains the perfect digestion of dragons, allowing her to eat basically anything at all that isn't explicitly poisonous or diseased, even inorganic stuff like, dirt, rocks, and metal if she really has to (though without a Bite attack, such as from the Mighty Attacks Legacy Secret, she can't actually chew on rocks and metal). Additionally, she ceases to age according to her old body's limitations, and instead becomes ageless like a dragon. Any effects of old age are retroactively removed, and she does not gain any further old age effects. Unlike a true dragon, the Dragonfire Adept doesn't actually grow to larger size categories or anything like that, no matter how long they live.

\textbf{Legacy Secrets (Ex):} At 3rd level, 9th level, and 15th level the Dragonfire Adept selects a Legacy Secret to learn. Each secret provides effects that improve at those levels, and a selected secret grants its full effects no matter the order you select them in. Pick from the following list:

\begin{description*}
\item[Mighty Attacks:] the Dragonfire Adept gains a Primary Bite (1d6+Str for a Medium character), a Primary Tail (1d8+Str*1.5 for a Medium character) and two Secondary Claws (1d4+Str*0.5 for a Medium character). These are all actually magic weapons with an Enhancement Bonus of +1 per 3 hit dice (round up). At level nine, the Dragonfire Adept gains an enhancement bonus to Strength equal to +1 per 3 hit dice (round up) and the damage dice of all her natural attacks improves by one stage (as if they had gained a size category). At level fifteen the Dragon Body attacks gain a 19-20 threat range, and her natural attack damage improves by another stage.
\item[Mighty Wings:] the Dragonfire Adept gains two Secondary Wing attacks (1d4+Str*0.5 for a Medium character) and a Flight speed of 60ft with (Poor) maneuverability. At level nine, the flight speed improves to 90ft  and (Average) maneuverability. At level fifteen it improves to 120ft and (Good) maneuverability.
\item[Master of Exhalations:] the Dragonfire Adept can leave a number of 5ft square "gaps" in her breath area equal to her hit dice, to save allies from death. At level nine her breath is so intense that a creature must have a CR of 4 greater than her own to apply Evasion or Improved Evasion against it, and the breath's damage pierces an amount of Energy Resistance equal to the Dragonfire Adept's level. At level fifteen she can automatically deal maximum damage with her breath weapon three times per day.
\item[Frightful Presence:] You gain the Frightful Presence special ability, effective whenever you attack with a natural weapon, fly overhead, or use your breath weapon. All creatures within range with HD less than your own must make a Will save (DC 10+1/2 level+Charisma Mod) or be \linkcondition{Shaken} for 4d6 rounds. If their HD is more than 4 less than your own they are \linkcondition{Panicked} for 4d6 rounds instead. Creatures that make their save are immune to your Frightful Presence for 24 hours. Naturally, other creatures with a Frightful Presence ability are immune to this, and you are immune to their Frightful Presence. This is a [Mind-Affecting], [Fear] effect. At level three the range is 100ft, At level nine the range is 200ft, and at level fifteen the range becomes 300ft.
\item[Disciple of Bahamut:] the Dragonfire Adept has a permanent Magic Circle Against Evil effect, can Detect Evil at will, and once per day can make her breath weapon Smiting against Evil creatures: any evil creatures caught in the breath take -4 to their save and take an additional 50\% damage (regardless of if they save or not). At level nine she can performing a smiting breath three times per day, and once per day she can add a \linkspell{Banishment} effect to her breath weapon (any who fail their save against the primary breath effect are automatically affected by the Banishment, no separate save). At level fifteen she can smite five times per day, and cast \linkspell{Heal} three times per day as a spell-like ability.
\item[Servant of Tiamat:] the Dragonfire Adept has a permanent Magic Circle Against Good effect, can Detect Good at will, and gains an Enhancement bonus to Intimidate equal to her level. At level nine she can use two different breath weapons at the same time three times per day (any overlapping area doesn't stack, a target in both areas is only affected by one of the breaths or the other, the Dragonfire Adept's choice). At level fifteen this upgrades to three breath weapons at once, and it can be used five times per day.
\item[Visions of Lichdom:] the Dragonfire Adept already knows she wants to be a Dracolich. She has a pseudo-phylactery: some important item that is used as a focus, from which she can cast Magic Jar at will, but only on reptilian Animals with fewer hit dice than she has. At level nine, she becomes immune to Poison and Disease, and she can choose to release a rotting ichor breath weapon - instead of dealing damage, all in the area must pass a Fortitude Save or be Nauseated for 1 round per 5 dice of damage it deals (round up). At level fifteen, her type changes to Undead, gaining the [Dark Minded] Subtype. She can choose whether or not to also have the [Unliving] Subtype. Protip: Con scores are awesome.
\end{description*}

\textbf{Spell Vision (Su):} A 4th level Dragonfire Adept has studied enough on the subject of magical items, magical treasures, and treasure hoards in general to begin seeing the auras of such things. She gains a permanent \linkspell{Arcane Sight} effect. With a full-round action she can \linkspell{Identify} an item as a spell-like ability.

\textbf{Energy Resistance (Ex):} A 5th level Dragonfire Adept gains Energy Resistance against Acid, Cold, Electric, and Fire damage equal to her level. At 9th level this improves to two times her level, and at 13th level this improves to three times her level. If the Dragonfire Adept is wearing draconic equipment that grants Energy Resistance as well, that stacks with this energy resistance.

\textbf{Spheres:} At 6th level the Dragonfire Adept gains access to an Elemental Sphere at the Basic rank. At 12th level she gains a second sphere at Basic. At 18th level she gains a third basic sphere at Basic. The Dragonfire Adept can't use these selections to improve an existing sphere to a higher grade.

\textbf{Dragoncraft (Ex):} At 6th level the Dragonfire Adept can take old dragon parts and craft them into weapons and armor like a pro. They count as having the Craft Magical Arms and Armor feat, but only when crafting weapons from dragon parts (though you can make just about any weapon from dragon parts), or when crafting a Dragonscale Suit, Dragonscale Plate, or Dragonscale Shield.

\textbf{Hardened Scales (Ex):} A 7th level Dragonfire Adept's special training allows them to harden their skin into protective scales that can block harm from physical attacks. She gains an Enhancement bonus to Natural Armor equal to 1/3rd her level (rounded up).

\textbf{Juvenile Spell-likes (Sp):} A 7th level Dragonfire Adept can cast \linkspell{Plant Growth}, \linkspell{Stone Shape}, and \linkspell{Wall of Ice} each once per day as a spell-like ability.

\textbf{Sonic Breath (Su):} At 8th level the Dragonfire Adept has learned to deal Sonic damage with her breath weapon. The sonic damage can come in the form of a massive booming rumble (allowing a Fortitude save), or a high pitched screech (allowing a Will save).

\textbf{Greater Draconic Mind (Ex):} At 8th level, the Dragonfire Adept's thoughts become even more like those of a dragon, improving her senses further. She gains Darkvision out to 250ft, as well as Blindsense and Tremorsense of 120ft. At the same time, she becomes very greedy for material wealth. Any attempt to bribe her with coin or gems should generally be considered to be twice as effective as otherwise (Specifics are up to the player and GM).

\textbf{Elemental Enhancements (Su):} A 10th level Dragonfire Adept, having already learned all five energy types, learns to add a special effect to their breath weapon depending on the energy type used with each attack. If a target fails their save against an energy damage breath they suffer an additional effect, as follows:

\begin{itemize*}
\item Fire: Creatures and objects catch on fire. Also make a Dispel attempt against all [Cold] effects in the area.
\item Cold: Creatures are Slowed for one round, and water in the area is frozen as if by a Freezing Sphere effect. Also make a Dispel attempt against all [Fire] effects in the area.
\item Electricity: Creatures are Entangled for 1 round. Any barriers made of metal, such as metal or adamantine doors or walls, do not block line of effect against this breath.
\item Acid: Creatures are sickened for 1 minute. Unattended objects in the area automatically take an equal amount of damage one round later.
\item Sonic: Creatures are deafened for 1 minute, and objects are affected as if by the area form of a Shatter effect.
\end{itemize*}

\textbf{Reflective Scales (Ex):} At 11th level a Dragonfire Adept's scales are not just hardened against the physical, but they repel the magical as well. She gains a Resistance bonus to saves equal to 1/3rd her level (rounded up).

\textbf{Force Breath (Su):} A 12th level Dragonfire Adept learns to deal force damage with her breath weapon. This has a reflex save, and has the normal benefits of being force damage (ignores hardness when damaging objects, has no miss chance against Incorporeal creatures, and can affect Ethereal targets even while not on the Ethereal Plane).

\textbf{Adult Spell-likes (Sp):} A 13th level Dragonfire Adept can case \linkspell{Control Weather}, \linkspell{Find The Path}, and \linkspell{Wall of Stone}, each once per day, as a spell-like ability.

\textbf{Shadow Breath (Su):} A 14th level Dragonfire Adept can breathe a wave of consuming shadow. Instead of dealing dice of damage, any target that fails a Fortitude save against the breath suffers one negative level per five damage dice that would have been dealt (round down). The negative levels go away on their own in an hour, with no chance of converting into permanent level loss.

\textbf{Master Draconic Mind (Ex):} A 14th level Dragonfire Adept's mind becomes even more dragon-like, improving their senses for the final time. They gain Darkvision out to 500ft, Blindsense and Tremorsense out to 250ft, and Blindsight out to 120ft. As with before, the Dragonfire Adept's desires to amass coin and gems grow to even greater heights. Even though the Dragonfire Adept probably no longer has any use for them, having moved to Wish Economy goods several levels ago, the Dragonfire Adept can probably still be bribed to do things (within reason) if offered coins and gems as payment. Any such bribes should be considered three times as persuasive as normal (again, the specifics of this are up to the GM and player).

\textbf{Draconic Soul (Su):} A 15th level Dragonfire Adept transforms her soul to have the nature of the dragon. This gives her Spell Resistance equal to 5 + her level.

\textbf{Gaseous Breath (Su):} A 16th level Dragonfire Adept's breath attack can take the form of a gaseous cloud that requires creatures to make a Will save to avoid one of the following effects:

\begin{itemize*}
\item Fall Asleep for one round per five damage dice (round up)
\item Be Paralyzed for one round per five damage dice (round up)
\item Panic for one round per five damage dice (round up)
\end{itemize*}

\textbf{Draconic Immunity (Ex):} A 17th level Dragonfire Adept training gives them immunity to either an Energy type, or something else about as common, such as [Compulsion] effects or [Death] effects or something like that.

\textbf{Space Rending Breath (Su):} An 18th level Dragonfire Adept's breath weapon is so powerful that it can tear open the fabric between worlds. By using her breath weapon, she can open a \linkspell{Gate} to another plane. It lasts on its own for a number of rounds equal to the Dragonfire Adept's Constitution Modifier (minimum of 1), and only one such Gate can be active at once (opening a second one closes the first).

\textbf{Draconic Health (Ex):} A 19th level Dragonfire Adept converts all of her Dragonfire Adept hit dice from d8s into d12s. Reroll all hit dice, and only keep the new result if it gives a higher hit point total than before. All future levels in Dragonfire Adept continue to use d12s for hit dice.

\textbf{Ancient Spell-likes (Sp):} A 19th level Dragonfire Adept can use \linkspell{Discern Location}, \linkspell{Foresight}, and \linkspell{Reverse Gravity}, each once per day, as a spell-like ability.

\textbf{Ultimate Breath (Su):} At 20th level, every time the Dragonfire Adept uses their breath weapon, they automatically win the game.
