%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\classentry{Druid}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\tagline{"Look deep into nature, and then you will understand everything better."}

\textbf{Alignment:} Neutral good, lawful neutral, neutral, chaotic neutral, or neutral evil.

\textbf{Races:} Any, though usually the races that live in the wils, such as Elves and Orcs, will naturally have more druids.

\textbf{Starting Gold:} 4d6x10 gp (140 gold)

\textbf{Starting Age:} As Cleric.

\textbf{Hit Die:} d8

The druid's class skills (and the key ability for each skill) are \linkskill{Concentration} (Con), \linkskill{Craft} (Int), \linkskill{Diplomacy} (Cha), \linkskill{Handle Animal} (Cha), \linkskill{Heal} (Wis), \linkskill{Knowledge} (nature) (Int), \linkskill{Listen} (Wis), \linkskill{Profession} (Wis), \linkskill{Ride} (Dex), \linkskill{Spellcraft} (Int), \linkskill{Spot} (Wis), \linkskill{Survival} (Wis), and \linkskill{Swim} (Str).

\textbf{Skills/Level:} 4 + Intelligence Bonus

\modebab{}
\goodfor{}
\poorref{}
\goodwil{}

\begin{fullcastingclasstable}
\levelone{\multicolumn{1}{p{5.5cm}}{Animal companion, Nature Sense, Wild Empathy} &  1 & -- & -- & -- & -- & -- & -- & -- & --}
\leveltwo{Woodland Stride &  2 & -- & -- & -- & -- & -- & -- & -- & --}
\levelthree{Trackless Step &  2 & 1 & -- & -- & -- & -- & -- & -- & --}
\levelfour{Resist Nature's Lure &  3 & 2 & -- & -- & -- & -- & -- & -- & --}
\levelfive{Wild Shape 1/day & 3 & 2 & 1 & -- & -- & -- & -- & -- & --}
\levelsix{Wild Shape 2/day &  3 & 3 & 2 & -- & -- & -- & -- & -- & --}
\levelseven{Wild Shape 3/day &  4 & 3 & 2 & 1 & -- & -- & -- & -- & --}
\leveleight{Wild Shape (Large) &  4 & 3 & 3 & 2 & -- & -- & -- & -- & --}
\levelnine{Venom Immunity &  4 & 4 & 3 & 2 & 1 & -- & -- & -- & --}
\levelten{Wild Shape 4/day &  4 & 4 & 3 & 3 & 2 & -- & -- & -- & --}
\leveleleven{Wild Shape (Tiny) & 5 & 4 & 3 & 3 & 2 & 1 & -- & -- & --}
\leveltwelve{Wild Shape (Plant) &  5 & 4 & 4 & 3 & 3 & 2 & -- & -- & --}
\levelthirteen{A Thousand Faces & 5 & 5 & 4 & 4 & 3 & 2 & 1 & -- & --}
\levelfourteen{Wild Shape 5/day &  5 & 5 & 4 & 4 & 4 & 3 & 2 & -- & --}
\levelfifteen{\multicolumn{1}{p{5.5cm}}{Timeless Body, Wild Shape (Huge)} &  5 & 5 & 4 & 4 & 4 & 3 & 2 & 1 & --}
\levelsixteen{Wild Shape (Elemental 1/day) &  5 & 5 & 5 & 4 & 4 & 3 & 3 & 2 & --}
\levelseventeen{-- &  5 & 5 & 5 & 5 & 4 & 4 & 3 & 2 & 1}
\leveleighteen{\multicolumn{1}{p{5.5cm}}{Wild Shape 6/day (Elemental 2/day)} &  5 & 5 & 5 & 5 & 5 & 4 & 3 & 3 & 2}
\levelnineteen{-- &  5 & 5 & 5 & 5 & 5 & 4 & 4 & 3 & 3}
\leveltwenty{\multicolumn{1}{p{5.5cm}}{Wild Shape (Elemental 3/day, Huge Elemental)} &  5 & 5 & 5 & 5 & 5 & 4 & 4 & 4 & 4}
\end{fullcastingclasstable}

\classfeatures

\textbf{Weapon and Armor Proficiency:} Druids are proficient with the following weapons: club, dagger, dart, quarterstaff, scimitar, sickle, shortspear, sling, and spear. They are also proficient with all natural attacks (claw, bite, and so forth) of any form they assume with wild shape (see below).

Druids are proficient with light and medium armor but are prohibited from wearing metal armor; thus, they may wear only padded, leather, or hide armor. (A druid may also wear wooden armor that has been altered by the \linkspell{Ironwood} spell so that it functions as though it were steel. See the \textit{ironwood} spell description) Druids are proficient with shields (except tower shields) but must use only wooden ones.

A druid who wears prohibited armor or carries a prohibited shield is unable to cast druid spells or use any of her supernatural or spell-like class abilities while doing so and for 24 hours thereafter.

\textbf{Spells:} A druid casts divine spells, which are drawn from the druid spell list. Her alignment may restrict her from casting certain spells opposed to her moral or ethical beliefs; see Chaotic, Evil, Good, and Lawful Spells, below. A druid must choose and prepare her spells in advance (see below).

To prepare or cast a spell, the druid must have a Wisdom score equal to at least 10 + the spell level. The Difficulty Class for a saving throw against a druid's spell is 10 + the spell level + the druid's Wisdom modifier.

Like other spellcasters, a druid can cast only a certain number of spells of each spell level per day. Her base daily spell allotment is given on Table: The Druid. In addition, she receives bonus spells per day if she has a high Wisdom score. She does not have access to any domain spells or granted powers, as a cleric does.

A druid prepares and casts spells the way a cleric does, though she cannot lose a prepared spell to cast a \textit{cure} spell in its place (but see Spontaneous Casting, below). A druid may prepare and cast any spell on the druid spell list, provided that she can cast spells of that level, but she must choose which spells to prepare during her daily meditation.

\textbf{Orisons:} In addition to their normal allotment of spells, a Druid can prepare a number of 0th level spells per day, known as "orisons". A Druid can prepare three orisons each day, and they can use any orison that they have prepared an unlimited number of times.

\textbf{Spontaneous Casting:} A druid can channel stored spell energy into summoning spells that she hasn't prepared ahead of time. She can "lose" a prepared spell in order to cast any \linkspell{Summon Nature's Ally I}{Summon Nature's Ally} spell of the same level or lower.

\textbf{Chaotic, Evil, Good, and Lawful Spells:} A druid can't cast spells of an alignment opposed to her own or her deity's (if she has one). Spells associated with particular alignments are indicated by the chaos, evil, good, and law descriptors in their spell descriptions.

\textbf{Druidic Languages:} A druid knows Druidic, a secret language known only to druids, which she learns upon becoming a 1st-level druid. Druidic is a free language for a druid; that is, she knows it in addition to her regular allotment of languages and it doesn't take up a language slot. Druids are forbidden to teach this language to nondruids. Druidic has its own alphabet.

\textbf{Animal Companion (Ex):} A druid gets an Animal as a Cohort starting at first level. The Druid gets +4 on Handle Animal checks with their Companion, and they can use the skill with their Companion as a Free Action. From levels 1 to 3 the animal has entirely typical stats. At levels 4 and above the animal maintains a CR of the Druid's level -2, just like a normal cohort. Advance the animal in whatever way seems appropriate to maintain its CR.

\textbf{Nature Sense (Ex):} A druid gains a +2 bonus on \linkskill{Knowledge} (nature) and \linkskill{Survival} checks.

\textbf{Wild Empathy (Ex):} A druid can improve the attitude of an animal. This ability functions just like a \linkskill{Diplomacy} check made to improve the attitude of a person. The druid rolls 1d20 and adds her druid level and her Charisma modifier to determine the wild empathy check result.

The typical domestic animal has a starting attitude of indifferent, while wild animals are usually unfriendly.

To use wild empathy, the druid and the animal must be able to study each other, which means that they must be within 30 feet of one another under normal conditions. Generally, influencing an animal in this way takes 1 minute but, as with influencing people, it might take more or less time.

A druid can also use this ability to influence a magical beast with an Intelligence score of 1 or 2, but she takes a -4 penalty on the check.

\textbf{Woodland Stride (Ex):} Starting at 2nd level, a druid may move through any sort of undergrowth (such as natural thorns, briars, overgrown areas, and similar terrain) at her normal speed and without taking damage or suffering any other impairment. However, thorns, briars, and overgrown areas that have been magically manipulated to impede motion still affect her.

\textbf{Trackless Step (Ex):} Starting at 3rd level, a druid leaves no trail in natural surroundings and cannot be tracked. She may choose to leave a trail if so desired.

\textbf{Resist Nature's Lure (Ex):} Starting at 4th level, a druid gains a +4 bonus on saving throws against the spell-like abilities of fey.

\textbf{Wild Shape (Su):} At 5th level, a druid gains the ability to turn herself into any Small or Medium animal and back again once per day. Her options for new forms include all creatures with the animal type. This ability functions like the \linkspell{Polymorph} spell, except as noted here. The effect lasts for 1 hour per druid level, or until she changes back. Changing form (to animal or back) is a standard action and doesn't provoke an attack of opportunity.

The form chosen must be that of an animal the druid is familiar with. 

A druid loses her ability to speak while in animal form because she is limited to the sounds that a normal, untrained animal can make, but she can communicate normally with other animals of the same general grouping as her new form. (The normal sound a wild parrot makes is a squawk, so changing to this form does not permit speech.)

A druid can use this ability more times per day at 6th, 7th, 10th, 14th, and 18th level, as noted on Table: The Druid. In addition, she gains the ability to take the shape of a Large animal at 8th level, a Tiny animal at 11th level, and a Huge animal at 15th level.

The new form's Hit Dice can't exceed the character's druid level.

At 12th level, a druid becomes able to use wild shape to change into a plant creature with the same size restrictions as for animal forms. (A druid can't use this ability to take the form of a plant that isn't a creature.)

At 16th level, a druid becomes able to use wild shape to change into a Small, Medium, or Large elemental (air, earth, fire, or water) once per day. These elemental forms are in addition to her normal wild shape usage. In addition to the normal effects of wild shape, the druid gains all the elemental's extraordinary, supernatural, and spell-like abilities. She also gains the elemental's feats for as long as she maintains the wild shape, but she retains her own creature type.

At 18th level, a druid becomes able to assume elemental form twice per day, and at 20th level she can do so three times per day. At 20th level, a druid may use this wild shape ability to change into a Huge elemental.

\textbf{Venom Immunity (Ex):} At 9th level, a druid gains immunity to all poisons. 

\textbf{A Thousand Faces (Su):} At 13th level, a druid gains the ability to change her appearance at will, as if using the \linkspell{Alter Self} spell, but only while in her normal form.

\textbf{Timeless Body (Ex):} After attaining 15th level, a druid no longer takes ability score penalties for aging and cannot be magically aged. Any penalties she may have already incurred, however, remain in place.

Bonuses still accrue, and the druid still dies of old age when her time is up.

\textbf{Ex-Druids:} A druid who ceases to revere nature, changes to a prohibited alignment, or teaches the Druidic language to a nondruid loses all spells and druid abilities (including her animal companion, but not including weapon, armor, and shield proficiencies). She cannot thereafter gain levels as a druid until she atones (see the \linkspell{Atonement} spell description).
