%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\classentry{Fire Mage}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\tagline{"Yes, fire \textbf{is} cool."}

A Fire Mage is someone who burns their own soul out to burn the bodies of others. Tactically, they shine against groups of enemies, because fires spread across the battlefield like a plague.

\textbf{Alignment:} Fire is a destructive force, and a lot of Fire Mages are Chaotic. But they don't have to be.

\textbf{Races:} Fire Mages appear in all races, though significant portions of many races live in areas where being a practicing Fire Mage is basically illegal. 

\textbf{Starting Gold:} 6d6x10 gp (210 gold)

\textbf{Starting Age:} As Rogue.

\textbf{Hit Die:} d8

\textbf{Class Skills:} The Fire Mage's class skills (and the key ability for each skill) are \linkskill{Bluff} (Cha), \linkskill{Climb} (Str), \linkskill{Craft} (Int), \linkskill{Concentration} (Con), \linkskill{Disguise} (Cha), \linkskill{Escape Artist} (Dex), \linkskill{Handle Animal} (Cha), \linkskill{Intimidate} (Cha), \linkskill{Jump} (Str), \linkskill{Listen} (Wis), \linkskill{Move Silently} (Dex), \linkskill{Profession} (Wis), \linkskill{Ride} (Dex), \linkskill{Search} (Int), \linkskill{Spellcraft} (Int), \linkskill{Spot} (Wis), \linkskill{Survival} (Wis), and \linkskill{Use Rope} (Dex).

\textbf{Skills/Level:} 4 + Intelligence Bonus

\modebab{}
\goodfor{}
\goodref{}
\goodwil{}

\begin{classtable}
\levelone{Fire Resistance, Fire Burst, Fire Bolts, Impress Flames, Fire Magic}
\leveltwo{Ignite}
\levelthree{Piercing Flames, Hand of Fire}
\levelfour{Fire Immunity, Smokeless Flame}
\levelfive{Fireballs}
\levelsix{Mindfire}
\levelseven{Visions of Flame}
\leveleight{Soul of Cinders}
\levelnine{Sculpt Flames}
\levelten{Conflagration}
\leveleleven{Beacon, Firewalk}
\leveltwelve{Bonds of Fire}
\levelthirteen{Fire Clouds}
\levelfourteen{Searing Light, Ray of Light}
\levelfifteen{Sending, Rain of Fire}
\end{classtable}

\classfeatures

\textbf{Weapon and Armor Proficiency:} Fire Mages are proficient with all simple weapons, as well as the whip, all martial axes, and all sizes and varieties of scimitar (including falchions). Fire Mages are proficient with light armor but not with shields of any kind.

\textbf{Fire Resistance (Ex):} A Fire Mage has a Resistance to Fire equal to twice his level.

\textbf{Fire Burst (Sp):} As a standard action, a Fire Mage can emit a burst of flame from his body, striking all creatures and objects within 10' of his position except himself. This burst of flames inflicts 1d6 of fire damage, with an allowed Reflex Save for half (DC 10 + half Level + Charisma Modifier).

\textbf{Fire Bolts (Sp):} A Fire Mage can throw bolts of fire as an attack action. A Fire Bolt tavels out to short range, and inflicts 1d6 of Fire damage per level. A Fire Bolt strikes its target with a ranged touch attack.

\textbf{Impress Flames (Ex):} Every time a Fire Mage inflicts Fire damage on any target, whether with his class abilities or another source of fire, he inflicts an amount of extra Fire Damage equal to his class level or his Charisma modifier, whichever is less.

\textbf{Fire Magic (Ex):} A Fire Mage is considered to have every spell with the Fire Descriptor on his spell list for the purpose of activating magic items.

\textbf{Ignite (Sp):} As a standard action, a 2nd level Fire Mage can cause any creature or object to burst into flame. A creature on fire suffers 1d6 of Fire damage per round (the Mage's Impress Flames ability applies to each round of course), and the creature can attempt to put itself out with a DC 15 Reflex save. This ability can be used out to Medium range, and it always hits.

\textbf{Piercing Flames (Ex):} From 3rd level on, a Fire Mage's Fire cuts through Fire Resistance, hardness, and Immunity. No more than half of the damage inflicted by his fire damage can be negated by hardness or immunity or resistance to Fire. In addition, the Fire Mage ignores the first 5 points of Fire Resistance that a target has.

\textbf{Hand of Fire (Su):} A 3rd level Fire Mage can set fire to their own body, causing them to count as armed at all times, even with unarmed attacks. The Fire Mage also causes an extra 1d6 of Fire damage with all melee attacks.

\textbf{Fire Immunity (Ex):} A 4th level Fire Mage is immune to Fire.

\textbf{Smokeless Flame (Sp):} A 4th level Fire Mage can create fires that produce no heat and do not burn. These fires can be anything from the size of a torch to a bonfire, and produce light accordingly. Each lasts until the next time the sun rises. Smokeless Flame can be created anywhere within Medium range.

\textbf{Fireballs (Sp):} A 5th level Fire Mage can hurl explosive fire anywhere within Long Range as a Full Round Action. This Fire explodes into a 20' radius burst and inflicts 1d6 of Fire Damage per level. All creatures within the area are entitled to a Reflex save to halve damage (DC 10 + half Level + Charisma Modifier).

\textbf{Mindfire (Sp):} A 6th level Fire Mage can start a Fire in a creature's mind, duplicating the effects of rage or confusion for a number of minutes equal to his Level. The victim must be within Medium Range, and is entitled to a Will Save to negate this effect (DC 10 + half Level + Charisma Modifier). This is a Mind influencing Compulsion effect.

\textbf{Visions of Flame (Sp):} A 7th level Fire Mage can contact other plane to communicate with the denizens of the Elemental Plane of Fire. A Fire Mage is in no danger of becoming insane or damaged by this experience.

\textbf{Soul of Cinders (Su):} An 8th level Fire Mage has burnt his soul to ash, and is no longer susceptible to Energy Drain or Fear.

\textbf{Sculpt Flames (Sp):} A 9th level Fire Mage can create delicate shapes and walls made of fire. The Fire is fully shapeable, but cannot pass through more than 2 squares per level. Any creature passing through a square with fire in it suffers 1d6 of fire damage per level. A creature which is in a square that is being filled with fire is entitled to a Reflex Save (DC 10 + half Level + Charisma Modifier) to move to the nearest non-flaming square as an immediate action. These fires persist for 1 round per level. Alternately, the Fire Mage can replicate a wall of fire which persists for 1 minute per level.

\textbf{Conflagration (Sp):} At 10th level, a Fire Mage can surround himself with a nimbus of flames that extends for 10' in all directions from his person. All other targets in this area suffer a d10 of Fire Damage per level, but are entitled to a Reflex Save (DC 10 + half Level + Charisma Modifier). In addition, a Fire Mage can cast fireshield at will (Hot Shield only).

\textbf{Beacon (Sp):} An 11th level Fire Mage can create a magically permanent bonfire as a standard action. He always knows exactly where each Beacon he has created is and will know if it is put out by any means.

\textbf{Firewalk (Sp):} At 11th level a Fire Mae can walk into any fire large enough to fit his person and appear in any other fire that is likewise of sufficient size anywhere on any plane of existence. The Fire Mage must know where the target fire is. The Fire Mage can take any number of willing creatures or carried objects that are also able to fit in both flames.

\textbf{Bonds of Fire (Sp):} A 12th level Fire Mage can craft solid fire and entrap a victim in it. The bonds will immobilize a creature which fails a Reflex Save (DC 10 + half Level + Charisma Modifier), and will entangle the creature unless it succeeds in its save by more than 5. A creature can attempt to escape by taking a Full round action to make a Strength or Escape Artist test with a DC equal to the Use Rope Skill Result of the Fire Mage. The victim suffers 20 points of Fire Damage per round, and the bonds of fire last until the victim escapes or the Fire Mage dismisses them.

\textbf{Fire Clouds (Sp):} As a Full Round Action, a 13th level Fire Mage can create huge billowing clouds of Fire. The Fire Clouds must be created within Long range, and persist for 3 rounds whether they are still in range or not. The cloud is shapeable, and covers at most 3 10ft cubes per Level. Each round, everyone and everything inside the cloud suffers 1d6 of Fire damage per level, but is entitled to a Reflex save for half damage (DC 10 + half Level + Charisma Modifier).

\textbf{Searing Light (Sp):} A 14th level Fire Mage can call levels of illumination that are painful and destructive as the unmitigated baleful glare of the sun itself. All darkness within 5 miles is dispelled, and everything is illuminated. All undead suffer a 10 points of damage per round. All creatures specifically vulnerable to light suffer 10 damage per round (thus, vampires suffer 20 damage per round). All creatures are dazzled. Creatures must pass a Fortitude save (DC 10 + half Level + Charisma Modifier) every minute or become blind for the remainder of the effect. Creatures that are blinded when the effect ends are entitled to another Fort save to get their vision back, but if they fail this save the blinding is permanent. This effect lasts until the Fire Mage dismisses it or he is incapacitated.

\textbf{Ray of Light (Sp):} As an attack action, a 14th level Fire Mage can fire a ray of Light at any target within Short Range. It inflicts 1d6 of Light Damage per level if it hits with a Ranged Tuuch Attack. Undead take 10 extra damage. Creatures specifically vulnerable to Light suffer an additional 10 damage.

\textbf{Sending (Sp):} A 15th level Fire Mage can send a message, as the sending spell to any creature on any plane of existence with a standard action and receive a reply even if they are on different planes of existence.

\textbf{Rain of Fire (Sp):} At 15th level, the Fire Mage can open the skies and dump raw inferno upon all who would oppose him. The fires inflict 1d6 of Fire Damage per level, and victims are permitted a Reflex save (DC 10 + half level + Charisma Modifier). The Fire Mage chooses which squares are struck with fire, and any number of squares within Long range can be targeted at once.
