%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\classentry{Jester}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\tagline{"Well no, but if I was doing it to anyone \textbf{else}, you'd think it was funny."}

To be a Jester is to see the joke in every tragedy. For them, life's a party, and most poor bastards are not invited. They live hard, play hard, and laugh hard knowing that at any moment their life might be cut short by an uncaring world. Jesters may play at being buffoons, but each is a student of life and of people, and they understand not only what makes people laugh, but what makes them cry. As adventurers, they often appreciate baubles and magical trinkets as much as anyone else, but their main goal is \textit{to have fun.} When fighting enemies, their sense of humor takes a macabre and dark turn, becoming cruel and vicious to better demoralize their foe. As followers of the Laughing God Who Has No Temples, they are generally disrespectful atheists who wander the world looking for excitement and amusement, righting wrongs or committing crimes as the mood takes them.

\textbf{Alignment:} A Jester may be of any non-Lawful alignment.

\textbf{Races:} Jesters appear in all cultures and all races have need of buffoons.

\textbf{Starting Gold:} 6d4x10 gp (150 gold)

\textbf{Starting Age:} As Rogue.

\textbf{Hit Die:} d6

\textbf{Class Skills:} The Jester's skills (and the key ability for each skill) are \linkskill{Balance} (Dex), \linkskill{Bluff} (Cha), \linkskill{Climb} (Str), \linkskill{Concentration} (Con), \linkskill{Craft} (Int), \linkskill{Diplomacy} (Cha), \linkskill{Disable Device} (Int), \linkskill{Disguise} (Cha), \linkskill{Gather Information} (Cha), \linkskill{Hide} (Dex), \linkskill{Intimidate} (Cha), \linkskill{Jump} (Str), \linkskill{Listen} (Wis), \linkskill{Move Silently} (Dex), \linkskill{Perform} (Cha), \linkskill{Profession} (Wis), \linkskill{Search} (Int), \linkskill{Sense Motive} (Wis), \linkskill{Sleight of Hand} (Dex), \linkskill{Spellcraft} (Int), \linkskill{Spot} (Wis), \linkskill{Swim} (Str), \linkskill{Tumble} (Dex), and \linkskill{Use Magic Device} (Cha).

\textbf{Skills/Level:} 6 + Intelligence Bonus

\modebab{}
\poorfor{}
\goodref{}
\poorwil{}

\begin{minorcastingclasstable}
\levelone{Harlequin's Mask, Poison Use & -- & -- & -- & -- & -- & --}
\leveltwo{Laugh It Off & 0 & -- & -- & -- & -- & --}
\levelthree{+1d6 Sneak Attack, Power Slide & 1 & -- & -- & -- & -- & --}
\levelfour{Jester's Fient & 2 & 0 & -- & -- & -- & --}
\levelfive{Cruel Comment & 3 & 1 & -- & -- & -- & --}
\levelsix{+2d6 sneak Attack & 3 & 2 & -- & -- & -- & --}
\levelseven{Sight Gag & 3 & 2 & 0 & -- & -- & --}
\leveleight{Low Comedy, Slapstick & 3 & 3 & 1 & -- & -- & --}
\levelnine{+3d6 sneak Attack & 3 & 3 & 2 & -- & -- & --}
\levelten{Jack-in-the-Box King & 3 & 3 & 2 & 0 & -- & --}
\leveleleven{+4d6 sneak Attack & 3 & 3 & 3 & 1 & -- & --}
\leveltwelve{Killer Clown & 3 & 3 & 3 & 2 & -- & --}
\levelthirteen{+5d6 sneak Attack & 3 & 3 & 3 & 2 & 0 & --}
\levelfourteen{Annoy the Gods & 3 & 3 & 3 & 3 & 1 & --}
\levelfifteen{+6d6 sneak Attack & 4 & 3 & 3 & 3 & 2 & --}
\levelsixteen{Prat Fall & 4 & 4 & 3 & 3 & 2 & 0}
\levelseventeen{+7d6 sneak Attack & 4 & 4 & 4 & 3 & 3 & 1}
\leveleighteen{Last Trick & 4 & 4 & 4 & 4 & 3 & 2}
\levelnineteen{+8d6 sneak Attack & 4 & 4 & 4 & 4 & 4 & 3}
\leveltwenty{Eternal Trickster & 4 & 4 & 4 & 4 & 4 & 4}
\end{minorcastingclasstable}

\classfeatures

\textbf{Weapon and Armor Proficiency:} Jesters are proficient with light armor but not with shields of any kind. A Jester is proficient with no weapons, but suffers no attack penalty for using a weapon with which they are not proficient or which is made for a character of a different size than themselves. Even, perhaps especially, improvised weapons may be used without the usual -4 penalty.

\textbf{Spellcasting:} The Jester is a Spontaneous Arcane Spellcaster. A Jester casts spells from the Jester Spell List (below). A Jester automatically knows every spell on his spell list. He can cast any spell he knows without preparing them ahead of time, provided that spell slots of an appropriate level are still available. To cast a Jester spell, he must have a Charisma at least equal to 10 + the Spell level. The DC of the Jester's spells is Charisma based and the bonus spells are Charisma based.

\textbf{Cantrips:} A Jester's 0th level spells, known as "cantrips", can be used an unlimited number of times. As with other jester spells, a jester knows all cantrips on the jester spell list.

\textbf{Ignore Components:} A Jester may cast spells from the Jester list without using material components, regardless of whether they are costly or not. This has no effect on any spells that a Jester casts from any other spell-list.

\textbf{Poison Use (Ex):} A Jester may prepare, apply, and use poison without any chance of poisoning himself.

\textbf{Harlequin's Mask (Ex):} As long as a Jester's face is painted, masked, or adorned in the manner of a harlequin or other comedic figure, he is immune to compulsion effects.

\textbf{Laugh It Off (Ex):} Fate protects fools and little children, and Jesters certainly adopt the role of fools. At 2nd level, a Jester may add his Charisma modifier as a morale bonus to his saves.

\textbf{Power Slide (Ex):} If a 3rd level Jester takes damage from an attack, he may allow herself to be flung backwards, thereby lessening the impact. He may make a Balance check with a DC equal to the damage inflicted and if she succeeds, he suffers only half damage. This is a skill check, not a Saving Throw, so abilities such as Evasion do not apply. He is moved away from the source of damage by 5' for every 5 points of damage (or part there of) negated in this way. If there is not enough space for him to move, he suffers a d6 of damage for each square not moved. If he passes through an occupied square, the Jester would have to make a tumble check to avoid attacks of opportunity.

If this ability is gained from another class, then the Jester may choose to increase or decrease the total distance moved by 50\% (so a Power Slide that negated 12 points of damage can cause him to move 5', 10', or 15' at her choice).

\textbf{Sneak Attack (Ex):} At 3rd level, a Jester gains the ability to make sneak attacks as a rogue would. At 3rd level, his sneak attacks inflict 1 extra d6 of damage, and this increases by 1d6 at levels 6, 9, 11, 13, 15, 17, and 19.

\textbf{Jester's Feint (Ex):} At 4th level, a Jester learns to shock and unnerve his enemies by throwing unexpected objects at them. At a swift action, he may toss a brightly colored object in the square of an enemy with a Sleight of Hand Check opposed by the enemy's Spot check. If it succeeds, the enemy is denied his Dex bonus for the Jester's next attack.

Some Jesters use objects with magical or alchemic effects that act in an enemy's square to use with this ability, while others use colored balls, fruit, pieces of cloth or scarves, or other cast-off materials that fit the requirement of being brightly colored. Wealthy, desperate, or foolish Jesters sometime used coins or gems.

\textbf{Cruel Comment (Ex):} At 5th level, the Jester has learned to say extremely funny but hurtful things about others. As a swift action, the Jester can make a Bluff check opposed by the target's level plus Charisma check. If the target fails this check, he suffers a -4 to attack rolls, saves, and all other checks. This effect lasts 3 rounds. This is a language-dependant ability.

\textbf{Sight Gag (Ex):} At 7th level, the Jester may apply the Silent Spell and Still Spell metamagics spontaneously to his spells, but only if he casts them as full-round actions. This ability only works with spells on the Jester list, and it does not increase the spell's level or slot used.

\textbf{Low Comedy (Ex):} By using this ability, a Jester of 8th level or higher can double the armor check penalty of an opponent within 50 feet that he hits with a ranged touch attack. Using this ability is an attack action and counts as a thrown weapon. The penalty can be restored to its normal value with 10 minutes and a bar of soap.

\textbf{Slapstick (Ex):} At 8th level, any successful sneak attack also inflict a -2 Dex penalty to an enemy for one round.

\textbf{Jack-in-the-Box King (Sp):} Twice per day, a 10th level Jester may use \linkspell{Fabricate} or \linkspell{Major Creation} as a spell-like ability, but only if he is constructing weapons or traps.

\textbf{Killer Clown (Ex):} At 12th level, so long as he meets the requirements of his Harlequin's face ability, the Jester can make a special Intimidate check as a move action. If successful, this check causes the enemy to suffer the panicked condition for a round per Jester level. This is a mind-effecting fear effect.

\textbf{Annoy the Gods (Su):} As world-class pranksters, Jesters must learn to avoid the curses and transformations of enemies with a sense of humor. Any time a 14th level Jester has spent at least one round as the victim of an effect that could be removed by a \linkspell{break enchantment} effect, the effect is removed.

\textbf{Prat Fall (Ex):} At 16th level, any time a Jester strikes an enemy with a sneak attack, the Jester can make a free Trip attack that does not provoke an Attack of Opportunity. This ability cannot be used on any one enemy more than once a round. The Jester may not be tripped if this fails, and it may be used with ranged sneak attacks. The Jester may substitute his Dexterity modifier for his Strength modifier for the opposed test to trip his foe.

\textbf{Last Trick (Su):} At 18th level, the Jester can turn even his death into a joke. Any time the Jester is killed or knocked unconscious, one of his spells known is cast as if it were spell in a \linkspell{Contingency} effect.

\textbf{Eternal Trickster (Ex):} At 20th level, the Jester can become a personification of the Laughing God Who has No Temples. While meeting the requirements of his Harlequin's Mask ability, he does not age and is under the effects of a \linkspell{Mind Blank} effect.

\textbf{Jester Spells:}

\begin{description*}
\item[0th Level:] \linkspell{Alarm}, \linkspell{Detect Magic}, \linkspell{Detect Poison}, \linkspell{Grease}, \linkspell{Unseen Servant}, \linkspell{Ventriloquism}.

\item[1stLevel:] \linkspell{Fire Trap}, \linkspell{Glitterdust}, \linkspell{Magic Mouth}, \linkspell{Misdirection}, \linkspell{Pyrotechnics}, \linkspell{Reduce Person}, \linkspell{Sleet Storm}, \linkspell{Hideous Laughter}, \linkspell{Teleport Trap}, \linkspell{Touch of Idiocy}.

\item[2nd Level:] \linkspell{Baleful Transposition}, \linkspell{Explosive Runes}, \linkspell{Glyph of Warding}, \linkspell{Rage}, \linkspell{Rope Trick}, \linkspell{Secret Page}, \linkspell{Snake Sigil}.

\item[3rd Level:] \linkspell{Feeblemind}, \linkspell{Minor Globe of Invulnerability}, \linkspell{Modify Memory}, \linkspell{Faithful Hound}, \linkspell{Nightmare}, \linkspell{Servant Horde}, \linkspell{Shrink Item}.

\item[4th Level:] \linkspell{Globe of Invulnerability}, \linkspell{Greater Glyph of Warding}, \linkspell{Insect Plague}, \linkspell{Persistent Image}, \linkspell{Symbol of Weakness}, \linkspell{Tree Shape}.

\item[5th Level:] \linkspell{Interposing Hand}, \linkspell{Energy Immunity}, \linkspell{Eyebite}, \linkspell{Repulsion}, \linkspell{Screen}, \linkspell{Symbol of Insanity}, \linkspell{Telekinesis}.

\item[6th Level:] \linkspell{Creeping Doom}, \linkspell{Insanity}, \linkspell{Refuge}, \linkspell{Symbol of Sleep}, \linkspell{Symbol of Stunning}, \linkspell{Temporal Stasis}.
\end{description*}
