%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\classentry{Knight}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\tagline{"Do you hear me you big lizard? You unhand that young man this instant!"}

Knights are more than a social position, in fact many knights don't have any social standing at all. These knight errants uphold the values of honor, and make a name for themselves adventuring.

\textbf{Playing a Knight:} A Knight has the potential to dish out tremendous damage to a single opponent, and it is tempting to think of them as monster killers. However, it is best to realize in advance that the Knight \textit{does not} often realize their tremendous damage output. The threat of the Knight's Designate Opponent ability is just that -- a threat. A Knight excels at \textit{defensive} tasks, and attacking a Knight is often one of the least effective options an opponent might exercise.

So by making it be a logical combat action for your opponents to attack your party's defensive expert, you've really contributed a lot to the party. A Knight can take a lot of the heat off the rest of the party. So don't get frustrated if enemies constantly interrupt your Designate Opponent action -- that's the whole point. A Knight's role is to protect others, and the best way you can do that is to provide a legitimate threat to your opponents.

\textbf{Alignment:} Many Knights are Lawful. But not all of them. You have to maintain your code of conduct, but plenty of Chaotic creatures can do that too.

\textbf{Races:} Knights require a fairly social background to receive their training. After all, a solitary creature generally has little use for honor. As such, while Knights often spend tremendous amounts of time far from civilization, they are almost exclusively recruited from the ranks of races that are highly urban in nature.

\textbf{Starting Gold:} 6d6x10 gp (210 gold)

\textbf{Starting Age:} As Fighter.

\textbf{Hit Die:} d12

\textbf{Class Skills:} The Knight's class skills (and the key ability for each skill) are \linkskill{Climb} (Str), \linkskill{Craft} (Int), \linkskill{Diplomacy} (Cha), \linkskill{Handle Animal} (Cha), \linkskill{Intimidate} (Cha), \linkskill{Jump} (Str), \linkskill{Knowledge} (History, Nobility, and Geography) (Int), \linkskill{Listen} (Wis), \linkskill{Perform} (Cha), \linkskill{Ride} (Dex), \linkskill{Sense Motive} (Wis), \linkskill{Spot} (Wis), and \linkskill{Swim} (Str).

\textbf{Skills/Level:} 4 + Intelligence Bonus

\goodbab{}
\poorfor{}
\poorref{}
\goodwil{}

\begin{classtable}
\levelone{Designate Opponent, Mounted Combat, Code of Conduct}
\leveltwo{Damage Reduction}
\levelthree{Energy Resistance, Speak to Animals}
\levelfour{Immunity to Fear, Knightly Spirit}
\levelfive{Command}
\levelsix{Defend Others, Quick Recovery}
\levelseven{Bastion of Defense, Draw Fire}
\leveleight{Mettle, Spell Shield}
\levelnine{Sacrifice}
\levelten{Knightly Order}
\end{classtable}

\classfeatures

\textbf{Weapon and Armor Proficiency:} Knights are proficient with all simple weapons and Martial Weapons. Knights are proficient with Light, Medium, and Heavy Armor, Shields, and Great Shields.

\textbf{Designate Opponent (Ex):} As a Swift Action, a Knight may mark an opponent as their primary foe. This foe must be within medium range and be able to hear the Knight's challenge. If the target creature inflicts ay damage on the Knight before the Knight's next turn, the attempt fails. Otherwise, any attacks the Knight uses against the opponent \textit{during} her next turn inflict an extra d6 of damage for each Knight level. This effect ends at the end of her next turn, or when she has struck her opponent a number of times equal to the number of attacks normally allotted her by her Base Attack Bonus.

\textit{Example:} Vayn is a 6th level Knight presently benefiting from a \linkspell{Haste} spell, granting her an extra attack during a Full Attack action. On her turn she designates an Ettin as her primary opponent, and the Ettin declines to attack her during the ensuing turn. When her next turn comes up, she uses a Full Attack and attacks 3 times. The first two hits inflict an extra 6d6 of damage, and then she designates the Ettin as her opponent again. It won't soon ignore her!

\textbf{Mounted Combat:} A Knight gains Mounted Combat as a bonus feat at 1st level. If she already has Mounted Combat, she may gain any Combat feat she meets the prerequisites for instead.

\textbf{Code of Conduct:} A Knight must fight with honor even when her opponents do not. Indeed, a Knight subscribes to honor to a degree far more than that which is strictly considered necessary by other honorable characters. Actions which even hint at the appearance of impropriety are anathema to the Knight:

\begin{itemize*}
\item A Knight must not accept undo assistance from allies even in combat. A Knight must refuse bonuses from Aid Another actions.
\item A Knight must refrain from the use poisons of any kind, even normally acceptable poisons such as blade toxins.
\item A Knight may not voluntarily change shape, whether she is impersonating a specific creature or not.
\item A Knight may not sell Magic Items.
\end{itemize*}

A Knight who fails to abide by her code of conduct loses the ability to use any of her Knightly abilities which require actions until she atones.

\textbf{Damage Reduction (Ex):} A Knight trains to suffer the unbearable with chivalry and grace. At 2nd level, she gains Damage Reduction of X/-, where X is half her Knight level, rounded down.

\textbf{Energy Resistance (Ex):} A Knight may protect herself from energy types that she expects. As a Swift Action, a 3rd level Knight may grant herself Energy Resistance against any energy type she chooses equal to her Knight Level plus her Shield Bonus. This energy resistance lasts until she spends a Swift Action to choose another Energy type or her Shield bonus is reduced.

\textbf{Speak to Animals (Ex):} A Knight can make herself understood by beasts. Her steed always seems to be able to catch the thrust of anything she says. A 3rd level Knight gains a bonus to any of her Ride and Handle Animal checks equal to half her Knight Level. In addition, there is no limit to how many tricks she can teach a creature, and her Handle Animal checks are not penalized for attempting to get a creature to perform a trick it does not know.

\textbf{Immunity to Fear (Ex):} At 4th level, a Knight becomes immune to [Fear] effects.

\textbf{Knightly Spirit (Ex):} As a Move Equivalent Action, a 4th level Knight may restore any amount of attribute damage or drain that she has suffered.

\textbf{Command:} A Knight gains \linkfeat{Command} as a bonus feat at level 5.

\textbf{Defend Others (Ex):} A 6th level Knight may use her own body to defend others. Any ally adjacent to the Knight gains Evasion, though she does not.

\textbf{Quick Recovery (Ex):} If a 6th level Knight is \textit{stunned} or \textit{dazed} during her turn, that condition automatically ends at the end of that turn, even if the duration would normally be longer.

\textbf{Bastion of Defense (Ex):} A 7th level Knight can defend others with great facility. All adjacent allies except the Knight gain a +2 Dodge bonus to their Armor Class and Reflex Saves.

\textbf{Draw Fire (Ex):} A 7th level Knight can exploit the weaknesses of unintelligent opponents. With a Swift Action, she may pique the interest of any mindless opponent within medium range. That creature must make a Willpower Save (DC 10 + ½ Hit Dice + Constitution Modifier) or spend all of its actions moving towards or attacking the Knight. This effect ends after a number of rounds equal to the Knight's class level.

\textbf{Mettle (Ex):} An 8th level Knight who succeeds at a Fortitude Partial or Willpower Partial save is not affected at all (basically like Evasion, but for Fortitude and Willpower saves).

\textbf{Spell Shield (Ex):} An 8th level Knight gains Spell Resistance of 5 + her character level. This Spell Resistance is increased by her shield bonus to AC if she has one.

\textbf{Sacrifice (Ex):} As an immediate action, a 9th level Knight may make herself the target of an attack or targeted effect that targets any creature within her reach.

\textbf{Knightly Order:} What is a powerful Knight without a descriptive adjective? Upon reaching 10th level, a Knight \textit{must} join or found a Knightly order. From this point on, she may ignore one of the prerequisites for joining a Knightly Order prestige class. In addition, becoming a member of an order has special meaning for a 10th level Knight, and she gains an ability related to the order she joins. Some sample orders are listed below:

\begin{itemize*}
\item \textbf{Angelic Knight} The Angelic Knights are a transformational order that attempts to live by the precepts of the upper planes. An Angelic Knight gains wings that allow her to Fly 60ft with perfect maneuverability. Also an Angelic Knight benefits from \linkspell{Protection From Evil} at all times.
\item \textbf{Bane Knight} The Bane Knights stand for running around burning the countryside with extreme burning. Bane Knights are immune to fire and do not have to breathe. In addition, a Bane Knight may set any unattended object on fire with a Swift Action at up to Medium Range.
\item \textbf{Chaos Knight} Chaos Knights stand for madness and Giant Frog. With the powers of Giant Frog, they can Giant Frog. Also their natural armor bonus increases by +5 and they are immune to \textit{Sleep} effects.
\item \textbf{Dragon Knight} Dedicated to the Platinum Dragon, the Dragon Knights serve love and justice in equal measure as dishes to those who need them. A Dragon Knight gains a +5 bonus to Sense Motive and any armor she wears has an enhancement bonus of 2 higher than normal (it also gains a platinum sheen in the process, and as a side effect a Dragon Knight is never dirty for more than a few seconds).
\item \textbf{Elemental Knight} The Elemental Knights may be dedicated to a particular element, or somehow dedicated to all of them. An Elemental Knight can \linkspell{Planeshift} at will to any Inner plane or the Prime Material plane. Also, she is immune to \textit{stunning} and ignores the harmful planar effects of the Inner Planes.
\item \textbf{Fey Knight} Using the powers of the Sprites, the Fey Knight has many fairy strengths. Firstly, she gains DR 10/Iron. Also, any of her attacks may do non-lethal damage at any time if this is desired. Also she never ages and does not need to drink.
\item \textbf{Great Knight} Clad in opulent armor, the Great Knight cares only for her own power. The Great Knight gains a +4 bonus on Disarm or Sunder tests, and gains a +4 Profane bonus to her Strength.
\item \textbf{Hell Knight} Forged in the sulphurous clouds of Hell, the Hell Knight is bathed in an evil radiance. In addition to being granted a ceremonial weapon made of green steel, a Hell Knight gains the coveted See In Darkness ability of the Devils. Also, she has an inherent ability to know what every creature within 60' her of finds most repugnant.
\item \textbf{Imperial Knight} The great Empire needs champions able to unswervingly support its interests, and the Imperial Knight is one of the best. She may impose a \linkspell{Zone of Truth} at will as a Supernatural ability, and all of her attacks are Lawfully aligned. Also, she continuously benefits from \linkspell{Magic Circle Against Chaos}.
\end{itemize*}
