%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\classentry{Sorcerer}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\tagline{"Darkness beyond twilight, crimson beyond blood that flows, buried in the flow of time is where your power grows."}

Sorcerers are characters that have found a way to fuse some sort of magical power into their own soul, and now they use that magical power to cast spells. Sometimes this comes from a strange ancestry, sometimes there's a magical transformation, a divine edict, a lurking otherworldly influence, a magical contract, just about any explanation that you can imagine. The thing to keep in mind is that, unlike with Clerics and Druids, once a Sorcerer has been infused with their power it can't just be pulled away. Many Sorcerers end up rebelling against those who once granted them power, and sometimes even surpassing them.

Sorcerers don't necessarily have any formal magical training, and the process of obtaining a sorcerous path isn't always the same from path to path, or from one Sorcerer to the next within the same path. The consistent element among all Sorcerers is that they have more spell energy to throw around each day than any other spellcaster of the same level. Usually this leads them to being a little more indiscriminate about it.

\textbf{Playing a Sorcerer:} A Sorcerer needs a high Charisma score. Other stats are nice, but everything the Sorcerer does it powered by their Charisma score, so that's always top priority. You only gain a limited number of spells known besides your path spells, but you get more spell slots per day than any other class. So you'll be casting many of your spells more than once in a day; try to select spells that are very general. Sorcerers aren't very physically tough, so it's usually best to just "stay in the back" like a wizard does and launch spells from afar.

\textbf{Alignment:} Every alignment has its share of Sorcerers, though some individual Sorcerer paths are more prone to one alignment or another.

\textbf{Races:} Every single race has sorcerers of every path, though some races are more prone to one path or another. Magical races do not necessarily have to follow the path associated with their kind.

\textbf{Starting Gold:} 2d6x10 gp (70 gold)

\textbf{Starting Age:} As Rogue.

\textbf{Hit Die:} d6

\textbf{Class Skills:} The Sorcerer's class skills (and the key ability for each skill) are \linkskill{Bluff} (Cha), \linkskill{Concentration} (Con), \linkskill{Craft} (Int), \linkskill{Knowledge} (Arcana) (Int), \linkskill{Profession} (Wis), and \linkskill{Spellcraft} (Int).

\textbf{Skills/Level:} 4 + Intelligence Bonus

\poorbab{}
\poorfor{}
\poorref{}
\goodwil{}

\begin{fullcastingclasstable}
\levelone{Sorcerous Path, Sorcerous Secret & 3 & -- & -- & -- & -- & -- & -- & -- & --}
\leveltwo{--& 4 & -- & -- & -- & -- & -- & -- & -- & --}
\levelthree{Sorcerous Secret & 5 & -- & -- & -- & -- & -- & -- & -- & --}
\levelfour{--& 6 & 3 & -- & -- & -- & -- & -- & -- & --}
\levelfive{Sorcerous Secret & 6 & 4 & -- & -- & -- & -- & -- & -- & --}
\levelsix{--& 6 & 5 & 3 & -- & -- & -- & -- & -- & --}
\levelseven{Sorcerous Secret & 6 & 6 & 4 & -- & -- & -- & -- & -- & --}
\leveleight{--& 6 & 6 & 5 & 3 & -- & -- & -- & -- & --}
\levelnine{Sorcerous Secret & 6 & 6 & 6 & 4 & -- & -- & -- & -- & --}
\levelten{--& 6 & 6 & 6 & 5 & 3 & -- & -- & -- & --}
\leveleleven{Sorcerous Secret & 6 & 6 & 6 & 6 & 4 & -- & -- & -- & --}
\leveltwelve{--& 6 & 6 & 6 & 6 & 5 & 3 & -- & -- & --}
\levelthirteen{Sorcerous Secret & 6 & 6 & 6 & 6 & 6 & 4 & -- & -- & --}
\levelfourteen{--& 6 & 6 & 6 & 6 & 6 & 5 & 3 & -- & --}
\levelfifteen{Sorcerous Secret& 6 & 6 & 6 & 6 & 6 & 6 & 4 & -- & --}
\levelsixteen{--& 6 & 6 & 6 & 6 & 6 & 6 & 5 & 3 & --}
\levelseventeen{Sorcerous Secret & 6 & 6 & 6 & 6 & 6 & 6 & 6 & 4 & --}
\leveleighteen{--& 6 & 6 & 6 & 6 & 6 & 6 & 6 & 5 & 3}
\levelnineteen{Sorcerous Secret & 6 & 6 & 6 & 6 & 6 & 6 & 6 & 6 & 4}
\leveltwenty{Ultimate Sorcery & 6 & 6 & 6 & 6 & 6 & 6 & 6 & 6 & 6}
\end{fullcastingclasstable}

\classfeatures

\textbf{Weapon and Armor Proficiency:} Sorcerers are proficient with all Simple weapons. They are not proficient with any form of Armor or Shield, and such things can interfere with their spellcasting as well (see \linksec{Arcane Spell Failure}).

\textbf{Spells:} A Sorcerer casts Arcane spells from their path list, as well as spells from the Wizard spell list. Any spell that the Sorcerer knows can be cast as long as they have a remaining slot available, Sorcerers do not need to prepare their spells ahead of time.

To cast a spell, a Sorcerer must have a Charisma score equal to at least 10 + the spell level. The Difficulty Class for a saving throw against a Sorcerer's spell is 10 + the spell level + the Sorcerer's Charisma modifier.

Like other spellcasters, a Sorcerer can cast only a certain number of spells of each spell level per day. His base daily spell allotment is given on Table: The Sorcerer. In addition, she receives bonus spells per day if she has a high Charisma score.

A Sorcerer's selection of spells is extremely limited. They begin play knowing all the 0th and 1st level spells of their Path. At each level above first they can select an additional spell off of the Wizard Spell List of any spell level that they have available.

Unlike other arcane spellcasters, a Sorcerer does not need to provide materials components for any of her spells unless there is a costly material component price. The Sorcerer's path provides the additional energy to replace any minor material components.

\textbf{Cantrips:} In addition to their normal spells per day, each Sorcerer knows three cantrips according to their Sorcerous Path. These cantrips can be cast as often as the Sorcerer desires. At third level the Sorcerer can select one additional Cantrip to know, from the Wizard Spell List. 

\textbf{Sorcerous Path (Ex):} At 1st level a Sorcerer must select what Path their sorcery comes from. Each Sorcerer path grants a special ability, some additional class skills, and a list of automatically known spells. Here are some Paths, though you could probably write others if you wanted:

\begin{description}
\item[Aberrant Power] You get power from beyond the spheres, from another world, another time. Your magic is bizarre and strange, outside of what others of your race have experienced.

\textbf{Scion of Madness (Ex):} You may act normally while dazed or confused. This ability does not function if a dazed status was inflicted upon you by a spell that you cast yourself.

\textbf{Path Skills:} Decipher Script, Knowledge (Dungeoneering), Knowledge (The Planes), Swim

\begin{description*}
\item[Cantrips] Dancing Lights, Daze, Resistance
\item[1st] Disguise Self, Obscuring Mist, Sleep
\item[2nd] Blur, Rope Trick, Touch of Idiocy
\item[3rd] Confusion, Deep Slumber, Displacement
\item[4th] Dimension Door, Black Tentacles, Fear
\item[5th] Plane Shift, Nightmare, Teleport
\item[6th] Eyebite, Mass Suggestion, Shadow Walk
\item[7th] Insanity, Prismatic Spray, Teleport Object
\item[8th] Dimensional Lock, Maze, Prismatic Wall
\item[9th] Freedom, Gate, Prismatic Sphere
\end{description*}

\item[Abyssal Might] You are tainted and inspired by demons, or perhaps a specific demon. Your power brings ruin and devastation to the world.

\textbf{Path Skills:} Disguise, Knowledge (The Planes), Knowledge (Religion), Survival

\textbf{Electricity Immunity (Ex):} You have immunity to electricity effects and damage.

\begin{description*}
\item[Cantrips] Guidance, Resistance, Touch of Fatigue
\item[1st] Align Weapon, Lightning Bolt, Darkness
\item[2nd] Alter Self, Shatter, Web
\item[3rd] Chain Lightning, Deeper Darkness, Stinking Cloud
\item[4th] Charm Monster, Polymorph, Summon 2d6 Dretches (treat as Summon Monster IV)
\item[5th] Feeblemind, Plane Shift, True Seeing
\item[6th] Blade Barrier, Insanity, Reverse Gravity
\item[7th] Fire Storm, Greater Teleport, Power Word: Stun
\item[8th] Dimensional Lock, Greater Planar Binding, Power Word: Kill
\item[9th] Energy Drain, Implosion, Wish
\end{description*}

\item[Arcane Blood] You have natural magic.

\textbf{Path Skills:} Spot, Listen, Perform

\textbf{Arcane Sight (Su):} You have a permanent \linkspell{Arcane Sight} effect.

\begin{description*}
\item[Cantrips] Arcane Mark, Mage Hand, Message
\item[1st] Color Spray, Greater Dispelling, Greater Magic Weapon
\item[2nd] Arcane Lock, Hypnotic Pattern, Rope Trick
\item[3rd] Bestow Curse, Illusory Script, Shrink Item
\item[4th] Break Enchantment, Mage's Sword, Rainbow Pattern
\item[5th] Secret Chest, Sending, Waves of Exhaustion
\item[6th] Contingency, Disintegrate, Repulsion
\item[7th] Forcecage, Phase Door, Prismatic Spray
\item[8th] Discern Location, Maze, Symbol of Insanity
\item[9th] Gate, Shades, Storm of Vengeance
\end{description*}

\item[Celestial Power] You have the power of the sacred lands. Your magic may have been blessed by Archons or Eladrin, or it may have come to you by much sketchier means such as drinking Celestial Ambrosia or stealing heavenly fire.

\textbf{Path Skills:} Diplomacy, Knowledge (Religion), Knowledge (The Planes), Sense Motive

\textbf{Know Evil (Su):} You can see the alignment auras of creatures within 60' of you as if you had been concentrating on an appropriate detect alignment spell or benefited from a divine version of true seeing. This gives you no special ability to see through illusions of any kind however.

\begin{description*}
\item[Cantrips] Guidance, Light, Resistance
\item[1st] Daylight, Magic Circle Against Evil, Sleep
\item[2nd] Glitterdust, Lesser Restoration, Searing Light
\item[3rd] Dismissal, Prayer, Remove Curse
\item[4th] Restoration, Spell Resistance, Sunbeam
\item[5th] Hallow, Plane Shift, Sunburst
\item[6th] Banishment, Heal, Mass Suggestion
\item[7th] Greater Restoration, Power Word Stun, Resurrection
\item[8th] Earthquake, Mass Heal, Power Word Blind
\item[9th] Gate, Implosion, Mass Hold Monster
\end{description*}

\item[Destined Magic] Fate has conspired to give you magic. It probably has some kind of plan for what you are supposed to do with it as well. You can decide for yourself whether you have any choice in the matter.

\textbf{Path Skills:} Escape Artist, Sense Motive, Sleight of Hand

\textbf{A Higher Purpose (Su):} Once per day, you may reroll one of your Saving Throws. You must keep the second roll, even if it is lower.

\begin{description*}
\item[Cantrips] Bane, Guidance, Resistance
\item[1st] Aid, Augury, True Sight
\item[2nd] Bestow Curse, Heroism, Slow
\item[3rd] Freedom of Movement, Lesser Geas, Prayer
\item[4th] Banishment, Divination, Greater Heroism
\item[5th] Geas, Heroes' Feast, Legend Lore
\item[6th] Find the Path, Foresight, Heal
\item[7th] Discern Location, Limited Wish, Resurrection
\item[8th] Greater Scrying, Moment of Prescience, Protection from Spells
\item[9th] Soul Bind, Time Stop, True Resurrection
\end{description*}

\item[Draconic Power] You have gained the natural powers of the dragon, whether naturally or through theft. The blood of Tiamat now flows through your veins.

\textbf{Path Skills:} Climb, Jump, Handle Animal

\textbf{Energy Immunity (Ex):} Depending upon the type of dragon from whom you draw the most power, select one type of Energy (Fire, Acid, Electricity, or Cold). You are immune to that kind of energy damage.

\begin{description*}
\item[Cantrips] Endure Elements, Speak with Animals, Ventriloquism
\item[1st] Obscuring Mist, Spider Climb, Water Breathing
\item[2nd] Darkness, Locate Object, Wind Wall
\item[3rd] Plant Growth, Suggestion, Stinking Cloud
\item[4th] Control Winds, Hallucinatory Terrain, Wall of Ice
\item[5th] Freezing Fog, Insect Plague, Mirage Arcana
\item[6th] Command Plants, Find the Path, Move Earth
\item[7th] Control Weather, Summon Djinn (as a Brass Dragon), Sunburst
\item[8th] Discern Location, Foresight, Whirlwind
\item[9th] Elemental Swarm, Refuge, Shapechange
\end{description*}

\item[Earth Power] You have the elemental powers of Earth, whether from ancient hanky panky with the Dao or directly from the earth beneath your feet.

\textbf{Path Skills:} Balance, Climb, Diplomacy

\textbf{Tremor Sense (Su):} You have Tremor Sense out to 10'. At 7th level, this extends to 20', and every odd numbered level after that the radius increases by 5 feet.

\begin{description*}
\item[Cantrips] Detect Snares and Pits, Magic Stone, Mending
\item[1st] Grease, Longstrider, Pass Without Trace
\item[2nd] Heat Metal, Meld into Stone, Soften Earth and Stone
\item[3rd] Blink, Shrink Item, Stone Shape
\item[4th] Stone Tell, Transmute Rock to Mud, Transmute Mud to Rock
\item[5th] Move Earth, Plane Shift, Wall of Stone
\item[6th] Flesh to Stone, Stone to Flesh, Wall of Iron
\item[7th] Greater Teleport, Limited Wish, Reverse Gravity
\item[8th] Earthquake, Iron Body, Trap the Soul
\item[9th] Elemental Swarm (Earth only), Gate, Wish
\end{description*}

\item[Fire Power] You have the powers of Fire, possibly as a blessing from the Efreet.

\textbf{Path Skills:} Knowledge (Nobility), Knowledge (The Planes), Decipher Script, Sense Motive

\textbf{Fire Immunity (Ex):} You have immunity to fire.

\begin{description*}
\item[Cantrips] Burning Hands, Detect Magic, Light
\item[1st] Enlarge Person, Fireball, Reduce Person
\item[2nd] Daylight, Invisibility, Scorching Ray
\item[3rd] Delayed Blast Fireball, Major Image, Wall of Fire
\item[4th] Fireshield, Greater Invisibility, Minor Creation
\item[5th] Ethereal Jaunt, Incendiary Cloud, Planeshift
\item[6th] Greater Scrying, Permanent Image, Sunburst
\item[7th] Fire Seeds, Greater Teleport, Limited Wish
\item[8th] Binding, Meteor Swarm, Trap the Soul
\item[9th] Gate, Storm of Vengeance, Wish
\end{description*}

\item[Fey Power] You use the magic of the Fey. The real and the unreal blend together at your whim.

\textbf{Path Skills:} Disguise, Handle Animal, Ride

\textbf{Fairy Trod (Su):} You may move unimpeded by vegetation and other natural difficult terrain, and leave no tracks in a natural surrounding. You cannot be perceived or tracked by scent.

\begin{description*}
\item[Cantrips] Flare, Ghost Sound, Light
\item[1st] Color Spray, Magic Aura, Silent Image
\item[2nd] Invisibility, Glitterdust, Whispering Wind
\item[3rd] Displacement, Major Image, Shrink Item
\item[4th] Dimension Door, Greater Invisibility, Rainbow Pattern
\item[5th] Feeblemind, Seeming, Teleport
\item[6th] Flesh to Stone, Permanent Image, Sympathy
\item[7th] Greater Teleport, Irresistible Dance, Project Image
\item[8th] Demand, Scintillating Pattern, Screen
\item[9th] Freedom, Teleportation Circle, Weird
\end{description*}

\item[Infernal Power] The power of the Hells flows through your arteries and veins. A dark fire of treachery and deceit powers your every waking moment.

\textbf{Path Skills:} Diplomacy, Knowledge (Nobility), Knowledge (The Planes), Sense Motive

\textbf{See in Darkness (Ex):} Like a Devil, you can see in the absence of light and even in magical darkness as if it was well illuminated with no particular range limitations.

\begin{description*}
\item[Cantrips] Flare, Guidance, Open/Close
\item[1st] Charm Person, Daze Monster, Tongues
\item[2nd] Blindness/Deafness, Detect Thoughts, Resist Energy
\item[3rd] Crushing Despair, Magic Circle against Good or Chaos, Suggestion
\item[4th] Charm Monster, Dream, Fire Shield
\item[5th] Mind Fog, Plane Shift, Seeming
\item[6th] Geas, Greater Arcane Sight, Sympathy
\item[7th] Antipathy, Greater Scrying, Greater Teleport
\item[8th] Demand, Mass Charm Monster, Screen
\item[9th] Dominate Monster, Gate, Imprisonment
\end{description*}

\item[Shadow Power] You channel the power of the plane of shadow, creating strange effects that blur the line between reality and illusion.

\textbf{Path Skills:} Escape Artist, Sleight of Hand, Stealth

\textbf{See in Darkness (Su):} You see in shadowy illumination and even full darkness as easily as fully lit areas, even in magically created areas of darkness.

\begin{description*}
\item[Cantrips] Dancing Lights, Ghost Sound, Prestidigitation
\item[1st] Color Spray, Mage Armor, Silent Image
\item[2nd] Darkness, Minor Image, Summon Swarm
\item[3rd] Deeper Darkness, Major Image, Stinking Cloud
\item[4th] Black Tentacles, Hallucinatory Terrain, Shadow Conjuration
\item[5th] Cloud Kill, Persistent Image, Shadow Evocation
\item[6th] Acid Fog, Programmed Image, Shadow walk
\item[7th] Greater Shadow Conjuration, Phase Door, Simulacrum
\item[8th] Mind Blank, Scintillating Pattern, Greater Shadow Evocation
\item[9th] Disjunction, Shades, Weird
\end{description*}

\item[Undead Power] You have the ever living power of the living dead. Like Mum-Ra.

\textbf{Path Skills:} Heal, Knowledge (History), Knowledge (Religion), Stealth

\textbf{Rebuke Undead (Su):} You can channel negative energy like a Cleric of an Evil god of your level.

\begin{description*}
\item[Cantrips] Disrupt Undead, Inflict Minor Wounds, Mending
\item[1st] Cause Fear, Inflict Moderate Wounds, Obscuring Mist
\item[2nd] Desecrate, False Life, Ghoul Touch
\item[3rd] Animate Dead, Gentle Repose, Vampiric Touch
\item[4th] Death Ward, Enervation, Phantasmal Killer
\item[5th] Create Undead, Finger of Death, Harm
\item[6th] Circle of Death, Legend Lore, Undeath to Death
\item[7th] Control Undead, Create Greater Undead, Resurrection
\item[8th] Mass Harm, Mind Blank, Symbol of Death
\item[9th] Energy Drain, True Resurrection, Wail of the Banshee
\end{description*}

\item[Time Power] For every thing there is a purpose, a time, and a season. Your magic has found its time and its season. It is to you to find for it a purpose.

\textbf{Path Skills:} Handle Animal, Heal, Survival

\textbf{Always in Time (Su):} Once per day you may reroll an Initiative check. The second roll must be taken even if it is lower.

\begin{description*}
\item[Cantrips] Daze, Mending, Touch of Fatigue
\item[1st] Erase, Ray of Enfeeblement, True Strike
\item[2nd] Shatter, Slow, Touch of Idiocy
\item[3rd] Gentle Repose, Haste, Sepia Snake Sigil
\item[4th] Dimension Door, Hold Monster, Waves of Fatigue
\item[5th] Break Enchantment, Fabricate, Permanency
\item[6th] Circle of Death, Disintegrate, Move Earth
\item[7th] Delayed Blast Fireball, Sequester, Vision
\item[8th] Binding, Moment of Prescience, Temporal Stasis
\item[9th] Foresight, Refuge, Time Stop
\end{description*}

\end{description}

\textbf{Sorcerous Secret:} At every odd class level (1st, 3rd, etc), the Sorcerer selects a Sorcerous Secret from among the following list:

\begin{description*}

\item[Arcane Blast (Su):] As an attack action, the Sorcerer can make a Short Ranged Touch Attack that deals 1d6 damage per level. The damage is of a type determined by the Sorcerer's Path, either Acid, Cold, Electric, Fire, or Physical (this can be an electric bolt, flame blobs, flying rocks, astral warping, whatever flavor fits the path).

\item[Armored Casting (Ex):] The Sorcerer can now cast her spells in Light Armor without Arcane Spell Failure, and she gains Light Armor Proficiency. This ability can be selected a second time, granting Medium Armor Casting (and Proficiency), and a third time to grant Heavy Armor Casting (and Proficiency).

\item[Arcane Infusion (Su):] The sorcerer gains a basic magic item bonus as a continual effect on themselves.

\item[Arcane Piercing (Su):] When dealing damage of any kind, the Sorcerer can choose to ignore an amount of Energy Resistance, DR, and/or Hardness equal to their character level. If she selects this a second time she can even pierce through an Immunity to a damage type, dealing half damage to targets that would normally be immune.

\item[Chaotic Soul (Su):] When the Sorcerer casts a spell of any spell level other than her highest, she may subtract 2 from its effective caster level and then add 1d6 to its effective caster level. If the die rolls a 1, a completely unexplained magical effect occurs instead of the spell, as though she had used a Rod of Wonder (the spell slot is still expended). The targeting for the effect is as close to the spell's original targeting as possible within the parameters of the wondrous effect.

\item[Claws of the Ancestors (Ex):] The Sorcerer's heritage manifests as pointy bits made of the Sorcerer's own body. She gains two primary claws and a secondary bite as natural weapons, which deal damage appropriate for the Sorcerer's size (1d6 for medium Sorcerers). These are magic weapons (with a +1 enhancement bonus per three character levels, rounded up) and they use the Sorcerer's Charisma bonus instead of his Strength bonus for all purposes. Once per round, if the Sorcerer hits with any of her natural weapons, she may apply one touch-range spell he knows with that weapon (expending the appropriate spell slot as normal).

\item[Extra Spell (Ex):] The Sorcerer learns one additional spell from the Wizard spell list. This spell can be of any spell level except for the Sorcerer's highest spell level. Every time the Sorcerer gains a level they can re-select what spell this ability grants, including selecting a higher level spell if their maximum spell level just went up. This ability can be selected more than once.

\item[Immortality (Ex):] The Sorcerer's path makes her immortal for whatever reason (mastery of time, heart of a dragon, angelic blessing, etc). She might or might not visibly age, but it does not affect her ability scores either way (and any existing age modifiers are removed). If she does age there's probably some ritual that can be done to restore her appearance to a younger state. The Sorcerer doesn't suffer any negative effects from being brought back from the dead. If the Sorcerer is at least 12th level and dies, she is automatically affected by Reincarnate after one day, except that she always retains her old race.

\item[Familiar (Ex):] A Sorcerer can turn a normal Animal into a familiar. Doing so takes 24 hours and uses up magical materials that cost 100 gp. The Sorcerer chooses the kind of familiar she gets. She can select any Animal of a size smaller than her own as the base creature. The creature's type becomes Magical Beast, and it gains a 10 for all mental attributes. The animal familiar can speak one language, selected from any of the Sorcerer's automatic languages according to their race. The familiar always has at least as many hit points and hit dice as the Sorcerer does, though if it would normally have more than that it keeps the higher amount. Its class skills are Listen, Spot, Survival, and all of the Sorcerer's Path Skills. It can also use the Sorcerer's base saves in place of its own if that would give it a higher total save bonus.

The familiar is probably pretty useless at fighting, and doesn't count as a Cohort. The main benefit of the familiar is that it can put all its skill points into a skill you don't have and then use that skill for you. Also it can fly or climb or whatever based on its animal type, so it can also do some simple scouting. If the familiar dies, it can be returned to life in any of the normal ways, or the Sorcerer can obtain a new one by performing a new ritual. The Sorcerer can also dismiss a familiar to get a new one if they need to, without having to kill the old one. It goes back to being just a normal animal.

\item[Improved Familiar (Ex):] (Requires Familiar) The Sorcerer's familiar improves greatly, becoming a full Cohort. Advance the familiar as necessary in whatever way you like to give it the proper CR. Unlike a normal familiar, an improved familiar always uses its own Hit Dice, Hit Points, and Saves according to whatever progression you're using for it. It can also be any animal of the Sorcerer's size or less (instead of having to be one size smaller). It's still a Magical Beast with an Intelligence of 6 that can speak at least one language though.

Since this option required another, your Improved Familiar also gains a Resistance Bonus to Saves and an Enhancement Bonus to Natural Armor (both equal to one third its level, rounded up). An Improved Familiar can also hold items in their paws and/or mouth (depending on animal) and use them just as well as if they had thumbs and crap, so they can fire little bows and use daggers and whatever, like they were in a Redwall book. It's totally adorable really, and it gives them +2 on Charisma Checks. The Sorcerer must be at least 6th level to gain an Improved Familiar.

\item[Planar Cohort (Ex):] The Sorcerer can gain some sort of extra-planar creature (an Outsider or Elemental) as their Cohort. It uses all the normal rules for Cohorts. The Sorcerer must be at least 6th level to select this option.

\item[Shield Casting (Ex):] The Sorcerer can now cast her spells while using a shield without chance of spell failure. She must still have one hand free to perform the Somatic component of the spell, if any, so she either needs to use a Buckler or not hold a weapon in hand to cast spells while using a shield.

\item[Skill Mastery (Ex):] The Sorcerer can Take 10 with her Path Skills, even if the situation would not normally allow her to do so.

\end{description*}

\textbf{Ultimate Sorcery (Ex):} Whenever a 20th level Sorcerer cast a spell, she automatically wins the game.
