%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\classentry{Soulborn}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\tagline{"Do you know what it means when a man has a sword made of blue soulfire? It means he can kill you with a sword made of blue soulfire."}

A Soulborn is a character whose soul is on completely arbitrary blue fire. This allows them to wreathe themselves in magical energies that give them jedi powers as if they had a number of magic items that enhanced their abilities. They can also create a lightsaber made out of soulfire that they use to chop things up.

\textbf{Necrocarnum Option:} Some characters will want to be powered by black soul fire instead of blue soul fire. That's fine. Such a character's soulfire is dim and spooky looking. Any references to shedding light like a torch are ignored for Necrocarnum Soulborn.

\textbf{Playing a Soulborn:} The Soulborn is a warrior whose weapon is as heavy as their soul. As such they can make a passable Strength Warrior or a passable Dexterity warrior. In addition they have a bunch of powers that work off of Charisma, so it is to be expected that Charisma would be their first or second best attribute. In most cases, a Soulborn's tactics are going to be to run up and smack things.

\textbf{Starting Age:} As Paladin

\textbf{Starting Equipment:} 5d6x10gp

\textbf{Alignment:} Soulborn can be any alignment, but they tend to be total douchebags about it regardless. Soulborn feel compelled to be "extreme" in their moral and ethical tirades and favor action and dickery rather than passively letting shit go. Even Neutral Soulborn get all tweaked up about "balance" and shit. They detect their alignment as if they were outsiders or clerics.

\textbf{Hit Die:} d10

\goodbab{}

\goodfor{}
\poorref{}
\goodwil{}

\textbf{Skill Points:} 4+Int

\textbf{Class Skills:} \linkskill{Balance}, \linkskill{Bluff}, \linkskill{Climb}, \linkskill{Diplomacy}, \linkskill{Hide}, \linkskill{Intimidate}, \linkskill{Jump}, \linkskill{Knowledge} (Any), \linkskill{Listen}, \linkskill{Move Silently}, \linkskill{Ride}, \linkskill{Search}, \linkskill{Sleight of Hand}, \linkskill{Spot}, \linkskill{Swim}, and \linkskill{Use Magic Device}.

\begin{extraclasstable}{\textbf{Chakras}}
\levelone{Soulblade, Soulmelds & 1}
\leveltwo{Resilient Soul, Soul Smite & 1}
\levelthree{Arcane Sight, Pressing Assault & 2}
\levelfour{Soulfire Burst & 2}
\levelfive{Better Soulmelds & 2}
\levelsix{Endless Smiting & 3}
\levelseven{Eternal Champion, Soul Arrow & 3}
\leveleight{Blood of Soulfire & 3}
\levelnine{Advanced Soulmelds & 4}
\levelten{Reborn Soul & 4}
\leveleleven{Parry Magic & 4}
\leveltwelve{Stunning Reaction & 5}
\levelthirteen{Astounding Soulmelds & 5}
\levelfourteen{Castigation, Souleater & 5}
\levelfifteen{Soul Cleave & 6}
\levelsixteen{Stunning Critical & 6}
\levelseventeen{Giant-size Soulmelds & 7}
\leveleighteen{Name of the Rose & 7}
\levelnineteen{Eternal Revolution & 7}
\leveltwenty{Inevitable Victory & 8}
\end{extraclasstable}

\classfeatures

\textbf{Weapon and Armor Proficiency:} Soulborn are proficient with all Simple and Martial Weapons, as well as with Light, Medium, and Heavy Armor. Also with Shields (but not Tower Shields).

\textbf{Soulblade (Su):} With a Swift Action, a Soulborn can call into existence a weapon of blue soul fire. The soulblade generally looks like a culturally appropriate bastard sword, but it may appear otherwise in the hands of Soulborn characters from other cultures or with different combat styles. The Soulblade is a light weapon that does 1d10 damage (for Medium) and has a threat range of 18-20. It has an enhancement bonus equal to one third of the character's level (round up). While out, the soulblade sheds light like a torch, and it vanishes the moment that it leaves the Soulborn's hand (though it can be recalled at a later time with a Swift Action). This weapon does Force damage and therefore ignores Hardness and is Super Effective against Incorporeal opponents.

\textbf{Soulmelds (Su):} A Soulborn has the ability to call upon a number of special blue glowing intangible wardrobe accessories that cause them to glow blue and gain additional powers. Each Soulmeld is unique, and should have its own name (check the Soulmeld chart below in order to name it). Each Soulmeld has a Basic bonus and a Special bonus. A Soulborn can only use a fraction of the Soulmelds they have at a time. At first level, the Soulborn "knows" 2 Soulmelds and learns an additional Soulmeld every time they gain a Soulborn level. Whenever they gain a level, they may trade one of the Soulmelds they know for a different Soulmeld. The number of Soulmelds that can actually be used at one time is the character's number of Chakras, which is 1 at first level, rising to 2 at 3rd, 3 at 6th, 4 at 9th, 5 at 12th, 6 at 15th, 7 at 17th, and finally 8 at 20th. It takes 1 minute of meditation to change which Soulmelds are available (up to the character's number of Chakras), but only a Swift Action to activate any or all of them. This activation can be combined with the action to activate a Soulblade if desired. Soulmelds shed light as a torch.

If a Soulmeld provides the ability to use an effect a limited number of times per day, the amount is reset only by having the sun rise or set, not by simply rearranging one's soulmelds. If a Soulmeld allows the casting of a spell, this spell is used as a Supernatural Ability and the caster level is the Soulborn's Level.

\textbf{Basic Bonuses:} Every Soulmeld (even Advanced or Giant-Size Soulmelds) has exactly one Basic Bonus, which is defined when the Soulmeld is learned:
\begin{itemize*}
\item Deflection bonus to AC (1/3 level, rounded up)
\item Resistance Bonus to Saving Throws (1/3 level, rounded up)
\item Enhancement Bonus to an attribute (1/3 level, rounded up)
\item Enhancement Bonus to a Skill other than Use Magic Device (Level + 2)
\item Enhancement Bonus to Natural Armor Bonus (1/3 Level, rounded up)
\item Spell Resistance (8 + Level)
\item Energy Resistance to one Energy type (3 points per level)
\end{itemize*}

\textbf{Special Bonuses:} Each Soulmeld has a Special Bonus. At higher levels, a Soulborn can select their Special Bonuses from the Better list, the Advanced List, or even the Giant-Size list. But at first, they have to make do with this list:
\begin{description*}
\item[Animal Summoning:] Once per day per Charisma modifier, the Soulborn can summon an animal with a CR half their own or less as a Standard Action. The summoned creature lasts 10 rounds.
\item[Bolt of Agony:] As a standard action, the Soulborn can shoot bolts of soulfire at things within 60'. It's a ranged touch attack that inflicts a d10 of Force damage and forces the target to make a Fortitude Save (DC 8 + half level + Charisma Modifier) or be dazed for 1 round.
\item[Counterspelling:] The Soulborn can, as an immediate action attempt to counter a spell they can see by making a Dispel check using their level as the caster level.
\item[Darkvision:] The Soulborn gains Darkvision 120'.
\item[Displacement:] The character has a 20\% Concealment Miss Chance.
\item[Enlargement:] The Soulborn grows as if from \linkspell{Enlarge Person}.
\item[Levitation:] The character can hover in the air as per the effects of the spell levitate.
\item[Nimbus of Light:] Sheds light as a Sunrod, once per day per 4 levels (rounded up), the Soulborn can use flashburst (SpC) targeted on themselves. They are immune to the blinding effects.
\item[Shrinking:] The Soulborn shrinks as if affected with \linkspell{Reduce Person}.
\item[Silence:] The Soulborn can cast silence on themselves at will. Each silence effect lasts until they dismiss it or the Soulmeld is swapped out, but they may only have one silence effect active at one time.
\item[Wall Walking:] The Soulborn can be attracted to any surface as if to the ground, allowing them to walk or run on walls and ceilings.
\end{description*}

\textbf{Resilient Soul:} A Soulborn of 2nd Level or higher adds their Charisma modifier to all their Saves. If they are for whatever reason already doing that, they get +1 to all saves instead.

\textbf{Soul Smite (Su):} A Soulborn of 2nd Level or higher can declare themselves to be Soul Smiting as a Swift Action. For the rest of the turn, the Soulborn adds their Charisma modifier to their attack rolls and their Soulborn level to their damage rolls on all attacks. When a Soul Smite is declared, it can't be declared again for 10 rounds.

\textbf{Arcane Sight (Su):} At 3rd level, a Soulborn benefits at all times from Arcane Sight.

\textbf{Pressing Assault (Ex):} From 3rd level on, when opponents use a 5' step within the threatened area of the Soulborn this provokes an Attack of Opportunity from them.

\textbf{Soulfire Burst (Su):} At 4th level, as a standard action the Soulborn can emit a burst of soulfire in all directions. This strikes all other creatures (not objects) within 15 feet with a d6 of Force damage per level. Targets are entitled to a Reflex save for half damage, with a DC of 10 + 1/2 Level + Charisma modifier. This cannot be used again for 10 rounds.

\textbf{Better Soulmelds:} From 5th level on, the Sulborn can select powers off the Better Soulmeld List when making Soulmelds:
\begin{description*}
\item[Blind Sight:] The character has Blindsight out to 60'
\item[Crushing Despair:] The Soulborn exudes an aura of palpable ennui. All opponents within 30' suffer a Morale Penalty to Attack Rolls, Damage Rolls, and Saves equal to 1/3 the character's level (round up)
\item[Force Armor:] The character gains an armor bonus of 7 + 1/3 level (round up).
\item[Invisibility:] The Soulborn can become invisible as per the spell invisibility as a Swift Action at will.
\item[Mental Bastion:] The character is immune to [Compulsions].
\item[Soul Lash:] The Soulborn's Soulblade provides Reach, and can still threaten adjacent opponents.
\item[Startling Power:] Once per turn, the Soulborn can force a target they have just struck for damage with a melee weapon to make a Fortitude Save (DC 9 + 1/2 level + Charisma Modifier) or become dazed for one turn.
\item[Super Speed:] The character's Land Speed is increased by 5' per level.
\item[Winged Flight:] The Soulborn is held aloft on energy wings or something, and gains a Flight speed equal to twice their land speed with Average Maneuverability.
\item[X-Ray Vision:] The Soulborn can see through things like they had a Ring of X-Ray Vision.
\end{description*}

\textbf{Endless Smiting:} At 6th level, a Soulborn does not have to wait 10 rounds between using Soul Smites.

\textbf{Eternal Champion:} At 7th level, a Soulborn doesn't age and suffers no level loss when returned from the dead.

\textbf{Soul Arrow (Su):} At 7th level, a Soulborn can fire bits of soulfire out of bows or crossbows instead of arrows or bolts. This soul arrows have an enhancement bonus of the character's level divided by 3 (round up) and do Force damage. If they hit, they also cause the target to shed light like a torch for one round, negating the effects of things like displacement or blur as if they had been outlined by \linkspell{Fairie Fire}.

\textbf{Blood of Soulfire (Su):} An 8th level Soulborn is immune to poison and when they suffer damage from physical attacks they cause 1 point of Force Damage to all creatures within 5' of them as Soulfire splashes out.

\textbf{Advanced Soulmelds:} From 9th level on, the Sulborn can select powers off the Advanced Soulmeld List when making Soulmelds:
\begin{description*}
\item[All Boogy-Boogy:] The Soulborn can create an aura of fear as a free action. All creatures within 10' of the Soulborn need to make a Will save against a Fear effect (DC 10 + 1/2 Level + Charisma Modifier) or become panicked for 4 rounds. Creatures who save cannot be affected by that Fear Aura for 24 hours.
\item[Aura of Luck:] Every ally within 30' of the Soulborn gets a Luck Bonus on Attack Rolls, Skill Checks, and Saving Throws equal to 1/3 the Soulborn's level (round up).
\item[Blink:] The Soulborn benefits from blink, and his own attacks do not suffer the miss chance.
\item[Demon Summoning:] The Soulborn can summon an Outsider once a day. The Outsider must have a CR two less than their level and sticks around for an hour as if having been summoned. The Outsider is of an alignment appropriate to the Soulborn.
\item[Dimension Door:] The Soulborn can teleport up to 120 feet as a Standard Action as per dimension door.
\item[Fireshield:] Any creature who strikes the Soulborn in melee while they are wreathed in soulfire takes d10 + Level in Force Damage unless they used a reach weapon to do it. The Soulborn is also immune to Forc Damage while this is up.
\item[Haste:] The character benefits from \linkspell{Haste} all the time.
\item[Mental Static:] The area within 40' of the Soulborn is considered distracting, and spellcasters must make a Concentration check to avoid losing spells cast. The DC is 10 + Spell Level + Charisma Modifier. And if a spellcaster has to make a Concentration check for any other reason, the DC is increased by the Soulborn's Charisma Modifier.
\item[Telekinesis:] The Soulborn can use telekinesis at will, with only the sustained force option available (no thrust).
\item[Time Ripple:] Once per turn as a free action, the Soulborn can cast slow. DC 9 + half Level + Charisma Modifier.
\end{description*}

\textbf{Reborn Soul (Su):} When a 10th level Soulborn has been dead for an entire day their body returns to life, with all parts replaced as if benefiting from resurrection.

\textbf{Parry Magic (Su):} If an 11th level Soulborn is aware of magic being cast that draws line of effect through their threatened area (including such spells that target them) and they have their Soulblade out, they can attempt to sever the strands of magic power as an Attack of Opportunity. They make a Dispel Check using their Level for the caster level on their Dispel Check.

\textbf{Stunning Reaction (Su):} If a 12th level Soulborn damages an opponent with an Attack of Opportunity, that opponent must make a Fortitude Save (DC 10 + half Level + Charisma Modifier) or be stunned for 1 turn.

\textbf{Astounding Soulmelds:} From 13th level on, the Sulborn can select powers off the Astounding Soulmeld List when making Soulmelds:
\begin{description*}
\item[Antimagic Cone:] The Soulborn emits a 60' long antimagic cone in front of themselves like a Beholder.
\item[Banishment:] The Soulborn can use banishment at will as a standard action. The DC is 10 + half Level + Charisma Modifier.
\item[Force Cage:] Once per day, the Soulborn can trap an enemy in a forcecage.
\item[Incorporeality:] The Soulborn is incorporeal.
\item[Mind Blank:] The Character benefits from mindblank all the time.
\item[Missed Step:] The Soulborn can, once per turn, teleport up to 60 feet as a free action.
\item[Open Gateway:] Once per day per Charisma Modifier, the Soulborn can open a gate (travel version only).
\item[Prism Strike:] Whenever the Soulborn strikes an enemy with Soulfire, they also have to roll as if struck with a prismatic spray.
\item[Teleport:] The Soulborn can, as a Standard Action, use greater teleport (self plus 50 pounds of crap only).
\item[Tentacles of Darkness:] Once per day per Charisma Modifier, the Soulborn can use \linkspell{Black Tentacles}.
\end{description*}

\textbf{Casigate (Su):} As an Immediate Action, a 14th level Soulborn can declare that their next attack within the following round hits. The die roll is merely a formality to see if it also critical hits.

\textbf{Souleater (Su):} A 14th level Soulborn can see souls hovering around dead bodies for about a week (or until that soul gets corrupted into a vengeful spirit or raised from the dead or bound into an object or whatever). They can choose to eat those souls, preventing them from being used for other tasks. Souls are delicious.

\textbf{Soul Cleave (Su):} As a Swift Action, the 15th level Soulborn can declare their next attack within the round to be a Soul Cleave, targeting the victim's soul directly. This attack is a touch attack, and also forces the victim to make a Fortitude Save (DC 10 + 1/2 Level + Charisma Modifier) or die. A soul cleave is only a special attack against a target that actually has a soul.

\textbf{Stunning Critical (Ex):} At 16th level, any time the Soulborn inflicts a critical hit, the victim is stunned for 1 round.

\textbf{Giant-Size Soulmelds:} From 17th level on, the Sulborn can select powers off the Giant-Size Soulmeld List when making Soulmelds:
\begin{description*}
\item[Eternal Winter:] The character gains the [Cold] Subtype and an area within 3 miles of them in all directions is reduced in temperature 3 categories. The Soulborn can cast frostburn at will.
\item[Giant Size:] The Character's size is Colossal, like they were the recipient of giant size.
\item[No U:] Whenever the character is targeted by a [Death] effect or Gaze attack and passes their Saving Throw, they may target the originator of that effect with the same effect.
\item[Personal Sun:] The character gains the [Fire] Subtype and an area within 3 miles of them in all directions is rised in temperature by 3 categories. The Soulborn can cast dessicate at will.
\item[Really Small:] The character's size is Diminutive, like they were the recipient of miniature size.
\item[The Silence:] A Silence Field emanates for 120' in all directions. The Soulborn can also cast \linkspell{Silence} at will.
\item[Word of Doom:] Every creature within 60' has to make a Fortitude Save or die (DC 10 + half level + Charisma Modifier). This is a full round action.`
\end{description*}

\textbf{Name of the Rose:} At 18th level, the character is the Rose Champion and can select an area on the Great Wheel that becomes divinely morphic according to their whim.

\textbf{Eternal Revolution:} A 19th level Soulborn has a literal army of petitioners to call upon, and gains the Army of Demons [Leadership] feat as a bonus feat.

\textbf{Inevitable Victory:} At 20th level, the Soulborn wins the game.

\begin{basictable}{Soulborn Soulmeld Names}{l l l l}
\textbf{d20} & \textbf{Color} & \textbf{Adjective} & \textbf{Noun}\\
1 & Azure & Crushing & Claws \\
2 & Aqueous & Rising & Mantle \\
3 & Beryl & Fierce & Cloak \\
4 & Blue & Dimming & Wings \\
5 & Cerulean & Clutching & Armor \\
6 & Cobalt & Grasping & Mask \\
7 & Electric & Gnawing & Gloves \\
8 & Indigo & Devastating & Sleeves \\
9 & Midnight & Expansive & Robe \\
10 & Navy & Protective & Helm \\
11 & Ocean & Secret & Hat \\
12 & Sapphire & Monstrous & Horns \\
13 & Teal & Horrendous & Gauntlets \\
14 & Turquoise & Wicked & Cape \\
15 & Ultramarine & Awesome & Belt \\
16 & Sky & Vengeful & Boots \\
17 & Steel & Depressive & Trail \\
18 & Cyan & Repetitive & Eyes \\
19 & Black & Gorgeous & Braids \\
20 & Red & Futile & Amulet\\
\end{basictable}