%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\classentry{Totemist}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\tagline{"My soul burns with the strength of the behir of my ancestors."}

Totemists are people whose souls are filled with an arbitrarily blue flame that causes them to channel the beast souls of the natural world. This being the natural world of myth, those beast souls are crazy crap like blink dogs, and they give the Totemist real magical powers.

A Totemist has powers that are comparable in strength to spells that are usable an unlimited number of times in a day. However, each power has a cool-down period that makes it unlikely to be used twice in the same battle. These powers are Charisma based, so it is to be expected that a Totemist will be putting Charisma as their primary attribute.

\textbf{Playing a Soulborn:} The Soulborn is a warrior whose weapon is as heavy as their soul. As such they can make a passable Strength Warrior or a passable Dexterity warrior. In addition they have a bunch of powers that work off of Charisma, so it is to be expected that Charisma would be their first or second best attribute. In most cases, a Soulborn's tactics are going to be to run up and smack things.

\textbf{Starting Age:} As Druid

\textbf{Starting Equipment:} 6d4x10gp

\textbf{Alignment:} Totemists can be of any alignment, but like Magical Beasts that alignment is largely to be taken with a grain of salt. They behave a lot like animals, so even if they are totally all chaotic evil and torture fools it's more like how cats spend an hour killing a mouse if they aren't hungry than any depraved sadism. Totemists hardly detect a non-neutral alignment at all even if they have one.

\textbf{Hit Die:} d8

\modebab{}

\poorfor{}
\poorref{}
\goodwil{}

\textbf{Skill Points:} 4+Int

\textbf{Class Skills:} \linkskill{Balance}, \linkskill{Bluff}, \linkskill{Climb}, \linkskill{Craft}, \linkskill{Diplomacy}, \linkskill{Handle Animal}, \linkskill{Hide}, \linkskill{Intimidate}, \linkskill{Jump}, \linkskill{Knowledge} (Any), \linkskill{Listen}, \linkskill{Move Silently}, \linkskill{Ride}, \linkskill{Search}, \linkskill{Sleight of Hand}, \linkskill{Spot}, \linkskill{Survival}, \linkskill{Swim}, and \linkskill{Use Magic Device}.

\begin{extraclasstable}{\textbf{Chakras}}
\levelone{\multicolumn{1}{p{7cm}}{Soulmelds, Basic Totems, Call Totems, Wild Empathy} & 2}
\leveltwo{Respect for the Dead, Woodland Stride & 3}
\levelthree{Arcane Sight & 3}
\levelfour{Better Soulmelds & 3}
\levelfive{Blood of Soulfire & 4}
\levelsix{Beast Companion & 4}
\levelseven{Advanced Soulmelds & 4}
\leveleight{Speak With Souls & 5}
\levelnine{Corpse Fashion, Reincarnate & 5}
\levelten{Astounding Soulmelds & 5}
\leveleleven{ & 6}
\leveltwelve{Autolife & 6}
\levelthirteen{Favor of the Totems & 6}
\levelfourteen{Exciting Soulmelds & 7}
\levelfifteen{Embody Totem & 7}
\levelsixteen{ & 8}
\levelseventeen{Giant-Size Soulmelds & 8}
\leveleighteen{Limitless Favor of the Totems & 8}
\levelnineteen{ & 9}
\leveltwenty{Triumph Promised by The Ancestors & 9}
\end{extraclasstable}

\classfeatures

\textbf{Weapon and Armor Proficiency:} Totemists are proficient with Simple Weapons, as well as the Trident, the Kukri, the shortsword, the gladius, the light and heavy pick, the shortbow, the longbow, the pincerstaff, the net, and the guisarme. Totemists are proficient with light and medium armor.

\textbf{Soulmelds (Su):} A Totemist has the ability to call upon a number of special blue glowing intangible yet vaguely beast-related wardrobe accessories that cause them to glow blue and gain additional powers. Each Soulmeld is unique, and should have its own name (check the Soulmeld chart below in order to name it). Each Soulmeld has a Basic bonus and a Totemic Power. A Totemist can only show a fraction of the Soulmelds they have at a time. At first level, the Totemist "knows" 3 Soulmelds and learns two additional Soulmelds every time they gain a Totemist level. The number of Soulmelds that can actually be used at one time is the character's number of Chakras, which is 2 at first level, rising to 3 at 2nd, 4 at 5th, 5 at 8th, 6 at 11th, 7 at 14th, 8 at 16th, and finally 9 at 19th. It takes 1 minute of meditation to change which Soulmelds are available (up to the character's number of Chakras), but only a Swift Action to activate and display any or all of them. Soulmelds shed light as a torch. Actually calling upon the Totem's power is usually a Standard Action.

\textbf{Basic Bonuses:} Every Soulmeld (even Advanced or Giant-Size Soulmelds) has exactly one Basic Bonus, which is defined when the Soulmld is learned:
\begin{itemize*}
\item Deflection bonus to AC (1/3 level, rounded up)
\item Resistance Bonus to Saving Throws (1/3 level, rounded up)
\item Enhancement Bonus to an attribute (1/3 level, rounded up)
\item Enhancement Bonus to a Skill other than Use Magic Device (Level + 2)
\item Enhancement Bonus to Natural Armor Bonus (1/3 Level, rounded up)
\item Spell Resistance (8 + Level)
\item Energy Resistance to one Energy type (3 points per level)
\end{itemize*}


\textbf{Basic Totems:} At first, each Soulmeld is attached to a Basic Totem, and the power delivered when called upon is as such:
\begin{description*}
\item[Ankheg:] Spit soul acid out to Short Range. Ranged Touch Attack. Inflicts 1d4 Acid damage/level and on the Totemist's next turn will inflict a similar amount unless the acid has been doused with vinegar or beer or something in the meantime.
\item[Ash Rat:] Heavy Smoke extends around the Totemist like \linkspell{Obscuring Mist}. The smoke lasts for 4 rounds, and creatures other than the Totemist suffer 1 point of Fire damage per round that they are in the ashy haze.
\item[Blood Ape:] The character increases in size by 1 size category, and their attributes are adjusted as normal. This change lasts for 4 rounds.
\item[Blood Hawks:] The Totemist makes a ranged touch attack against up to one enemy within Medium Range per level. Each target struck suffers 1d3 of Force damage and 2 points of Constitution Damage from blood loss.
\item[Dark Mantle:] As \linkspell{Darkness}, but all light is blocked and it provides complete concealment. Or 3e darkness if you prefer.
\item[Flame Snake:] Touch forces target to take 1d4 Fire Damage/level and to make a Fortitude Save against Poison or lose 1d6 Strength, Dexterity, and Constitution.
\item[Harpoon Spider:] A soul harpoon is sent after an enemy within Short Range. Ranged Touch Attack. On a hit, the target suffers 1d8 Force damage and must make a Fortitude save or be drawn as many squares towards the Totemist as the totemist feels like dragging them (as if bullrushed).
\item[Howler:] Scream causes Wisdom Damage. Burst out to Short Range. Will Save or suffer 1d6 Wisdom damage. Totemist is immune, this is a [Mind Affecting] [Sonic] effect.
\item[Krenshar:] Screech causes target within Short Range to be panicked for 1d4 rounds if they fail a Will save. This is a [Sonic] [Mind Affecting] [Fear] Effect.
\item[Light Hawk:] Rainbow colors shoot off into a Short Ranged Cone. Creatures in the cone must make a Will save or be stunned for 1d2 rounds. This is a [Mind Affecting] [Pattern].
\item[Mephit:] Breath Weapon of something weird and noxious. Extends to a cone out to Short Range. All creatures in the area must pass a Fortitude Save or be nauseated for 1d2 rounds.
\item[Owlbear:] Melee Touch Attack Pins target for 1 round.
\item[Rust Monster:] As \linkspell{Rusting Grasp}.
\item[Shocker Lizard:] Melee touch attack inflicts 1d8/level Subdual Electricity damage.
\item[Stirge:] Melee Touch Attack causes 1d4 damage/level and heals the Totemist an equal amount as to the damage inflicted on a living creature.
\item[Stun Worm:] Touch forces target to make a Fortitude save or be \linkcondition{Paralyzed} for a minute.
\end{description*}

\textbf{Call Totems (Su):} A Totemist can use the Totem Powers of any active Soulmelds any number of times in a day. However, upon calling upon such a Totem, they may not call on the same Totem for the next three rounds. So at first level a Totemist has only 2 Chakras bound, so they could call upon two different powers in the first two rounds of combat, but then they would be unable to use either one again in the next two rounds of combat, forcing them to fall back on weaponry or hiding. The Save DC of any save a Totem's power offers is 10 + 1/2 Level + Charisma Modifier. And every power is used at the Totemist's Character Level.

\textbf{Wild Empathy (Ex):} Totemists can use Handle Animal as if it was frickin Diplomacy and they were speaking the Queen's Bloody English with any Animal or Magical Beast, whether that creature has a language or not.

\textbf{Respect for the Dead (Ex):} At 2nd level, Totemists treat any armor made out of animal parts as if it was a lot easier to use, and reduce the Armor Check Penalty and Armor Stealth Penalty of such armors by 4, making it a lot more likely that they can move at full speed while wearing someone's mother as a breastplate.

\textbf{Woodland Stride (Ex):} Totemists of 2nd level and up are totally at home in natural environments, even really jacked up ones. They ignore naturally occurring difficult terrain and don't take damage from crap like thorns.

\textbf{Arcane Sight (Su):} At 3rd level, a Soulborn benefits at all times from Arcane Sight.

\textbf{Better Soulmelds:} At fourth level, each Soulmeld can be attached to a Better Totem, and the power delivered when called upon is as such:
\begin{description*}
\item[Ahuizotl:] Melee Touch Attack causes he target to be \linkcondition{Blind}.
\item[Aranea:] Can throw a soul Web. Creatures within or moving within a 15' burst within short range must make a Reflex Save or be entangled and anchored in place. An entangled creature may make an Escape Artist or Strength check (DC 20) as a full-round action to wriggle or break free, but if they move out of their square into another square with soul web in it they'll have to make another Reflex save or be caught again. The web dissipates in 1 minute/level or when dismissed, and does not burn.
\item[Behir:] A line of electricity extends out to short range from the Totemist's mouth. It does 1d6 Electricity Damage/level and allows a Reflex Save for half damage.
\item[Chimera:] A cone of fire is breathed out to short range. It does 1d6 Fire Damage/level and allows a Reflex Save for half damage.
\item[Cloaked Ape:] The Totemist gains Fast Healing equal to their level for 4 rounds. This ability can be invoked as a Swift action.
\item[Cloaker:] Creates images equivalent to \linkspell{Major Image} within Short Range. The Totemist need not concentrate on the images, but they vanish in 4 rounds.
\item[Cockatrice:] Touch forces target to make a Fortitude Save or be petrified.
\item[Digester:] A cone of Acid is spat out to short range. Targets in the area suffer 1d4 Acid Damage/level (Reflex Half), and then the following turn suffer the same amount of damage unless they have cleaned themselves off.
\item[Joystealer:] Target within Medium Range must make a Will Save or suffer 1d6 of Charisma Damage and be afflicted as per \linkspell{Crushing Despair}.
\item[Manticore:] The Totemist launches a number of spikes of soul energy equal to their Level, distributed between one or more targets within Medium Range. Each spike inflicts 1d6 damage.
\item[Pegasus:] Totemist gains a 90' Flight Speed with Good Maneuverability for the next 4 rounds. Activating this is a Swift Action.
\item[Phase Wasp:] The Totemist gains the benefits of \linkspell{True Seeing} for 4 rounds.
\item[Shadow Mastiff:] All other creatures within Short Range must make a Will Save or become \linkcondition{Panicked} for 1d6 rounds. This is a [Sonic] [Mind Affecting] [Fear] effect.
\item[Thorn Maw:] With a melee touch attack, the target suffers 2d6 Force Damage. There are then thorns of force crawling in their skin like a Linkin Park Song, and they take 2d6 of Force Damage each round on the Totemist's turn for 1 round/level. This ongoing damage can be halted by taking a Standard Action to make a DC 15 Heal check to gauge out the force thorns. Each attempt inflicts 1 hit point of damage whether it succeeds or fails.
\item[Unicorn:] Heal a touched target by 1d6/level and remove any poisons they are afflicted with.
\item[Winter Wolf:] The Totemist breathes a cone of Cold out to Short Range. It inflicts 1d6/level Cold Damage, with Reflex save for half damage.
\end{description*}

\textbf{Blood of Soulfire (Su):} A 5th level Totemist is immune to poison and when they suffer damage from physical attacks they cause 1 point of Force Damage to all creatures within 5' of them as Soulfire splashes out.

\textbf{Beast Companion:} At 6th level, a Totemist is entitled to a companion. Their companion is a Magical Beast with a CR 2 less than their character level. When the Totemist gains a level, their companion either gets more powerful for no reason or their companion wanders off and they get a new companion. Either way.

\textbf{Advanced Soulmelds:} At seventh level, each Soulmeld can be attached to an Advanced Totem, and the power delivered when called upon is as such:
\begin{description*}
\item[Basilisk:] Target within medium range must make a Fortitude save or be \linkcondition{Petrified}.
\item[Blink Dog:] As \linkspell{Dimension Door}.
\item[Brood Keeper:] A spectral swarm races out to engulf your enemies, as summon swarm. The swarm summoned uses your save DC (10 + half level + Cha modifier) for its abilities, inflicts force damage rather than normal damage, is incorporeal, and persists for four rounds.
\item[Bulette:] The ground trembles as earth and stone excavate themselves at the Totemist's urging. The character can tunnel out up to a 10'x10'x40' area. Every end must be within short range, and yes you can create holes under enemies and drop them in.
\item[Chaos Beetle:] One target within Short Range must make a Will Save or be confused as per the spell \linkspell{Confusion}. This can be invoked as a Swift Action.
\item[Displacer:] The Totemist gains full displacement and a 50\% miss chance for 4 rounds. This is a Swift Action to activate.
\item[Ethereal Marauder:] The Totemist and everything they carry is shifted to the Ethereal Plane or back to the Material from the Ethereal.
\item[Frost Salamander:] The Totemist exudes an aura of cold. All creatures that begin their turns within 15' of the Totemist suffer 1d6/2 levels of Cold Damage. This effect lasts 4 rounds.
\item[Girallon:] Spectral arms rip the target to pieces. The Totemist makes 4 melee touch attacks, and each is a claw that inflicts 1d6 Damage / 2 levels.
\item[Lamia:] As \linkspell{Charm Monster}. This is a [Mind Affecting] [Compulsion] and allows a Will Save.
\item[Mud Maw:] Two soul tendrils lash out and grab enemies. The Totemist can make two melee touch attacks against one or two creatures within 10'. Any creature touched is pinned for 1 round.
\item[Nymph:] Short Ranged Burst. All creatures in area that can see the Totemist must make a Fortitude Save or be \linkcondition{blind}.
\item[Phoenix:] For the next 4 rounds, the Totemist is immune to Fire, and heals when they would suffer fire damage. Also there is a 5' burst of flame centered on the Totemist that inflicts 1d6/level Fire Damage (Reflex Half), and that heals the Totemist because it is Fire Damage.
\item[Remorhaz:] The Totemist catches on fire, and anything she touches or that even hits her in melee suffers 1d6/level of fire damage from the experience. This effect lasts 4 rounds.
\item[Wyvern:] Melee Touch Attack causes target to suffer 3d6 Constitution Damage from Poison. Fortitude Save for Half.
\item[Yrthak:] Target within Medium Range suffers 1d6/level Sonic damage, Fortitude half.
\end{description*}

\textbf{Speak with Souls (Su):} A Totemist of 8th level can see the souls of the living and the dead. They are apparently little blue flamy things like in Soul Eater. The Totemist can speak with the souls of the dead as if the dead were still alive. The souls depart in about a week unless they get transformed, consumed, or returned to life before that point.

\textbf{Corpse Fashion (Su):} Three times a day, a 9th level Totemist can fabricate things out of animal parts. This can make things as respectable as hide armor or as creepy as human bone swords.

\textbf{Reincarnate (Su):} Three times a week, a 9th level Totemist can bring someone back from the dead in a new body. Like reincarnation.

\textbf{Astounding Soulmelds:} At tenth level, each Soulmeld can be attached to an Astounding Totem, and the power delivered when called upon is as such:
\begin{description*}
\item[Avalancher:] As \linkspell{Transmute Rock to Mud}.
\item[Cloud Ray:] As \linkspell{Telekinesis}.
\item[Frost Worm:] A strange trill forces everyone to stand still. Emanation extends to Medium range and affects every creature except the Totemist. Creatures that fail a Will Save are stunned for a d4 rounds. This is a [Sonic] effect.
\item[Inferno Spider:] Can throw a flaming soul web. Creatures within or moving within a 15' burst within short range must make a Reflex Save or be entangled and anchored in place. An entangled creature may make an Escape Artist or Strength check (DC 20) as a full-round action to wriggle or break free, but if they move out of their square into another square with soul web in it they'll have to make another Reflex save or be caught again. The web dissipates in 1 minute/level or when dismissed, and is on fire. All creatures suffer 1d8 + Level Fire Damage every round they begin in the area of the web.
\item[Lodestone Marauder:] Magnetic pulse yoinks all freestanding and handheld metal objects in a Medium Cone and piles them at the Totemist's feet. Creatures can hold onto their weapons and whatnot by making a Reflex save. Creatures wearing metal armor are subjected to a strong gale.
\item[Naga:] Target within short range must make a Fortitude Save against Poison or Die. Successful save still results in 1d8 Poison damage to Constitution.
\item[Nightmare Beast:] A creature that is asleep within 5 miles that the Totemist is aware of makes a Fortitude save or dies. This is a [Death] effect.
\item[Nightmare:] Can \linkspell{Plane Shift} into a different realm of existence.
\item[Peryton:] Touch attack inflicts 10 points of damage per level.
\item[Pixie:] All creatures in a 15' burst within Medium range must make a Will Save or fall asleep for 10 minutes/level. This is a [Mind Affecting] effect.
\item[Purple Worm:] Touch Attack shrinks the target to the size of a walnut and swallows them whole. Target suffers 4d8 Acid damage a round and cannot free themselves. If they are transported out of the Totemist or the Totemist dies, they return to normal size.
\item[Rapture Locust:] All creatures within Short Range must make a Will save or be dazed for a d6 rounds. Dazed creatures have locusts made of blue soulfire chewing on them for 2d6 Force damage per round until they snap out of it.
\item[Roper:] The Totemist can fire 6 soul strands at one or more targets within Short Range. Each Strand is a Ranged Touch Attack that inflicts 1d8 Strength Damage.
\item[Sphinx:] The Totemist lets out a mighty roar, and all creatures within Long Range must make a Willpower Save or become \linkcondition{Panicked} for 2d6 rounds. Even creatures that succeed in their save are shaken. This is a [Mind Affecting] [Sonic] [Fear] effect.
\end{description*}

\textbf{Auto-Life (Su):} If a 12th level Totemist has been dead for a whole day, they reincarnate into a new body unless something has happened to their soul in the meantime. This does not cost them a level, it's just slightly disconcerting.

\textbf{Favor of the Totems:} From 13th level on, a Totemist need only forgo calling on a Totem's powers for 2 rounds after the last time they called upon the Totem's Powers.

\textbf{Exciting Soulmelds:} At fourteenth level, each Soulmeld can be attached to an Exciting Totem, and the power delivered when called upon is as such:
\begin{description*}
\item[Acid Snake:] As \linkspell{Acid Fog}. The fog lasts for 4 rounds.
\item[Brain Rat:] All targets within a Medium Cone must make a Will save or be stunned for 2d4 rounds. This is a [Mind Affecting] [Psionic] effect.
\item[Catoblepas:] Target within Medium Range must make a Fortitude Save or die. This is a [Death] effect. Even if the target succeeds, they still take 1d8 damage/2 levels.
\item[Gorgon:] The Totemist breathes a cone out to Short Range. All creatures in the cone must make a Fortitude Save or be petrified.
\item[Gravity Coon:] As \linkspell{Reverse Gravity}, targets are allowed a Reflex Save as normal.
\item[Lammasu:] As \linkspell{Heal}.
\item[Psi Hornet:] As \linkspell{Dominate Monster}. Target is entitled to a Will Save. This is a [Mind Affecting] [Compulsion].
\item[Razor Boar:] Touch attack decapitates target. This is a [Death] effect.
\item[Spirit of the Air:] The Totemist decides what the weather is.
\item[Titanic Toad:] The Totemist stamps on the ground and flattens everything around them. All other creatures and standing objects in a 40' radius are subjected to a d8/level in Force Damage and are knocked prone. A successful Reflex save halves the damage and negates the prone effect.
\end{description*}

\textbf{Embody Totem (Su):} With a standard action, a 15th level Totemist can transform into one of the creatures that is one of their displayed totems. You can argue with the DM as to how Wildshape works, but you get all the Extraordinary, Supernatural, and Spell-like abilities whether they are Attacks or Qualities or whatever.

\textbf{Giant-size Soulmelds:} At Seventeenth level, each Soulmeld can be attached to a Giant-size Totem, and the power delivered when called upon is as such:
\begin{description*}
\item[Chaos Roc:] All creatures in a Medium Range Cone are struck with 2 colors from a \linkspell{Prismatic Spray}.
\item[Eye Fiend:] The Totemis can create a conical emanation of anti-magic field that extends from their body in any direction and can be rotated each turn. It persists for 4 rounds, and goes out to short range.
\item[Leviathan:] The Totemist is Colossal as per the spell \linkspell{Giant Size} for four rounds. This Totem is invoked as a Swift Action.
\item[Lucent Worm:] Every creature that is in the Totemist's Threatened Area before the start of their next turn must make a Fortitude save or be \linkcondition{paralyzed} for 4 rounds.
\item[Megapede:] wave of force precedes the Totemist as they stampede enemies. Any creatures and freestanding objects within 20 feet are pushed out of the area, suffering 1d20 force damage per 5' moved. The force lasts until the beginning of next turn, and enemies are pushed out of their area (for another d20 of damage per 5' square pushed) as the Totemist moves. Creatures are entitled to a Reflex save for half damage and to move out of the way in a direction of their choice to avoid getting Tekken juggled.
\item[Sky Bleeder:] Acid rains from the sky for a mile in every direction, causing 3d4 Acid damage a round for the next 4 rounds.
\item[Tarrasque:] The Totemist is restored to full health and all baleful conditions end.
\item[Thunder Worm:] The Totemist becomes Incorporeal for the next 4 rounds, and in departing from physicality lets off a huge thunderclap that breaks things in all directions. Everything around the Totemist in a Medium Ranged Burst is subjected to 1d8/level Sonic damage (Reflex Half).
\item[Time Hawk:] The Totemist takes a second round of action after her normal one. This Totem is invoked as a Swift Action.
\item[Underdrake:] The Totemist vomits forth a creature compatible with \linkspell{Summon Monster VIII}.
\end{description*}

\textbf{Limitless Favor of the Totems:} At 18th level, the Totemist can call on any of her displayed Totems that she did not call last turn.

\textbf{Triumph Promised by Ancestors (Su):} At 20th level, the Totemist wins the game.

\textbf{Soulmelds Table:} To name a Soulmeld, combine the Totem with an adjective, a color, and a thingy. This can go in any order you want. So for example, you might have Dimming Electric Corollax Wings or Corollax Crushing Cyan Gauntlets. Whatever. You can fudge it a bit so it sounds less ridiculous (or not, at your option). Also, you can really have your soulmelds be any color you want, as long as they are blue.

\begin{basictable}{Totemist Soulmeld Names}{l l l l}
\textbf{d20} & \textbf{Adjective} & \textbf{Color} & \textbf{Noun}\\
1 & Crushing & Azure & Claws \\
2 & Rising & Beryl & Mantle \\
3 & Fierce & Aqueous & Cloak\\
4 & Dimming & Blue & Wings \\
5 & Clutching & Cerulean & Armor \\
6 & Gnawing & Cobalt & Mask \\
7 & Grasping & Electric & Gloves \\
8 & Devastating & Midnight & Sleeves \\
9 & Expansive & Indigo & Robe \\
10 & Secret & Navy & Helm \\
11 & Protective & Ocean & Hat \\
12 & Monstrous & Sapphire & Horns \\
13 & Horrendous & Teal & Gauntlets \\
14 & Awesome & Turquoise & Cape \\
15 & Wicked & Ultramarine & Belt \\
16 & Depressive & Sky & Boots \\
17 & Repetitive & Steel & Trail \\
18 & Vengeful & Cyan & Eyes \\
19 & Gorgeous & Pale & Braids \\
20 & Futile & Red & Amulet\\
\end{basictable}
