%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\classentry{True Fiend}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\tagline{"I am a lord of the realms infernal, if I wanted your opinion I would beat it out of you."}

Demon, Devil, Nokoloth, Dezabi\ldots{} these are the names that inspire terror throughout the planes, and with good reason. These True Fiends are far more powerful than the other denizens of the Dark Realms. These fiends stand above others and are destined to a life of greatness, to be legendary in the annals of Evil.

These True Fiends are good at everything they do, but this doesn't make them more powerful at any particular level than any other fiend. Indeed, level is a measure of power. The most powerful fiends are True Fiends \textit{and higher level} than Fiendish Brutes. The True Fiend advances in everything all at once, and thus gains new abilities relatively slowly compared to what other, more focused Fiendish progressions are capable of.

\textbf{Alignment:} Nothing \textit{requires} a True Fiend to be Evil, but it's\ldots{} highly recommended that they be Evil.

\textbf{Races:} The True Fiend is \textit{only} available to Outsiders with a plane of origin in the Lower Planes. Creatures from the prime material plane whose ancestors were from a Lower Plane may take this class, but they must have the Outsider type.

\textbf{Starting Gold:} 6d6x10 gp (210 gold)

\textbf{Starting Age:} Since a True Fiend is immortal and never ages, a character may claim any starting age she wishes.

\textbf{Hit Die:} d8

\textbf{Class Skills:} The True Fiend's class skills (and the key ability for each skill) are \linkskill{Bluff} (Cha), \linkskill{Climb} (Str), \linkskill{Concentration} (Con), \linkskill{Diplomacy} (Cha), \linkskill{Disguise} (Cha), \linkskill{Escape Artist} (Dex), \linkskill{Hide} (Dex), \linkskill{Intimidate} (Cha), \linkskill{Knowledge} (any) (Int), \linkskill{Listen} (Wis), \linkskill{Move Silently} (Dex), \linkskill{Search} (Int), \linkskill{Sense Motive} (Wis), \linkskill{Sleight of Hand} (Dex), \linkskill{Spellcraft} (Int), \linkskill{Spot} (Wis), \linkskill{Survival} (Wis), \linkskill{Use Magic Device} (Cha), and \linkskill{Use Rope} (Dex).

\textbf{Skills/Level:} 8 + Intelligence Bonus

\goodbab{}
\goodfor{}
\goodref{}
\goodwil{}

\begin{classtable}
\levelone{Immortality, Fiendish Traits}
\leveltwo{Telepathy}
\levelthree{Fiendish Damage Reduction}
\levelfour{Sphere}
\levelfive{Greater Fiendish Traits}
\levelsix{--}
\levelseven{Greater Fiendish Damage Reduction}
\leveleight{Sphere}
\levelnine{Summoning}
\levelten{--}
\leveleleven{Bonus Feat}
\leveltwelve{Sphere}
\levelthirteen{Greater Fiendish Damage Reduction}
\levelfourteen{--}
\levelfifteen{Greater Summoning}
\levelsixteen{Sphere}
\levelseventeen{Dark Power}
\leveleighteen{--}
\levelnineteen{Epic Damage Reduction}
\leveltwenty{Sphere}
\end{classtable}

\classfeatures

\textbf{Weapon and Armor Proficiency:} True Fiends are proficient with all simple and martial weapons, as well as the whip, the scourge, and the dire flail. True Fiends are proficient with light armor but not with shields of any kind.

\textbf{Immortality (Ex):} Like a pizza on the counter, the True Fiend only gets worse with age.

\textbf{Fiendish Traits:} A True Fiend is a member of one of the iconic aristocracies evil. Starting at first level she has gains access to the distinctive abilities of her race, as befits her plane of origin:

\begin{description}
\item[Nine Hells:] Devil Traits\\
\textbf{See in Darkness (Su):} A Devil can see in normal or magical darkness as if it was fully illuminated.\\
\textbf{Immunity to Fire (Ex):} A Devil takes no damage from fire of any kind.

\item[The Abyss:] Demon Traits\\
\textbf{Bonus Feat:} Forged with unbridled Chaos, every Demon is unique. Upon gaining access to its Fiendish Traits, a Demon gains one bonus feat of any [Fiend] feat that it qualifies for.\\
\textbf{Immunity to Electricity (Ex):} A Demon takes no damage from electricity of any kind.

\item[Gehenna:] Nokoloth Traits\\
\textbf{Magic Resistance (Ex):} Nokoloths are inherently resistant to magic, and have a Spell Resistance of 10 + their character level.\\
\textbf{Immunity to Acid (Ex):} A Nokoloth takes no damage from Acid of any kind.

\item[Carceri:] Dezabi Traits\\
\textbf{Freedom of Movement (Ex):} a Dezabi benefits from the effects of a \linkspell{Freedom of Movement} spell at all times.\\
\textbf{Immunity to Poison (Ex):} A Dezabi suffers no harmful effect from poisons of any kind.
\end{description}

\textbf{Telepathy (Su):} At 2nd level, a True Fiend gains the ability to communicate telepathically with any creature that speaks a language within 100 feet.

\textbf{Fiendish Damage Reduction (Su):} At 3rd level, the True Fiend gains damage reduction that stops their class level in damage and that can be penetrated by Good weapons \textit{or} weapons made out of a material that is baneful to the Fiend's race (Silver for Devils, Wood for Nokoloths, Iron for Demons, and Stone for Dezabi). At 7th level, the Damage Reduction can be penetrated only by Good weapons. At 13th level the Damage Reduction is only penetrated by weapons which are \textit{both} Good \textit{and} made of a baneful substance. At 19th level, the True Fiend's Damage Reduction can only be penetrated by Good \textit{and} Epic weapons.

\textbf{Sphere:} The True Fiend gains basic access to a sphere at 4th level, and gains a new sphere at every fourth level afterwards. If the True Fiend selects a sphere that she already has basic access to, she upgrades it to advanced access. If she already had advanced access, she gains expert access.

\textbf{Greater Fiendish Traits:} A True Fiend of 5th level or more gains access to more of the distinctive abilities of her race, as befits her plane of origin:

\begin{description}
\item[Nine Hells:] Devil Traits\\
\textit{Mundane Poison Immunity (Ex):} A Devil is immune to all non-magical poisons.\\
\textit{Resistances (Ex):} A Devil has Cold and Acid Resistance 10.

\item[The Abyss:] Demon Traits\\
\textit{Mundane Poison Immunity (Ex):} A Demon is immune to all non-magical poisons.\\
\textit{Resistances (Ex):} A Demon has Cold, Fire, and Acid Resistance 10. 

\item[Gehenna:] Nokoloth Traits\\
\textit{Mundane Poison Immunity (Ex):} A Nokoloth is immune to all non-magical poisons.\\
\textit{Resistances (Ex):} A Nokoloth has Cold, Fire, and Electricity Resistance 10. 

\item[Carceri:] Dezabi Traits\\
\textit{Immunities (Ex):} The worlds of Carceri are varied beyond belief and each is filled with a new torture that defies comprehension. Upon reaching 5th level, a Dezabi gains immunity to 2 Energy Types. Once chosen, the energy types cannot be changed.
\end{description}

\textbf{Summoning (Sp):} At 9th level, a True Fiend can attempt to summon others of its kind once per day (for example: a Nokoloth could summon other Nokoloths). Summoning another Fiend of the same character level has a 40\% chance of success, and summoning a Fiend of a lower level increases the chances of success by 10\% for every level the summoner's level exceeds the CR of the target.

\textbf{Bonus Feat:} At 11th level, a True Fiend gains a bonus feat. This feat may be any [Fiend] feat for which she meets the prerequisites.

\textbf{Greater Summoning (Sp):} A True Fiend of 15th level may attempt to use her summon power to summon a fiend of a level higher than her own, though doing so carries only a 30\% chance of success.

\textbf{Dark Power (Ex):} The powers of the lower planes are awesome to behold. At 17th level, the True Fiend gains a +10 bonus to defeating Spell Resistance with the spell-like abilities granted by her spheres.
